### 2021-09-26 tex/article.tex
tex update

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Journal of Computers and Fluids}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Auto-tuned Jacobi-like Multi-grid Smoother\\ for Fast Pressure Projection}

%% Group authors per affiliation:
\author{Gabriel D Weymouth}
\address{Engineering and Physical Sciences, University of Southampton, Southampton, UK}
\address{Data-Centric Engineering, Alan Turing Institute, London, UK}
\ead[url]{https://weymouth.github.io/}

\begin{abstract}
Pressure projection is the single most computationally expensive step in an unsteady incompressible fluid simulation. This work discusses the potential of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection, linking Multigrid methods to Convolutional Neural Networks. Required to maintain linearity in pressure, the best option for data-driven acceleration is in the preconditioning and smoothing stages. Using automatic differentiation, a high-speed parameterized smoother is developed which outperforms classic smoothing methods by 66-200\% on eleven 2D and 3D benchmarks. The tuned parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of any flow.
\end{abstract}

\begin{keyword}
pressure projection, linear algebra, data-driven
\end{keyword}

\end{frontmatter}

\section{Introduction}

Geometric Multigrid methods are among the fastest approach for the solution of variable coefficient discrete pressure Poisson equations posed on structured computational grids.

\section{Approach}

\section{Results}

\section{Conclusions}

\section*{References}

\bibliography{mybibfile}

\end{document}

### 2021-09-26 tex/article.tex
paper update

@@
 \bibliographystyle{elsarticle-num}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{amsmath}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Geometric Multigrid methods are among the fastest approach for the solution of variable coefficient discrete pressure Poisson equations posed on structured computational grids.
+Pressure projection is a bottleneck in high-speed unsteady incompressible flow solvers.
+The pressure projection step typically makes up 25-50\% of the solution cost even in serial simulations, and the proportional cost grows in massively parallel simulations as the elliptic pressure Poisson equation requires communication throughout the computational domain instead of being confined to a local characteristic.
+Methods such as artificial-compressibility, smooth-particle-hydrodynamics, and particle-in-cell attempt to side-step this computational cost by modelling or otherwise under-resolving the pressure evolution compared to the fluid's momentum.
+However, these approaches lead to significant errors in pressure forces, thereby making them unsuitable for many applications or requiring explicit pressure corrections.
 
-\section{Approach}
+Recent advances in data-driven acceleration of flow solvers have mainly focused on data-assimilation methods and data-driven turbulence closures.
+Data-assimilation methods typically avoid the expensive pressure projection step entirely, focusing on applications where time-accurate pressure forces are not important.
+Data-driven closures for Large Eddy Simulation (LES) and Unsteady Reynolds Averaged Navier-Stokes (unRANS) and even Spanwise Averaged Navier-Stokes (SANS) simulations have seen growing success and are capable of accurate force prediction.
+Convolutional Neural Networks (CNN)s were introduced by () and are among the best data-driven methods for classification and regression of 2D images and 3D fields, having been applied in fluid dynamics applications from turbulence closures to super-resolution predictions.
+The translational symmetry built into the convolution ensures that correlations between the input and output anywhere in the data are generalized automatically.
+CNN architectures often use a restriction phase, where the size of the network is reduced before expanding again, to focus learning on a few key variables and further improve generalization of the method to unseen cases.
+However, the pressure projection step in these studies have not been augmented, leaving their acceleration as an open topic.
+
+Some recent work has focused on the pressure projection step explicitly.
+Chaotic projection methods for massively parallel systems; not data driven.
+Multi-grid data-driven decomposition; high errors and unclear speed-up.
+This work links develops a high-speed parameterized smoother which outperforms classic smoothing methods on eleven 2D and 3D benchmarks.
+Moreover, as the approach in linear in the pressure and scale-invariant, the parameters can be tuned on a coarse simulation and maintain their accelerated performance on the fine simulation.
+
+\section{Data-driven Accelerated Solution of Linear Systems}
+
+The discrete Poisson equation at the heart of the projection step is defined as
+\begin{equation}
+    A x = b
+\end{equation}
+where $x$ is the desired pressure field vector, $b$ is the source term (proportional to the divergence of the velocity field to be projected), and $A$ is the Poisson matrix.
+For second-order conservative Poisson systems posed on structured grids in $M$ dimensions, $A$ is symmetric and has only $M$ non-zero sub-diagonals.
+This means matrix-vector multiplication $Ax$ has computational cost $O(NM)$ where $N$ is the number of elements in $x$.
+In addition each row and column of $A$ is zero-sum, meaning the matrix is negative semi-definite and has a single zero eigenvalue.
+
+Iterative method update an approximate solution $x^k$ to a new solution $x^{k+1}$ with reduced error. As the problem is linear we can determine the update $\epsilon$ as
+\begin{equation}
+    A \epsilon^k = r^k \equiv b - Ax^k
+\end{equation}
+where $r$ is the residual. In practise, only an approximate solution for $\epsilon$ is obtained, after which the solution and residual are incremented
+\begin{equation}
+    x^{k+1} = x^k+\epsilon^k, \quad r^{k+1} = r^k-A\epsilon^k.
+\end{equation}
+This process is iterated until the residual is reduced sufficiently, the required tolerance level being highly dependant on the application.
+
+A Multi-grid (MG) method is effectively a \textit{linear} CNN architecture where the residual is restricted down to a reduced-size problem and the solution is prolongated back up.
+The restriction-solve-prolongation processes distributes the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to \textit{smooth} the local high-frequency error in the projected solution.
+The MG architecture proceeds recursively on the reduced-size problems until a small linear algebra problem is reached which can be approximated with minimal cost.
+Because of their recursive nature, MG methods are among the fastest approaches for variable coefficient discrete pressure Poisson equations, demonstrating $N\log N$ scaling with the total size $N$ of the solution vector.
+
+When considering data-driven methods to accelerate the projection step, maintaining the linearity of the system is critical.
+However, this linearity needs only be maintained with respect to the input pressure field - the coefficients of the ``MG network'' could all potentially be adjusted to optimize performance for a specific sub-class of problems.
+
+\section{Parameterized Smoother Approach}
+
+We define a simple parameterized Jacobi-like smoother as a sparse matrix multiplication, i.e. the correction $\epsilon$ is given by
+\begin{equation}
+    \epsilon = \tilde A^{-1}r
+\end{equation}
+after which the solution and residual are incremented as
+This means that applying the smoother requires no back-propagation and so can be implemented as a fast vector-operation in serial or even parallel simulations.
+
+The diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are constructed separately
+\begin{equation}
+    \tilde a^{-1}_{ii} = \frac{f_D(a_{ii}/s|\theta_D)}{a_{ii}} , \quad
+    \tilde a^{-1}_{ij} = \frac{f_L(a_{ij}/s|\theta_L)}{a_{ii}}
+\end{equation}
+where the coefficients are scaled by $s=\max(a_{ij})$.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \caption{2D-box}
+        \label{fig:2D-box}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \caption{2D-$\mu$}
+        \label{fig:2D-mu}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \caption{2D-sphere}
+        \label{fig:2D-sphere}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/crossloss.png}
+        \caption{$\log_{10}$ residual reduction}
+        \label{fig:cross plot}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/crosscount.png}
+        \caption{Solver time}
+        \label{fig:synthetic time}
+    \end{subfigure}
+    \caption{(a-c) Sample solutions from the data-sets of three of the six synthetic cases.
+(d) Residual reduction over a single Multi-grid V-cycle on the `test' cases after tuning using the `train' case.
+Training case `union` refers to the smoother trained on all of the synthetic cases.
+(b) Time to reduce pressure residual by $10^{-3}$ for classical and parameterized smoothers on each synthetic case.
+Time is relative to the time of a single V-cycle using the Jacobi smoother.}
+    \label{fig:synthetic cases}
+\end{figure}
 
 \section{Results}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \caption{circle flow}
+        \label{fig:circle}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \caption{Taylor-Green Vortex}
+        \label{fig:TGV}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \caption{flapping wing}
+        \label{fig:donut}
+    \end{subfigure}
+    \begin{minipage}{0.45\textwidth}
+        \begin{subfigure}{\textwidth}
+        \centering
+        \caption{torus flow}
+        \label{fig:donut}
+        \end{subfigure}
+        \begin{subfigure}{\textwidth}
+        \centering
+        \caption{swimming shark}
+        \label{fig:donut}
+        \end{subfigure}
+    \end{minipage}
+    \hfill
+    \begin{subfigure}[b]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/compareloss.png}
+        \caption{$\log_{10}$ residual reduction}
+        \label{fig:synthetic time}
+    \end{subfigure}
+    \caption{(a-e) Snapshots from the five flow simulation cases.
+The Taylor-Green Vortex and torus flow are 3D cases, and the flapping wing and swimming shark have dynamic geometries.
+(f) Residual reduction over a single Multi-grid V-cycle for classical and parameterized smoothers on each case.
+The `transfer' smoother has been trained on the union of the synthetic data sets from Figure~\ref{fig:synthetic cases}.}
+    \label{fig:simulation cases}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/scaleloss.png}
+        \caption{$\log_{10}$ residual reduction}
+        \label{fig:scaled loss}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/crosscount.png}
+        \caption{Solver time}
+        \label{fig:simulation time}
+    \end{subfigure}
+        \caption{(a) Residual reduction over a single Multi-grid V-cycle on the full-resolution case.
+The `transfer' smoother has been trained on the union of the synthetic data sets from Figure~\ref{fig:synthetic cases}.
+The $\frac 18, \frac 14, \frac 12$ smoothers have been trained on simulations with the indicated reduced resolution \textit{in each spacial and temporal dimension}.
+(b) Time to reduce pressure residual by $10^{-3}$ for classical and parameterized smoothers on each simulation case.
+Time is relative to the time of a single V-cycle using the Jacobi smoother.}
+        \label{fig:tuned simulation}
+\end{figure}
 

### 2021-09-26 tex/article.tex
paper update

@@
 Data-driven closures for Large Eddy Simulation (LES) and Unsteady Reynolds Averaged Navier-Stokes (unRANS) and even Spanwise Averaged Navier-Stokes (SANS) simulations have seen growing success and are capable of accurate force prediction.
-Convolutional Neural Networks (CNN)s were introduced by () and are among the best data-driven methods for classification and regression of 2D images and 3D fields, having been applied in fluid dynamics applications from turbulence closures to super-resolution predictions.
-The translational symmetry built into the convolution ensures that correlations between the input and output anywhere in the data are generalized automatically.
-CNN architectures often use a restriction phase, where the size of the network is reduced before expanding again, to focus learning on a few key variables and further improve generalization of the method to unseen cases.
-However, the pressure projection step in these studies have not been augmented, leaving their acceleration as an open topic.
+Convolutional Neural Networks (CNN) are among the best data-driven methods for classification and regression of 2D images and 3D fields, having been applied in fluid dynamics for turbulence closures as well as other applications such as super-resolution prediction and generative models.
+CNN architectures have inherent translational symmetry and often use a restriction phase, where the size of the network is reduced before expanding again, both of which help with generalization to unseen cases.
 
+However, the pressure projection in these all of these studies have not been augmented, leaving their acceleration as an nearly untouched topic.
 Some recent work has focused on the pressure projection step explicitly.
@@
 
-\section{Data-driven Accelerated Solution of Linear Systems}
+\section{Linear System Description}
 
 The discrete Poisson equation at the heart of the projection step is defined as
-\begin{equation}
+\begin{equation}\label{eq:axb}
     A x = b
@@
 where $x$ is the desired pressure field vector, $b$ is the source term (proportional to the divergence of the velocity field to be projected), and $A$ is the Poisson matrix.
-For second-order conservative Poisson systems posed on structured grids in $M$ dimensions, $A$ is symmetric and has only $M$ non-zero sub-diagonals.
-This means matrix-vector multiplication $Ax$ has computational cost $O(NM)$ where $N$ is the number of elements in $x$.
-In addition each row and column of $A$ is zero-sum, meaning the matrix is negative semi-definite and has a single zero eigenvalue.
+For conservative Poisson equations, $A$ is symmetric, has zero-sum rows and columns, is negative semi-definite, and has a single zero eigenvalue.
+The matrix is also extremely sparse.
+Using a second-order scheme on structured grids in $M$ dimensions, $A$ has only $M$ non-zero sub-diagonals.
+While the solution vector size $N$ may easily be larger than $10^6$, this means matrix-vector multiplication $Ax$ has computational cost $O(NM)=O(N)$ instead of $O(N^2)$.
 
-Iterative method update an approximate solution $x^k$ to a new solution $x^{k+1}$ with reduced error. As the problem is linear we can determine the update $\epsilon$ as
+Iterative methods solve equation \ref{eq:axb} by updating an approximate solution $x^k$ to a new solution $x^{k+1}$ with reduced error.
+As the problem is linear, the equation for the update $\epsilon$ is simply
 \begin{equation}
@@
 
-A Multi-grid (MG) method is effectively a \textit{linear} CNN architecture where the residual is restricted down to a reduced-size problem and the solution is prolongated back up.
-The restriction-solve-prolongation processes distributes the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to \textit{smooth} the local high-frequency error in the projected solution.
+Multi-grid (MG) methods are among the fastest iterative solution approaches for variable coefficient discrete pressure Poisson equations.
+The MG operator is effectively a \textit{linear} CNN architecture where the system is preconditioned before the residual is restricted down to a reduced-size problem and the correction is prolongated back up.
+% \begin{equation}
+%     r_c = R r \quad\rightarrow\quad A_c \epsilon_c = r_c \quad\rightarrow\quad \epsilon = P \epsilon_c
+% \end{equation}
+% where $R$ is the $N_c \times N$ restriction operator, $P$ is the $N \times N_c$ prolongation operator 
+The restriction-solve-prolongation process, a V-cycle, distributes the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to \textit{smooth} the local high-frequency error in the projected solution.
 The MG architecture proceeds recursively on the reduced-size problems until a small linear algebra problem is reached which can be approximated with minimal cost.
-Because of their recursive nature, MG methods are among the fastest approaches for variable coefficient discrete pressure Poisson equations, demonstrating $N\log N$ scaling with the total size $N$ of the solution vector.
+This recursive approach results in only $O(N\log N)$ computational cost.
 
-When considering data-driven methods to accelerate the projection step, maintaining the linearity of the system is critical.
-However, this linearity needs only be maintained with respect to the input pressure field - the coefficients of the ``MG network'' could all potentially be adjusted to optimize performance for a specific sub-class of problems.
+\section{Data-driven Accelerated Solution Methods}
 
-\section{Parameterized Smoother Approach}
+As \textit{any} element of the residual of the elliptic system potentially influences \textit{every} element of the update, $O(N\log N)$ is the best possible solution time scaling.
+However, data-driven methods can still be used to accelerate pressure projection methods by speeding-up and increasing the residual reduction of each V-cycle iteration.
 
-We define a simple parameterized Jacobi-like smoother as a sparse matrix multiplication, i.e. the correction $\epsilon$ is given by
+The linearity of the system is another critical property, but this linearity needs only be maintained with respect to the update and residual fields.
+The coefficients of the ``MG network'' can all potentially be optimized for a specific sub-class of problems, and they can be made nonlinear functions of $A$.
+However, neither the restriction or prolongation operations are functions of $A$, and it not clear how this information could be integrated without slowing down the V-cycle.
+Similarly, a simple Jacobi preconditioner
+\begin{equation}
+    \epsilon = D^{-1}r
+\end{equation}
+where $D$ is the diagonal of $A$, is as fast as possible and is sufficient for the V-cycle to distribute the residual throughout the domain.
+This leaves the smoother as the best candidate for acceleration.
+
+While more complex options are certainly possible, this work uses a simple parameterized Jacobi-like smoother as
 \begin{equation}
@@
 \end{equation}
-after which the solution and residual are incremented as
-This means that applying the smoother requires no back-propagation and so can be implemented as a fast vector-operation in serial or even parallel simulations.
+where $\tilde A^{-1}=f(A|\theta)$ is an approximate matrix-inverse with the same sparsity as $A$ and $\theta$ are the parameters.
+Unlike Gauss-Sidel or SOR, the matrix-vector multiplication smoother requires no back-propagation and so can be implemented as a vector-operation in serial or parallel simulations, offering a significant potential speed-up.
 
-The diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are constructed separately
+There are few constraints on $\tilde A^{-1}$; it must have units of $A^{-1}$, and symmetry of $A$ implies the approximate inverse should also be symmetric.
+For simplicity, the diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are constructed separately
 \begin{equation}
@@
 \end{equation}
-where the coefficients are scaled by $s=\max(a_{ij})$.
+where diagonal-scaling is used externally, and the function inputs are scaled by $s=\max(a_{ij})$. Note a Jacobi smoother would use $f_D=1$ and $f_L=0$. T
 

### 2021-09-29 src/benchmark.jl
Update figures

@@ -1,0 +1,48 @@
+using LinearAlgebra, GeometricMultigrid, BenchmarkTools, Plots
+
+begin
+    include("candidate_smoothers.jl")
+    smoothers = [Jacobi!,GS!,SOR!,pseudo!]
+end
+begin
+    include("create_synthetic.jl")
+    suite = BenchmarkGroup()
+    A,b = static(;n=128,T=Float32)
+    for s ∈ smoothers
+        suite[s] = @benchmarkable mg!(st;mxiter=1,inner=2,smooth! = $s) setup=(st=mg_state($A,zero($b),$b,pseudo=true))
+    end
+end
+results = run(suite)
+time_factor = [minimum(results[s]).time/minimum(results[Jacobi!]).time for s ∈ [2:end]]
+begin
+    time_factor = [2.01557, 2.61135, 1.36815]
+end
+
+begin
+    include("create_synthetic.jl")
+    data = create_synthetic()
+end
+begin
+    itcount(A,b,s) = mg!(mg_state(A,zero(b),b,pseudo=true);reltol=1e-3,inner=2,smooth! = s,mxiter=32)
+    avecount(data,s) = sum(itcount(d...,s) for d ∈ data)/length(data)
+    counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
+end
+begin
+    counts = [ 3.0  3.0  2.64  2.33  3.65  3.08
+                3.0  4.0  2.53  2.5   3.05  3.92
+                3.0  3.0  1.88  2.27  3.17  3.0]
+end
+
+begin
+    using StatsPlots,CategoricalArrays
+    cats = ["Gauss-Sidel","SOR","Ã⁻¹ union"]
+    n = length(data)
+    colors = repeat([palette(:default)[2],palette(:default)[4],palette(:default)[3]],inner=n)
+    ctg = CategoricalArray(repeat(cats,inner=n))
+    levels!(ctg,cats)
+    groupedbar((counts.*time_factor)',size=(400,400),
+                group=ctg, legend=:bottomright,c=colors,
+                yaxis=("relative time"),
+                xaxis=("cases",(1:n,keys(data)),60))
+end
+savefig("synthetic_scaling.png")

### 2021-09-29 src/candidate_smoothers.jl

@@ -1,72 +1,83 @@
-# uniform 5-point stencil: loss ≈ -0.7, @btime(n=32)≈3.1μs
-smooth!(st,θ::AbstractVector;kw...) = smooth!(st,θ...;kw...)
-@fastmath function smooth!(st,a=1.004,b=0.159;kw...)
-    @loop st.ϵ[I] = st.iD[I]*(a*st.r[I]+b*rsum(I,st.r))
+using GeometricMultigrid
+using GeometricMultigrid: GS!,pseudo!,multL,multU,increment!
+Jacobi!(st;kw...) = GS!(st,inner=0)
+@fastmath function SOR!(st;inner=2,ω=0.9,kw...)
+    @loop st.ϵ[I] = ω*st.r[I]*st.iD[I]
+    for _ ∈ 1:inner
+        @loop st.ϵ[I] = (1-ω)*st.ϵ[I]+ω*st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ)-multU(I,st.A.L,st.ϵ))
+    end
     increment!(st;kw...)
 end
-rsum(I::CartesianIndex{N},r) where N = sum(@inbounds(r[I+δ(i,N)]+r[I-δ(i,N)]) for i in 1:N)
-θ = Float32[1.004244,0.15894948]
-loss(θ,train),loss(θ,test)
-@btime smooth!(st) setup=(st=mg_state($A,zero($b),$b))
 
-# uniform tensor kernel: loss ≈ -0.75. @btime(n=32)≈17.5μs
-using StaticArrays
-@inline smooth!(st,θ::AbstractVector;kw...) = smooth!(st,kern(θ...);kw...)
-@inline kern(a,b) = (v = SA[a 1 a]; b.*v'.*v)
-function smooth!(st,K::StaticArray;kw...)
-    @loop st.ϵ[I] = st.iD[I]*conv(K,@view(st.r.data[(I-oneunit(I)):(I+oneunit(I))]))
-    GeometricMultigrid.increment!(st;kw...)
-end
-function conv(K,v)
-    s = zero(eltype(K))
-    @inbounds @simd for i in eachindex(K,v)
-        s+=K[i]*v[i]
-    end
-    s
-end
-θ = Float32[0.201,1.167]
-loss(θ,train),loss(θ,test)
-@btime smooth!(st,K) setup=(st=mg_state($A,zero($b),$b);K = kern($θ...))
[…]

### 2021-09-29 src/create_synthetic.jl

@@ -48,13 +48,13 @@ end
 circle(;kw...) = sphere(;N=2,kw...)
 
 using DataStructures
-function make_data(;len=100,kw...)
+function create_synthetic(;len=100,kw...)
     OrderedDict(
-        "2D-box"=>[static(N=2;kw...) for i ∈ 1:len],
-        "3D-box"=>[static(N=3;kw...) for i ∈ 1:len],
-        "2D-μ"  =>[dipole(N=2;kw...) for i ∈ 1:len],
-        "3D-μ"  =>[dipole(N=3;kw...) for i ∈ 1:len],
-        "circle"=>[circle(;kw...) for i ∈ 1:len],
-        "sphere"=>[sphere(;kw...) for i ∈ 1:len]
+        "2D-static"=>[static(N=2;kw...) for i ∈ 1:len],
+        "3D-static"=>[static(N=3;kw...) for i ∈ 1:len],
+        "2D-dipole"=>[dipole(N=2;kw...) for i ∈ 1:len],
+        "3D-dipole"=>[dipole(N=3;kw...) for i ∈ 1:len],
+        "2D-sphere"=>[circle(;kw...) for i ∈ 1:len],
+        "3D-sphere"=>[sphere(;kw...) for i ∈ 1:len]
     )
 end

### 2021-09-29 src/create_waterlily.jl

@@ -76,7 +76,7 @@ function shark(p=6;k=5.3,A=0.1,St=0.3,Re=1e4,U=1,
 end	
 
 using DataStructures
-function make_data(;len=100,Δt=0.1,cases=[circle,TGV,donut,wing,shark],p=6,kw...)
+function create_waterlily(;len=100,Δt=0.1,cases=[circle,TGV,donut,wing,shark],p=6,kw...)
     data = OrderedDict()
     for case ∈ cases
         @show case

### 2021-09-29 src/test_waterlily.jl

@@ -3,8 +3,8 @@ import GeometricMultigrid: GS!,pseudo!,SOR!
 
 # Generate WaterLily simulation data
 begin # this block takes a few minutes...
-    include("data_waterlily.jl")
-    data = make_data()
+    include("create_waterlily.jl")
+    data = create_waterlily(;len=1,p=4)
 end
 
 # Set up a custom mg_state
@@ -41,9 +41,7 @@ end
 
 # Define smoother options and get loss across smoothers
 begin
-    Jacobi!(st;inner=2,kw...) = for _ ∈ 1:inner
-        GS!(st;inner=0,kw...)
-    end
+    Jacobi!(st;kw...) = GS!(st;inner=0,kw...)
     smoothers = [Jacobi!,GS!,pseudo!]
 end
 compareloss = [loss(d;smooth!) for smooth! ∈ smoothers, (_,d) ∈ data]
@@ -56,10 +54,11 @@ end
 
 begin
     using StatsPlots,CategoricalArrays
-    sizes = ["Jacobi","Gauss-Sidel","Ã⁻¹ transfer"]
-    ctg = CategoricalArray(repeat(sizes,inner=5))
-    levels!(ctg,sizes)
-    groupedbar(compareloss', group = ctg, legend=:bottomright,
+    cats = ["Jacobi","Gauss-Sidel","Ã⁻¹ transfer"]
+    ctg = CategoricalArray(repeat(cats,inner=length(data)))
+    levels!(ctg,cats)
+    groupedbar(compareloss', group = ctg, 
+                legend=:bottomright, size = (400,400),
                 yaxis=("log₁₀ residual reduction",:flip),
                 xaxis=("cases",(1:length(data),keys(data))))
 end
@@ -100,10 +99,10 @@ end
 # plot loss across examples and scales
 begin
     using StatsPlots,CategoricalArrays
-    sizes = ["transfer","⅛","¼","½","1"]
-    ctg = CategoricalArray(repeat(sizes,inner=5))
-    levels!(ctg,sizes)
-    groupedbar([compareloss[end,:] scaleloss'], 
+    cats = ["transfer","⅛","¼","½","1"]
+    ctg = CategoricalArray(repeat(cats,inner=length(data)))
+    levels!(ctg,cats)
+    groupedbar([compareloss[end,:] scaleloss'], size = (400,400),
[…]

### 2021-09-29 src/tune_synthetic.jl

@@ -2,7 +2,7 @@ using GeometricMultigrid, Plots, Printf, Optim
 
 # create synthetic example systems
 begin
-    include("data_synthetic.jl")
+    include("create_synthetic.jl")
     data = make_data()
 end
 
@@ -29,87 +29,86 @@ begin
         Optim.minimizer(optimize(p->loss(data;p,models),p₀, Newton(); autodiff = :forward))
 
     opt = OrderedDict(name=>fit(train,models) for (name,train) ∈ data)
-    opt["all"] = fit(vcat((d for (_,d) in data)...),models)
-    opt["jacobi"] = zeros(Float32,5)
+    opt["union"] = fit(vcat((d for (_,d) in data)...),models)
+    # opt["jacobi"] = zeros(Float32,5)
     opt
 end
-# "2D-box" => [-2.36056, -1.40822, -0.203578, 0.271696, -5.47975f-7]
-# "3D-box" => [0.206214, 0.0214632, -0.00525863, 0.315253, 0.0135281]
-# "2D-μ"   => [-1.71116, -0.902871, -0.114227, 0.166726, 3.14462f-7]
-# "3D-μ"   => [-0.663327, -0.199177, -0.00915381, 0.149958, -1.54752f-7]
-# "circle" => [-0.003891, 0.047247, 0.0149267, 0.377898, -0.217221]
-# "sphere" => [-0.0966329, -0.0967704, -0.00862894, 0.432134, -0.271047]
-# "all"    => [-0.144944, -0.0162348, 0.00734042, 0.363533, -0.201831]
-# "jacobi" => [0.0, 0.0, 0.0, 0.0, 0.0]
+begin
+    opt = OrderedDict(
+        "2D-static" => [-2.36056, -1.40822, -0.203578, 0.271696, -5.47975f-7],
+        "3D-static" => [0.206214, 0.0214632, -0.00525863, 0.315253, 0.0135281],
+        "2D-dipole" => [-1.71116, -0.902871, -0.114227, 0.166726, 3.14462f-7],
+        "3D-dipole" => [-0.663327, -0.199177, -0.00915381, 0.149958, -1.54752f-7],
+        "2D-sphere" => [-0.003891, 0.047247, 0.0149267, 0.377898, -0.217221],
+        "3D-sphere" => [-0.0966329, -0.0967704, -0.00862894, 0.432134, -0.271047],
+        "union"  => [-0.144944, -0.0162348, 0.00734042, 0.363533, -0.201831])
+end
 
 # compare across example types
[…]

### 2021-09-29 tex/article.tex

@@
 This work discusses the potential of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection, linking Multigrid methods to Convolutional Neural Networks.
-Required to maintain linearity in pressure, the best option for data-driven acceleration is in the preconditioning and smoothing stages.
-Using automatic differentiation, a high-speed parameterized smoother is developed which outperforms classic smoothing methods by 66-200\% on eleven 2D and 3D benchmarks.
+Required to maintain linearity in pressure, the best option for data-driven acceleration is in the smoothing step.
+Using automatic differentiation, a high-speed parameterized smoother is developed which outperforms classic Multi-grid methods by 66-200\% on eleven 2D and 3D benchmarks.
 The tuned parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of any flow.
@@
 Data-driven closures for Large Eddy Simulation (LES) and Unsteady Reynolds Averaged Navier-Stokes (unRANS) and even Spanwise Averaged Navier-Stokes (SANS) simulations have seen growing success and are capable of accurate force prediction.
-Convolutional Neural Networks (CNN) are among the best data-driven methods for classification and regression of 2D images and 3D fields, having been applied in fluid dynamics for turbulence closures as well as other applications such as super-resolution prediction and generative models.
-CNN architectures have inherent translational symmetry and often use a restriction phase, where the size of the network is reduced before expanding again, both of which help with generalization to unseen cases.
+Deep learning Convolutional Neural Networks (CNN) have enabled many of these turbulence closures as well as other fluids applications such as super-resolution and generative models.
+CNN architectures have inherent translational symmetry and often use a restriction phase, where the size of the network is reduced before expanding again, both of which help generalize the trained networks to unseen prediction cases.
 
-However, the pressure projection in these all of these studies have not been augmented, leaving their acceleration as an nearly untouched topic.
+However, the pressure projection in these all of these studies have not been augmented, leaving their acceleration as a nearly untouched topic.
 Some recent work has focused on the pressure projection step explicitly.
@@
 Using a second-order scheme on structured grids in $M$ dimensions, $A$ has only $M$ non-zero sub-diagonals.
-While the solution vector size $N$ may easily be larger than $10^6$, this means matrix-vector multiplication $Ax$ has computational cost $O(NM)=O(N)$ instead of $O(N^2)$.
+While the solution vector size $N$ may easily be larger than $10^6$, the matrix-vector multiplication $Ax$ only has computational cost $O(NM)=O(N)$ instead of $O(N^2)$.
 
@@
 Multi-grid (MG) methods are among the fastest iterative solution approaches for variable coefficient discrete pressure Poisson equations.
-The MG operator is effectively a \textit{linear} CNN architecture where the system is preconditioned before the residual is restricted down to a reduced-size problem and the correction is prolongated back up.
+The MG operator is effectively a \textit{linear} convolutional architecture where the system is preconditioned before the residual is restricted down to a reduced-size problem and the correction is prolongated back up.
 % \begin{equation}
@@
 
-The linearity of the system is another critical property, but this linearity needs only be maintained with respect to the update and residual fields.
+The linearity of the system is a critical property which the data-driven method must maintain, but this linearity is only with respect to the update and residual fields.
 The coefficients of the ``MG network'' can all potentially be optimized for a specific sub-class of problems, and they can be made nonlinear functions of $A$.
-However, neither the restriction or prolongation operations are functions of $A$, and it not clear how this information could be integrated without slowing down the V-cycle.
-Similarly, a simple Jacobi preconditioner
+However, neither the restriction or prolongation operations are functions of $A$, and a workable method of including the dependence is unclear.\footnote{For example, the residual restriction could use $a_{ij}$ to define a non-uniform weight function $w_{ij} = r_i/r_j$, but since the matrix is symmetric the same weight should apply to $r_j/r_i$, resulting in a uniform pooling.} Similarly, a simple Jacobi preconditioner
 \begin{equation}
@@
 where $D$ is the diagonal of $A$, is as fast as possible and is sufficient for the V-cycle to distribute the residual throughout the domain.
-This leaves the smoother as the best candidate for acceleration.
+Therefore, for the remainder of the paper we will focus on the smoother as the best candidate for acceleration, using a simple Jacobi preconditioner and uniform pooling/distribution for restriction/prolongation.
 
-While more complex options are certainly possible, this work uses a simple parameterized Jacobi-like smoother as
+While more complex options are certainly possible, this work uses a simple parameterized Jacobi-like smoother
 \begin{equation}
@@
 \end{equation}
-where $\tilde A^{-1}=f(A|\theta)$ is an approximate matrix-inverse with the same sparsity as $A$ and $\theta$ are the parameters.
-Unlike Gauss-Sidel or SOR, the matrix-vector multiplication smoother requires no back-propagation and so can be implemented as a vector-operation in serial or parallel simulations, offering a significant potential speed-up.
+where $\tilde A^{-1}=f(A\,|\theta)$ is an approximate matrix-inverse with the same sparsity as $A$ and parameter vector $\theta$. 
+%The matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be computed and stored ahead of time.
+Unlike Gauss-Sidel or SOR smoothers, the matrix-vector multiplication smoother requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
 
-There are few constraints on $\tilde A^{-1}$; it must have units of $A^{-1}$, and symmetry of $A$ implies the approximate inverse should also be symmetric.
-For simplicity, the diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are constructed separately
+There are few constraints on $\tilde A^{-1}$: it must have units of $A^{-1}$, and symmetry of $A$ implies the approximate inverse should also be symmetric.
+For simplicity, the diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are all constructed independently
 \begin{equation}
-    \tilde a^{-1}_{ii} = \frac{f_D(a_{ii}/s|\theta_D)}{a_{ii}} , \quad
-    \tilde a^{-1}_{ij} = \frac{f_L(a_{ij}/s|\theta_L)}{a_{ii}}
+    \tilde a^{-1}_{ii} = \frac{f_D(a_{ii}/s\,|\theta_D)}{a_{ii}} , \quad
+    \tilde a^{-1}_{ij} = \frac{f_L(a_{ij}/s\,|\theta_L)}{a_{ii}+a_{jj}}
 \end{equation}
-where diagonal-scaling is used externally, and the function inputs are scaled by $s=\max(a_{ij})$. Note a Jacobi smoother would use $f_D=1$ and $f_L=0$. T
+where function inputs are scaled by the maximum off-diagonal $s=\max(A-D)$ and the outputs are scaled by the diagonal elements. Note a Jacobi smoother would use $f_D=1$ and $f_L=0$.
+
+Automatic differentiation (AD) is used to optimize the parameterized smoother for a set of training data $X=\{A,x^k,b\}$.
+The loss function is simply the reduction in the norm of the residual after a V-cycle iteration $L = \log_{10}(|r^{k+1}| / |r^{k}|)$, which means that example pressure \textit{solutions} are not required.
+This loss is averaged over each iteration and each example in the data-set.
+The optimal parameters are defined as
+\begin{equation}
+    \hat\theta = \min_\theta L(\theta\, |X)
+\end{equation}
+and determined using Newton's method.
+The ForwardDiff.jl AD package is used determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ automatically.
+The adaptive and recursive nature of the MG V-cycle and general nonlinear form of $f$ would make analytic derivatives prohibitively unwieldy and error prone, and numerical finite differences potentially unstable and inaccurate.
 
@@
 (d) Residual reduction over a single Multi-grid V-cycle on the `test' cases after tuning using the `train' case.
-Training case `union` refers to the smoother trained on all of the synthetic cases.
+Training case `union' refers to the smoother trained on all of the synthetic cases.
 (b) Time to reduce pressure residual by $10^{-3}$ for classical and parameterized smoothers on each synthetic case.
@@
 
-\section{Results}
+\section{Synthetic Projection Systems and Results}
+
+A set of six synthetic projection cases were constructed to establish the characteristics of the parameterized smoother.
+The three 2D cases are show in Figure~\ref{fig:2D-box}-\ref{fig:2D-sphere}, and each has a matching 3D case.
+The `box' cases have a simple constant gradient solution throughout the domain, with the direction and magnitude randomized.
+The dipole `$\mu$' cases have a localized dipole within a quiescent flow with randomized placement, direction and magnitude.
+The `sphere' cases have a moving sphere immersed within a quiescent flow with randomized radius, location, and velocity direction.
+Neumann boundary conditions are applied on all boundaries, including the immersed sphere, through adjustment of the $A$ matrix coefficients which are otherwise uniform.
+All cases are initialized with $x^0=0$, and all cases feature initially localized residuals; i.e.
+$r^0\ne0$ only in a fraction of the cells, but $x$ must be updated throughout the domain, starkly illustrating the elliptic nature of the projection step.
+
+Figure~\ref{fig:cross plot} shows the `test' performance of the parameterized smoother over a single V-cycle on 100 randomized examples after optimization using 100 examples of the `test' case.
+Each example uses a grid size of n=32 point in each direction ($N=32^2$ in 2D and $N=32^3$ in 3D) as testing with other resolutions found essentially no change in the performance.
+As expected, the performance is best when testing and training on the same case, with the residual reduced by $10^{-1.18}$ on the 2D-sphere case down to $10^{-1.75}$ on the 2D-box case.
+The performance for the simplest `box' and 2D-$\mu$ cases generalizes poorly, with some cases diverging instead converging, but the optimized 2D-sphere smoother generalizes essentially as well as the `union' smoother trained on all of the data.
+%The performance of the `union' smoother is only 1-4\% lower than the smoother trained on the test case for the dipole and sphere cases.
 
@@
 
+\section{Unsteady Incompressible Simulation Results}
+
 \begin{figure}

### 2021-09-30 src/TunedSmoother.jl
Refactor for paper

@@ -1,5 +1,12 @@
 module TunedSmoother
 
-greet() = print("Hello World!")
+include("candidate_smoothers.jl")
+export Jacobi!,GS!,SOR!,pseudo!,state
+
+include("create_synthetic.jl")
+export create_synthetic
+
+include("create_waterlily.jl")
+export create_waterlily
 
 end # module

### 2021-09-30 src/candidate_smoothers.jl

@@ -1,12 +1,63 @@
 using GeometricMultigrid
-using GeometricMultigrid: GS!,pseudo!,multL,multU,increment!
-Jacobi!(st;kw...) = GS!(st,inner=0)
-@fastmath function SOR!(st;inner=2,ω=0.9,kw...)
-    @loop st.ϵ[I] = ω*st.r[I]*st.iD[I]
-    for _ ∈ 1:inner
-        @loop st.ϵ[I] = (1-ω)*st.ϵ[I]+ω*st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ)-multU(I,st.A.L,st.ϵ))
+using GeometricMultigrid: multL, multU, mult, increment!, δ
+
+# Classical smoothers
+@fastmath function GS!(st;inner=2,kw...) # copied from GeometricMultigrid
+    @loop st.ϵ[I] = st.r[I]*st.iD[I]
+    @inbounds for _ ∈ 1:inner, I ∈ st.iD.R
+        st.ϵ[I] = st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ)-multU(I,st.A.L,st.ϵ))
     end
     increment!(st;kw...)
+end
+@fastmath function SOR!(st;inner=2,ω=1.05,kw...)
+    @loop st.ϵ[I] = ω*st.r[I]*st.iD[I]
+    @inbounds for _ ∈ 1:inner, I ∈ st.iD.R
+       st.ϵ[I] = (1-ω)*st.ϵ[I]+ω*st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ)-multU(I,st.A.L,st.ϵ))
+    end
+    increment!(st;kw...)
+end
+Jacobi!(st;kw...) = GS!(st,inner=0)
+
+# Parameterized approximate inverse matrix P
+function PseudoInv(A::FieldMatrix; scale=maximum(A.L),
+    p::AbstractVector{T}=Float32[-0.1449,-0.0162,0.00734,0.3635,-0.2018],
+    models=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5]))) where T
+
+    L,D,N = zeros(T,size(A.L)),zeros(T,size(A.D)),size(A.L)[end]
+    Dm,Lm = models(p)
+    for I ∈ A.R
+        invD = (abs(A.D[I])<1e-8) ? 0. : 1.0/A.D[I]
[…]

### 2021-09-30 src/create_synthetic.jl

@@ -11,7 +11,7 @@ function static(;n=32,N=2,T::Type=Float32,m=rand(T,N))
             I.I[i] !=2 && (L[I,i] = 1)
         end
     end
-    A,x = Poisson(L),FieldVec(x)
+    A,x = Poisson(L),FieldVector(x)
     A,A*x
 end
 
@@ -27,7 +27,7 @@ function dipole(;n=32,N=2,T::Type=Float32,x0=rand(T,N),m=rand(T,N),s=rand(),Δt=
         end
     end
     b .-= sum(b)/n^N
-    Poisson(L),FieldVec(b)
+    Poisson(L),FieldVector(b)
 end
 
 @fastmath kern₀(d) = 0.5+0.5d+0.5sin(π*d)/π
@@ -43,9 +43,8 @@ function sphere(;n=32,N=3,T::Type=Float32,x0=rand(T,N),m=rand(T,N),s=rand(),Δt=
         I.I[i] !=2 && (L[I,i] = Δt*μm)
         b[I] += Δt*m[i]*(μp-μm)
     end
-    Poisson(L),FieldVec(b)
+    Poisson(L),FieldVector(b)
 end
-circle(;kw...) = sphere(;N=2,kw...)
 
 using DataStructures
 function create_synthetic(;len=100,kw...)
@@ -54,7 +53,7 @@ function create_synthetic(;len=100,kw...)
         "3D-static"=>[static(N=3;kw...) for i ∈ 1:len],
         "2D-dipole"=>[dipole(N=2;kw...) for i ∈ 1:len],
         "3D-dipole"=>[dipole(N=3;kw...) for i ∈ 1:len],
-        "2D-sphere"=>[circle(;kw...) for i ∈ 1:len],
-        "3D-sphere"=>[sphere(;kw...) for i ∈ 1:len]
+        "2D-sphere"=>[sphere(N=2;kw...) for i ∈ 1:len],
+        "3D-sphere"=>[sphere(N=3;kw...) for i ∈ 1:len]
     )
 end

### 2021-09-30 src/create_waterlily.jl

@@ -1,20 +1,22 @@
-using WaterLily
+import WaterLily
+using WaterLily: AutoBody, Simulation
+using GeometricMultigrid: Poisson,FieldVector
 using LinearAlgebra: norm2
 
-function poisson_setup!(a::Flow)
+function poisson_setup!(a)
     a.u⁰ .= a.u; a.u .= 0
     WaterLily.conv_diff!(a.f,a.u⁰,ν=a.ν)
     WaterLily.BDIM!(a); WaterLily.BC!(a.u,a.U)
-    @inside a.σ[I] = (WaterLily.div(I,a.u)+a.σᵥ[I])/a.Δt[end]
+    WaterLily.@inside a.σ[I] = (WaterLily.div(I,a.u)+a.σᵥ[I])/a.Δt[end]
     a.u .= a.u⁰ # roll-back!
 end
 
 function sim_collect_poisson!(sim;Δt=0.1,remeasure)
     a = sim.flow # less typing
-    sim_step!(sim,sim_time(sim)+Δt;remeasure)  # ∫ over dt & get new a.p
-    measure!(a,sim.body;t=sim.L/sim.U*sim_time(sim)) # get new a.μ₀
+    WaterLily.sim_step!(sim,WaterLily.sim_time(sim)+Δt;remeasure)  # ∫ over dt & get new a.p
+    WaterLily.measure!(a,sim.body;t=sim.L/sim.U*WaterLily.sim_time(sim)) # get new a.μ₀
     poisson_setup!(a)                            # get new a.σ
-    return copy(a.p),copy(a.μ₀),copy(a.σ)
+    return Poisson(copy(a.μ₀)),FieldVector(copy(a.p)),FieldVector(copy(a.σ))
 end
 
 function circle(p=6;Re=250,n=16,m=8,T=Float64)
@@ -46,7 +48,7 @@ function donut(p=6;Re=1e3,T=Float64)
     Simulation((2n+2,n+2,n+2),[1.,0.,0.],R;ν,body,T)
 end
 
-using StaticArrays
+using StaticArrays: SVector, @SMatrix
 function wing(p=6;Re=250,U=1,amp=π/4,ϵ=1,thk=2ϵ+√2,T=Float64)
     L = 2^(p-1)
     sdf(x,t) = norm2(x .- SVector(0.,clamp(x[2],-L/2,L/2)))-thk/2

### 2021-09-30 benchmark.jl
update benchmark

@@ -1,0 +1,43 @@
+using BenchmarkTools, Plots, GeometricMultigrid, TunedSmoother
+
+begin
+    smoothers = [Jacobi!,GS!,SOR!,pseudo!]
+    suite = BenchmarkGroup()
+    A,b = TunedSmoother.static(;n=64,T=Float64)
+    for s ∈ smoothers
+        suite[s] = @benchmarkable mg!(st;mxiter=1,smooth! = $s) setup=(st=state($A,$b))
+    end
+end
+results = run(suite)
+time_factor = [minimum(results[s]).time/minimum(results[Jacobi!]).time for s ∈ smoothers[2:end]]
+
+begin
+    itcount(d,s;kw...) = mg!(state(d...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
+    avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
+end
+data = create_synthetic(;n=64)
+counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
+
+begin # inner=2
+    time_factor = [ 2.5587099273183047
+                    2.6826817316441263
+                    1.3066736339751297]   
+    counts = [ 3.0  4.0  1.64  1.3   3.9   3.6
+                4.0  3.0  1.68  1.28  3.95  3.0
+                3.0  3.0  1.14  1.28  3.23  3.84]
+    counts.*time_factor
+end
+
+begin
+    using StatsPlots,CategoricalArrays
+    cats = ["Gauss-Sidel","SOR","Ã⁻¹ union"]
+    n = length(data)
+    colors = repeat([palette(:default)[2],palette(:default)[4],palette(:default)[3]],inner=n)
+    ctg = CategoricalArray(repeat(cats,inner=n))
+    levels!(ctg,cats)
+    groupedbar((counts.*time_factor)',size=(400,400),
+                group=ctg, legend=:bottomright,c=colors,
+                yaxis=("relative time"),
+                xaxis=("cases",(1:n,keys(data)),60))
+end
+savefig("synthetic_timing.png")

### 2021-09-30 src/benchmark.jl

@@ -1,48 +1,0 @@
-using LinearAlgebra, GeometricMultigrid, BenchmarkTools, Plots
-
-begin
-    include("candidate_smoothers.jl")
-    smoothers = [Jacobi!,GS!,SOR!,pseudo!]
-end
-begin
-    include("create_synthetic.jl")
-    suite = BenchmarkGroup()
-    A,b = static(;n=128,T=Float32)
-    for s ∈ smoothers
-        suite[s] = @benchmarkable mg!(st;mxiter=1,inner=2,smooth! = $s) setup=(st=mg_state($A,zero($b),$b,pseudo=true))
-    end
-end
-results = run(suite)
-time_factor = [minimum(results[s]).time/minimum(results[Jacobi!]).time for s ∈ [2:end]]
-begin
-    time_factor = [2.01557, 2.61135, 1.36815]
-end
-
-begin
-    include("create_synthetic.jl")
-    data = create_synthetic()
-end
-begin
-    itcount(A,b,s) = mg!(mg_state(A,zero(b),b,pseudo=true);reltol=1e-3,inner=2,smooth! = s,mxiter=32)
-    avecount(data,s) = sum(itcount(d...,s) for d ∈ data)/length(data)
-    counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
-end
-begin
-    counts = [ 3.0  3.0  2.64  2.33  3.65  3.08
-                3.0  4.0  2.53  2.5   3.05  3.92
-                3.0  3.0  1.88  2.27  3.17  3.0]
-end
-
-begin
-    using StatsPlots,CategoricalArrays
-    cats = ["Gauss-Sidel","SOR","Ã⁻¹ union"]
-    n = length(data)
-    colors = repeat([palette(:default)[2],palette(:default)[4],palette(:default)[3]],inner=n)
-    ctg = CategoricalArray(repeat(cats,inner=n))
-    levels!(ctg,cats)
-    groupedbar((counts.*time_factor)',size=(400,400),
-                group=ctg, legend=:bottomright,c=colors,
-                yaxis=("relative time"),
-                xaxis=("cases",(1:n,keys(data)),60))
-end
-savefig("synthetic_scaling.png")

### 2021-09-30 benchmark.jl
Fixed up tune_synthetic

@@ -11,10 +11,6 @@ end
 results = run(suite)
 time_factor = [minimum(results[s]).time/minimum(results[Jacobi!]).time for s ∈ smoothers[2:end]]
 
-begin
-    itcount(d,s;kw...) = mg!(state(d...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
-    avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
-end
 data = create_synthetic(;n=64)
 counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
 

### 2021-09-30 src/TunedSmoother.jl

@@ -9,4 +9,7 @@ export create_synthetic
 include("create_waterlily.jl")
 export create_waterlily
 
+include("metrics.jl")
+export avecount,loss,fit
+
 end # module

### 2021-09-30 src/candidate_smoothers.jl

@@ -23,13 +23,13 @@ function PseudoInv(A::FieldMatrix; scale=maximum(A.L),
     p::AbstractVector{T}=Float32[-0.1449,-0.0162,0.00734,0.3635,-0.2018],
     models=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5]))) where T
 
-    L,D,N = zeros(T,size(A.L)),zeros(T,size(A.D)),size(A.L)[end]
+    L,D,N = zeros(T,size(A.L)),zeros(T,size(A.D)),length(size(A.D))
     Dm,Lm = models(p)
     for I ∈ A.R
         invD = (abs(A.D[I])<1e-8) ? 0. : 1.0/A.D[I]
         D[I] = invD*Dm(A.D[I]/scale)
         for i ∈ 1:N
-            J = I#-δ(i,N)
+            J = I-δ(i,N)
             invD = (abs(A.D[I]+A.D[J])<2e-8) ? 0. : 2.0/(A.D[I]+A.D[J])
             L[I,i] = invD*Lm(A.L[I,i]/scale)
         end

### 2021-09-30 src/metrics.jl

@@ -1,0 +1,14 @@
+# count average V-cycles to get reltol 1e-3
+itcount(d,s;kw...) = mg!(state(d...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
+avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
+
+# measure average residual reduction after it V-cycles
+Δresid(st;it=1,kw...) = (resid = mg!(st;mxiter=it,log=true,kw...);
+                        log10(resid[end]/resid[1])/it)
+loss(data;p=p₀,kw...) = sum(Δresid(state(d...;p);kw...) for d ∈ data)/length(data)
+
+# optimize parameters to minimize loss
+using Optim
+fit(data,p₀=zeros(Float32,5);smooth! = pseudo!,kw...) = Optim.minimizer(
+    optimize(p->loss(data;p,smooth!,kw...),p₀, Newton(),
+    Optim.Options(time_limit=60,show_trace=true); autodiff = :forward))

### 2021-09-30 src/tune_synthetic.jl

@@ -1,114 +1,0 @@
-using GeometricMultigrid, Plots, Printf, Optim
-
-# create synthetic example systems
-begin
-    include("create_synthetic.jl")
-    data = make_data()
-end
-
-# measure loss against examples
-begin
-    fill_pseudo!(st;kw...) = fill_pseudo!(st,st.child;kw...)
-    fill_pseudo!(st,child;kw...) = (fill_pseudo!(st,nothing;kw...);fill_pseudo!(child;kw...))
-    fill_pseudo!(st,::Nothing;kw...) = st.P=PseudoInv(st.A;kw...)
-
-    function predict(A,b;p::AbstractVector{T},kw...) where T
-        st = mg_state(A,zero(b,T),b)
-        fill_pseudo!(st;p,kw...)
-        h = mg!(st,mxiter=1,inner=2,log=true)
-        log10(h[2]/h[1])
-    end
-    loss(data;kw...) = sum(predict(d...;kw...) for d ∈ data)/length(data)
-end
-
-# optimize psuedo-inverse functions
-begin
-    models=p->(D->1+p[1]+D*(p[2]+D*p[3]),
-               L->       L*(p[4]+L*p[5]))
-    fit(data,models,p₀=zeros(Float32,5)) = 
-        Optim.minimizer(optimize(p->loss(data;p,models),p₀, Newton(); autodiff = :forward))
-
-    opt = OrderedDict(name=>fit(train,models) for (name,train) ∈ data)
-    opt["union"] = fit(vcat((d for (_,d) in data)...),models)
-    # opt["jacobi"] = zeros(Float32,5)
-    opt
-end
-begin
-    opt = OrderedDict(
-        "2D-static" => [-2.36056, -1.40822, -0.203578, 0.271696, -5.47975f-7],
-        "3D-static" => [0.206214, 0.0214632, -0.00525863, 0.315253, 0.0135281],
-        "2D-dipole" => [-1.71116, -0.902871, -0.114227, 0.166726, 3.14462f-7],
-        "3D-dipole" => [-0.663327, -0.199177, -0.00915381, 0.149958, -1.54752f-7],
-        "2D-sphere" => [-0.003891, 0.047247, 0.0149267, 0.377898, -0.217221],
-        "3D-sphere" => [-0.0966329, -0.0967704, -0.00862894, 0.432134, -0.271047],
-        "union"  => [-0.144944, -0.0162348, 0.00734042, 0.363533, -0.201831])
-end
-
-# compare across example types
[…]

### 2021-09-30 tune_synthetic.jl

@@ -1,0 +1,67 @@
+using TunedSmoother, Plots, DataStructures
+using GeometricMultigrid: mg!
+
+# create synthetic example systems
+begin
+    data = make_data()
+    opt = OrderedDict(name=>zeros(Float32,5) for name ∈ keys(data))
+    opt["union"] = zeros(Float32,5)
+end
+
+# optimize Parameterized smoother
+begin
+    for (name,train) ∈ data
+        @show name
+        opt[name] = fit(train,opt[name])
+    end
+    @show "union"
+    opt["union"] = fit(vcat((d for (_,d) in data)...),opt["union"])
+    opt
+end
+begin
+    # opt = OrderedDict(
+    #     "2D-static" => [-2.36056, -1.40822, -0.203578, 0.271696, -5.47975f-7],
+    #     "3D-static" => [0.206214, 0.0214632, -0.00525863, 0.315253, 0.0135281],
+    #     "2D-dipole" => [-1.71116, -0.902871, -0.114227, 0.166726, 3.14462f-7],
+    #     "3D-dipole" => [-0.663327, -0.199177, -0.00915381, 0.149958, -1.54752f-7],
+    #     "2D-sphere" => [-0.003891, 0.047247, 0.0149267, 0.377898, -0.217221],
+    #     "3D-sphere" => [-0.0966329, -0.0967704, -0.00862894, 0.432134, -0.271047],
+    #     "union"  => [-0.144944, -0.0162348, 0.00734042, 0.363533, -0.201831])
+    opt = OrderedDict(
+        "2D-static" => Float32[-2.46273, -1.32142, -0.175033, 0.145184, 0],
+        "3D-static" => Float32[0.93542, 0.210713, 0.00503395, 0.309537, 0.0135281],
+        "2D-dipole" => Float32[-2.56297, -1.41248, -0.188902, 0.163554, 0],
+        "3D-dipole" => Float32[-0.752343, -0.258171, -0.0168188, 0.145254, 0],
+        "2D-sphere" => Float32[0.0406717, 0.0436037, 0.0111401, 0.470527, -0.310894],
+        "3D-sphere" => Float32[-0.0483643, -0.0815794, -0.00751761, 0.54353, -0.381655],
+        "union"     => Float32[-0.100887, -0.00164709, 0.00833292, 0.418425, -0.260235])
+end
+
+# compare across example types
+crossloss = [loss(test;p,smooth! = pseudo!) for (_,p) ∈ opt, (_,test) ∈ data]
+begin
[…]

### 2021-10-01 benchmark.jl
Update benchmark with new union parameters

@@ -15,12 +15,12 @@ data = create_synthetic(;n=64)
 counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
 
 begin # inner=2
-    time_factor = [ 2.5587099273183047
-                    2.6826817316441263
-                    1.3066736339751297]   
-    counts = [ 3.0  4.0  1.64  1.3   3.9   3.6
-                4.0  3.0  1.68  1.28  3.95  3.0
-                3.0  3.0  1.14  1.28  3.23  3.84]
+    time_factor = [ 2.397728501892915
+                    2.5168063818280153
+                    1.3297458085451594]   
+    counts = [ 3.0  4.0  1.5   1.17  3.88  3.55
+                4.0  3.0  1.55  1.16  3.96  3.0
+                3.0  3.0  1.07  1.14  3.18  3.0]
     counts.*time_factor
 end
 

### 2021-10-01 src/candidate_smoothers.jl

@@ -42,7 +42,7 @@ fill_pseudo!(st;kw...) = fill_pseudo!(st,st.child;kw...)
 fill_pseudo!(st,child;kw...) = (fill_pseudo!(st,nothing;kw...);fill_pseudo!(child;kw...))
 fill_pseudo!(st,::Nothing;kw...) = st.P=PseudoInv(st.A;kw...)
 
-p₀ = Float32[-0.1449,-0.0162,0.00734,0.3635,-0.2018] # result from tune_synthetic
+p₀ = Float32[-0.100887, -0.00164709, 0.00833292, 0.418425, -0.260235] # result from tune_synthetic
 function state(A,x,b;p=p₀,xT::Type=eltype(p),kw...)
     y = zero(x,xT)     # make FieldVector of type xT
     @loop y[I] = x[I]  # copy values

### 2021-10-01 tex/article.tex

@@
 Pressure projection is a bottleneck in high-speed unsteady incompressible flow solvers.
-The pressure projection step typically makes up 25-50\% of the solution cost even in serial simulations, and the proportional cost grows in massively parallel simulations as the elliptic pressure Poisson equation requires communication throughout the computational domain instead of being confined to a local characteristic.
+Constructing approximate solutions the discrete pressure Poisson system typically makes up 25-50\% of the solution cost even in serial simulations, and the proportional cost grows in massively parallel simulations as the elliptic equation requires communication throughout the computational domain instead of being confined to a local characteristic.
 Methods such as artificial-compressibility, smooth-particle-hydrodynamics, and particle-in-cell attempt to side-step this computational cost by modelling or otherwise under-resolving the pressure evolution compared to the fluid's momentum.
@@
 
-However, the pressure projection in these all of these studies have not been augmented, leaving their acceleration as a nearly untouched topic.
+However, none of these studies have applied data-driven techniques to accelerate the critical projection step itself.
 Some recent work has focused on the pressure projection step explicitly.
@@
 
-The discrete Poisson equation at the heart of the projection step is defined as
+The discrete Poisson equation in the projection step is defined as
 \begin{equation}\label{eq:axb}
@@
 As the problem is linear, the equation for the update $\epsilon$ is simply
-\begin{equation}
+\begin{equation}\label{eq:aer} 
     A \epsilon^k = r^k \equiv b - Ax^k
@@
 
-The linearity of the system is a critical property which the data-driven method must maintain, but this linearity is only with respect to the update and residual fields.
-The coefficients of the ``MG network'' can all potentially be optimized for a specific sub-class of problems, and they can be made nonlinear functions of $A$.
-However, neither the restriction or prolongation operations are functions of $A$, and a workable method of including the dependence is unclear.\footnote{For example, the residual restriction could use $a_{ij}$ to define a non-uniform weight function $w_{ij} = r_i/r_j$, but since the matrix is symmetric the same weight should apply to $r_j/r_i$, resulting in a uniform pooling.} Similarly, a simple Jacobi preconditioner
+The linearity of equation \ref{eq:aer} is a critical property which the data-driven method must maintain in order to be useful in practise, but this linearity is only with respect to the update and residual fields.
+The operators of the ``MG network'' can all potentially be optimized for a specific sub-class of problems.
+In particular, those operators can be made into parameterized nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions, without violating linearity.
+
+Which MG operation is the best candidate for such an approach?
+The prolongation operator (restriction simply being its transpose) is not inherently a function of $A$, and while related super-resolution operators have seen improvements in the literature, these are always nonlinear functions of the field.
+The precondition operator is an option, but a simple Jacobi preconditioner
 \begin{equation}
@@
 There are few constraints on $\tilde A^{-1}$: it must have units of $A^{-1}$, and symmetry of $A$ implies the approximate inverse should also be symmetric.
-For simplicity, the diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are all constructed independently
+For simplicity, the diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are constructed independently
 \begin{equation}
-    \tilde a^{-1}_{ii} = \frac{f_D(a_{ii}/s\,|\theta_D)}{a_{ii}} , \quad
-    \tilde a^{-1}_{ij} = \frac{f_L(a_{ij}/s\,|\theta_L)}{a_{ii}+a_{jj}}
+    \tilde a^{-1}_{ii} = \frac{f_d(a_{ii}/s\,|\theta_d)}{a_{ii}} , \quad
+    \tilde a^{-1}_{ij} = \frac{f_o(a_{ij}/s\,|\theta_o)}{a_{ii}+a_{jj}}
 \end{equation}
-where function inputs are scaled by the maximum off-diagonal $s=\max(A-D)$ and the outputs are scaled by the diagonal elements. Note a Jacobi smoother would use $f_D=1$ and $f_L=0$.
+where function inputs are scaled by the maximum off-diagonal $s=\max(A-D)$ and the outputs are scaled by the diagonal elements.
+Note a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal $f_o=0$.
 
@@
         \includegraphics[width=\textwidth]{figures/crossloss.png}
-        \caption{$\log_{10}$ residual reduction}
+        \caption{single-cycle residual reduction}
         \label{fig:cross plot}
@@
         \centering
-        \includegraphics[width=\textwidth]{figures/crosscount.png}
-        \caption{Solver time}
+        \includegraphics[width=\textwidth]{figures/synthetic_timing.png}
+        \caption{solver time}
         \label{fig:synthetic time}
@@
 The three 2D cases are show in Figure~\ref{fig:2D-box}-\ref{fig:2D-sphere}, and each has a matching 3D case.
-The `box' cases have a simple constant gradient solution throughout the domain, with the direction and magnitude randomized.
-The dipole `$\mu$' cases have a localized dipole within a quiescent flow with randomized placement, direction and magnitude.
+The `static' cases have a simple hydro-static gradient solution throughout the domain, with the direction and magnitude randomized.
+The `dipole' cases have a localized dipole within a quiescent flow with randomized placement, direction and magnitude.
 The `sphere' cases have a moving sphere immersed within a quiescent flow with randomized radius, location, and velocity direction.
@@
 As expected, the performance is best when testing and training on the same case, with the residual reduced by $10^{-1.18}$ on the 2D-sphere case down to $10^{-1.75}$ on the 2D-box case.
-The performance for the simplest `box' and 2D-$\mu$ cases generalizes poorly, with some cases diverging instead converging, but the optimized 2D-sphere smoother generalizes essentially as well as the `union' smoother trained on all of the data.
+While the performance for the simplest cases generalizes poorly, the 2D-sphere smoother generalizes essentially as well as the `union' smoother trained on all of the data.
 %The performance of the `union' smoother is only 1-4\% lower than the smoother trained on the test case for the dipole and sphere cases.
+
+Figure~\ref{fig:synthetic time} characterizes the acceleration achieved by the data-driven smoother using the time taken to reduce the residual of each case by $10^{-3}$, scaled by the time to run a single V-cycle using a Jacobi smoother.
+The results for the Jacobi smoother are not given, since thousands of iterations are required.
+Remarkably, the Jacobi-like parameterized smoother is only 36\% slower per iteration, and yet converges in only a few V-cycles.
+This results in a 80-175\% speed up relative to optimized serial Gauss-Sidel and SOR smoothers, and the speed-up will be even more favorable in parallel computation.
 
@@
     \end{subfigure}
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.47\textwidth}
         \begin{subfigure}{\textwidth}
@@
     \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{0.47\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/compareloss.png}
-        \caption{$\log_{10}$ residual reduction}
-        \label{fig:synthetic time}
+        \caption{single-cycle residual reduction}
+        \label{fig:simulation residual}
     \end{subfigure}
@@
     \centering
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.47\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{figures/scaleloss.png}
-        \caption{$\log_{10}$ residual reduction}
+        \includegraphics[width=\textwidth]{figures/diag_fun.png}
+        \caption{diagonal functions}
         \label{fig:scaled loss}
@@
     \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/lower_fun.png}
+        \caption{off-diagonal functions}
+        \label{fig:simulation time}
+    \end{subfigure}
+        \caption{(a) Diagonal and (b) off-diagonal parameterized functions after optimization on each simulation case.
+The `transfer' smoother was tuned on the synthetic cases and `Jacobi' is shown for comparison.}
+        \label{fig:tuned simulation}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/scaleloss.png}
+        \caption{single-cycle residual reduction}
+        \label{fig:scaled loss}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.47\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/crosscount.png}
-        \caption{Solver time}
+        \caption{solver time}
         \label{fig:simulation time}

### 2021-10-01 benchmark.jl
change crossloss colorsheme and add a few calcs

@@ -14,6 +14,8 @@ time_factor = [minimum(results[s]).time/minimum(results[Jacobi!]).time for s ∈
 data = create_synthetic(;n=64)
 counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
 
+jacobicount = [itcount(d[1],Jacobi!,reltol=1) for (name,d) ∈ data]
+
 begin # inner=2
     time_factor = [ 2.397728501892915
                     2.5168063818280153
@@ -21,7 +23,8 @@ begin # inner=2
     counts = [ 3.0  4.0  1.5   1.17  3.88  3.55
                 4.0  3.0  1.55  1.16  3.96  3.0
                 3.0  3.0  1.07  1.14  3.18  3.0]
-    counts.*time_factor
+    rel_time = counts.*time_factor
+    accel = rel_time[1:2,:]./rel_time[3,:]' # speed up!!
 end
 
 begin

### 2021-10-01 tune_synthetic.jl

@@ -53,8 +53,8 @@ using Plots.PlotMeasures
 begin
     lim = maximum(abs.(crossloss))
     names(d) = (1:length(d),keys(d))
-    plot(size=(400,370))
-    display(heatmap!(crossloss',c=:RdBu_9,clims=(-lim,lim),
+    plot(size=(400,350))
+    display(heatmap!(crossloss',c=palette([:green,:white,:red],13),clims=(-lim,lim),
             title="log₁₀ residual reduction",titlefontsize=12,
             xaxis=("train",names(opt),60),yaxis=("test",names(data),:flip)))
 end

### 2021-10-01 tex/article.tex

@@
 Multi-grid data-driven decomposition; high errors and unclear speed-up.
-This work links develops a high-speed parameterized smoother which outperforms classic smoothing methods on eleven 2D and 3D benchmarks.
-Moreover, as the approach in linear in the pressure and scale-invariant, the parameters can be tuned on a coarse simulation and maintain their accelerated performance on the fine simulation.
+This work develops a high-speed data-driven project method which outperforms classic methods on eleven 2D and 3D benchmarks.
+Moreover, as the approach in linear in the pressure and scale-invariant, the parameters can be tuned on a coarse simulation and maintain their accelerated performance on unseen fine-grid simulations.
 
@@
 The operators of the ``MG network'' can all potentially be optimized for a specific sub-class of problems.
-In particular, those operators can be made into parameterized nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions, without violating linearity.
+In particular, those operators can be made into parameterized nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
 
@@
 where function inputs are scaled by the maximum off-diagonal $s=\max(A-D)$ and the outputs are scaled by the diagonal elements.
-Note a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal $f_o=0$.
+Note a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal function $f_o=0$.
+With the learning problem now reduced to two scaled single-variable functions, the specific choice of parameterization is not critical and a simple quadratic polynomial $f(a) = \sum_{p=0}^2 a^p \theta_p$ is chosen for $f_o$ and $f_d$.
+Using higher-order polynomials, splines, and interpolating kernels did not significantly change the results.
 
@@
 and determined using Newton's method.
-The ForwardDiff.jl AD package is used determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ automatically.
-The adaptive and recursive nature of the MG V-cycle and general nonlinear form of $f$ would make analytic derivatives prohibitively unwieldy and error prone, and numerical finite differences potentially unstable and inaccurate.
+The ForwardDiff.jl AD package is used determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ automatically, avoiding inaccurate and potentially unstable finite differences of the nonlinear recursive loss function.
 
@@
 The three 2D cases are show in Figure~\ref{fig:2D-box}-\ref{fig:2D-sphere}, and each has a matching 3D case.
-The `static' cases have a simple hydro-static gradient solution throughout the domain, with the direction and magnitude randomized.
+The `static' cases have a hydrostatic gradient throughout the domain, with the direction and magnitude randomized.
 The `dipole' cases have a localized dipole within a quiescent flow with randomized placement, direction and magnitude.
 The `sphere' cases have a moving sphere immersed within a quiescent flow with randomized radius, location, and velocity direction.
+All cases are initialized with $x^0=0$.
+%, and all cases feature initially localized residuals; i.e.
+$r^0\ne0$ only in a fraction of the cells, but $x$ must be updated throughout the domain, starkly illustrating the elliptic nature of the projection step.
 Neumann boundary conditions are applied on all boundaries, including the immersed sphere, through adjustment of the $A$ matrix coefficients which are otherwise uniform.
-All cases are initialized with $x^0=0$, and all cases feature initially localized residuals; i.e.
-$r^0\ne0$ only in a fraction of the cells, but $x$ must be updated throughout the domain, starkly illustrating the elliptic nature of the projection step.
 
-Figure~\ref{fig:cross plot} shows the `test' performance of the parameterized smoother over a single V-cycle on 100 randomized examples after optimization using 100 examples of the `test' case.
-Each example uses a grid size of n=32 point in each direction ($N=32^2$ in 2D and $N=32^3$ in 3D) as testing with other resolutions found essentially no change in the performance.
-As expected, the performance is best when testing and training on the same case, with the residual reduced by $10^{-1.18}$ on the 2D-sphere case down to $10^{-1.75}$ on the 2D-box case.
+Figure~\ref{fig:cross plot} characterizes the generalization of the parameterized smoother's residual reduction over a single V-cycle on 100 randomized `test' case examples after optimization using 100 examples of the `train' case.
+Each example uses a grid size of $n=32^M$ points ($N=32^2$ in 2D and $N=32^3$ in 3D) as testing with other resolutions found essentially no change in the performance.
+As expected, the performance is best when testing and training on the same case, with a single V-cycle reducing the residual from $10^{-1.17}$ on the 2D-sphere case down to $10^{-1.58}$ on the 3D-box case.
 While the performance for the simplest cases generalizes poorly, the 2D-sphere smoother generalizes essentially as well as the `union' smoother trained on all of the data.
@@
 
-Figure~\ref{fig:synthetic time} characterizes the acceleration achieved by the data-driven smoother using the time taken to reduce the residual of each case by $10^{-3}$, scaled by the time to run a single V-cycle using a Jacobi smoother.
-The results for the Jacobi smoother are not given, since thousands of iterations are required.
-Remarkably, the Jacobi-like parameterized smoother is only 36\% slower per iteration, and yet converges in only a few V-cycles.
-This results in a 80-175\% speed up relative to optimized serial Gauss-Sidel and SOR smoothers, and the speed-up will be even more favorable in parallel computation.
+Finally, the acceleration of the `union' data-driven smoother is evaluated on new example data of a different size, $n=64^M$ points.
+Figure~\ref{fig:synthetic time} shows the time to reduce the residual of each case by $10^{-3}$ relative to the time to run a single V-cycle using a Jacobi smoother, but the results for the Jacobi smoother are not shown since hundreds or even thousands of V-cycles are required to converge.
+Remarkably, the Jacobi-like parameterized smoother is only around 33\% slower per V-cycle, and yet converges in only 1-3 V-cycles in all cases.
+This results in a 80-175\% speed up relative to optimized serial Gauss-Sidel and SOR smoothers.
+This speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any need for additional communication.
 

### 2021-10-01 benchmark.jl
Add synthetic snapshots

@@ -1,4 +1,4 @@
-using BenchmarkTools, Plots, GeometricMultigrid, TunedSmoother
+using BenchmarkTools, Plots, TunedSmoother
 
 begin
     smoothers = [Jacobi!,GS!,SOR!,pseudo!]

### 2021-10-01 src/TunedSmoother.jl

@@ -7,9 +7,9 @@ include("create_synthetic.jl")
 export create_synthetic
 
 include("create_waterlily.jl")
-export create_waterlily
+export create_waterlily,circle,TGV,donut,wing,shark
 
 include("metrics.jl")
-export avecount,loss,fit
+export itcount,avecount,loss,fit,mg!
 
 end # module

### 2021-10-01 src/metrics.jl

@@ -1,3 +1,6 @@
+using GeometricMultigrid: mg!
+using Optim
+
 # count average V-cycles to get reltol 1e-3
 itcount(d,s;kw...) = mg!(state(d...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
 avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
@@ -8,7 +11,6 @@ avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
 loss(data;p=p₀,kw...) = sum(Δresid(state(d...;p);kw...) for d ∈ data)/length(data)
 
 # optimize parameters to minimize loss
-using Optim
 fit(data,p₀=zeros(Float32,5);smooth! = pseudo!,kw...) = Optim.minimizer(
     optimize(p->loss(data;p,smooth!,kw...),p₀, Newton(),
     Optim.Options(time_limit=60,show_trace=true); autodiff = :forward))

### 2021-10-01 tune_synthetic.jl

@@ -65,3 +65,13 @@ savefig("crossloss.png")
 #     i+2>length(y) && return y[end]
 #     y[i+2]*dx+y[i+1]*(1-dx)
 # end
+
+using GeometricMultigrid: mg, @loop
+data = create_synthetic(len=1)
+for name in ["2D-static", "2D-dipole", "2D-sphere"]
+    A,b = data[name][1]
+    x,hist = mg(A,b)
+    name == "2D-sphere" && (@loop x[I] *= -4*A.D[I])
+    heatmap(x.data[x.R],size = (250,250),legend=false,axis=nothing)
+    savefig(name*".png")
+end

### 2021-10-01 tex/article.tex

@@
 Note a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal function $f_o=0$.
-With the learning problem now reduced to two scaled single-variable functions, the specific choice of parameterization is not critical and a simple quadratic polynomial $f(a) = \sum_{p=0}^2 a^p \theta_p$ is chosen for $f_o$ and $f_d$.
+With the learning problem now reduced to two normalized single-variable functions, the specific choice of parameterization is not critical and a simple quadratic polynomial $f(a) = \sum_{p=0}^2 a^p \theta_p$ is chosen for $f_o$ and $f_d$.
 Using higher-order polynomials, splines, and interpolating kernels did not significantly change the results.
@@
 A set of six synthetic projection cases were constructed to establish the characteristics of the parameterized smoother.
-The three 2D cases are show in Figure~\ref{fig:2D-box}-\ref{fig:2D-sphere}, and each has a matching 3D case.
+The three 2D cases are shown in Figure~\ref{fig:2D-box}-\ref{fig:2D-sphere}, and each has a matching 3D case.
 The `static' cases have a hydrostatic gradient throughout the domain, with the direction and magnitude randomized.
@@
 Remarkably, the Jacobi-like parameterized smoother is only around 33\% slower per V-cycle, and yet converges in only 1-3 V-cycles in all cases.
-This results in a 80-175\% speed up relative to optimized serial Gauss-Sidel and SOR smoothers.
+This results in a 80-175\% speed-up relative to optimized serial Gauss-Sidel and SOR smoothers.
 This speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any need for additional communication.

### 2021-10-02 benchmark.jl
update benchmark

@@ -1,40 +1,43 @@
 using BenchmarkTools, Plots, TunedSmoother
+using GeometricMultigrid: Vcycle!
 
+data = create_synthetic(;n=64)
 begin
     smoothers = [Jacobi!,GS!,SOR!,pseudo!]
     suite = BenchmarkGroup()
-    A,b = TunedSmoother.static(;n=64,T=Float64)
-    for s ∈ smoothers
-        suite[s] = @benchmarkable mg!(st;mxiter=1,smooth! = $s) setup=(st=state($A,$b))
+    for s ∈ smoothers, (name,d) ∈ data
+        suite[name,s] = @benchmarkable Vcycle!(st;smooth! = $s) setup=(st=state($d[1]...))
     end
 end
-results = run(suite)
-time_factor = [minimum(results[s]).time/minimum(results[Jacobi!]).time for s ∈ smoothers[2:end]]
+begin # run benchmarks and count iterations
+    results = run(suite)
+    times = [minimum(results[name,s]).time for s ∈ smoothers, name ∈ keys(data)]
+    time_factor = times[2:end,:]./times[1,:]'
+    counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
+end
 
-data = create_synthetic(;n=64)
-counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
-
-jacobicount = [itcount(d[1],Jacobi!,reltol=1) for (name,d) ∈ data]
-
-begin # inner=2
+begin # results from block above
+    time_factor = [ 2.26743  2.29541  2.25677  2.24512  2.27092  2.30344
+                    2.87374  2.46019  2.86748  2.52186  2.87211  2.44708
+                    1.37096  1.56152  1.36767  1.54179  1.36671  1.54011]
     time_factor = [ 2.397728501892915
                     2.5168063818280153
-                    1.3297458085451594]   
-    counts = [ 3.0  4.0  1.5   1.17  3.88  3.55
+                    1.3297458085451594]
+    counts = [ 3.0  4.0  1.5   1.17  3.98  3.55
                 4.0  3.0  1.55  1.16  3.96  3.0
                 3.0  3.0  1.07  1.14  3.18  3.0]
     rel_time = counts.*time_factor
     accel = rel_time[1:2,:]./rel_time[3,:]' # speed up!!
 end
 
-begin
+begin # plot
     using StatsPlots,CategoricalArrays
[…]

### 2021-10-02 tex/article.tex
Updates from Overleaf

@@
 
-\title{Auto-tuned Jacobi-like Multi-grid Smoother\\ for Fast Pressure Projection}
+\title{Auto-tuned Multi-grid Solver for Accelerated \\ Pressure Projection}
 
@@
 Required to maintain linearity in pressure, the best option for data-driven acceleration is in the smoothing step.
-Using automatic differentiation, a high-speed parameterized smoother is developed which outperforms classic Multi-grid methods by 66-200\% on eleven 2D and 3D benchmarks.
+Using automatic differentiation, a high-speed parameterized smoother is developed which out-performs classic Multi-grid methods by 66-185\% on eleven 2D and 3D benchmarks.
 The tuned parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of any flow.
@@
 
-\section{Data-driven Accelerated Solution Methods}
+\section{Data-driven Accelerated Projection Method}
 
@@
 While more complex options are certainly possible, this work uses a simple parameterized Jacobi-like smoother
-\begin{equation}
+\begin{equation}\label{eq:smooth}
     \epsilon = \tilde A^{-1}r
@@
 %The matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be computed and stored ahead of time.
+As with all stationary smoothers, equation \ref{eq:smooth} can be iterated (an inner loop) at each MG level.
 Unlike Gauss-Sidel or SOR smoothers, the matrix-vector multiplication smoother requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
@@
 For simplicity, the diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are constructed independently
-\begin{equation}
+\begin{equation}\label{eq:approxinv}
     \tilde a^{-1}_{ii} = \frac{f_d(a_{ii}/s\,|\theta_d)}{a_{ii}} , \quad
@@
 
-Automatic differentiation (AD) is used to optimize the parameterized smoother for a set of training data $X=\{A,x^k,b\}$.
+The parameterized smoother is optimized for a set of training data $X=\{A,x^k,b\}$.
 The loss function is simply the reduction in the norm of the residual after a V-cycle iteration $L = \log_{10}(|r^{k+1}| / |r^{k}|)$, which means that example pressure \textit{solutions} are not required.
@@
 and determined using Newton's method.
-The ForwardDiff.jl AD package is used determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ automatically, avoiding inaccurate and potentially unstable finite differences of the nonlinear recursive loss function.
+Automatic differentiation (AD) is used to determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$, avoiding inaccurate and potentially unstable finite differences of the nonlinear recursive loss function.
+
+The data-driven solver and all the test cases and figures presented in the following sections are implemented in Julia and available for reproduction.
 
@@
         \centering
-        \caption{2D-box}
-        \label{fig:2D-box}
+        \includegraphics[width=\textwidth]{figures/2D-static.png}
+        \caption{2D-static}
+        \label{fig:2D-static}
     \end{subfigure}
@@
         \centering
-        \caption{2D-$\mu$}
+        \includegraphics[width=\textwidth]{figures/2D-dipole.png}
+        \caption{2D-dipole}
         \label{fig:2D-mu}
@@
         \centering
+        \includegraphics[width=\textwidth]{figures/2D-sphere.png}
         \caption{2D-sphere}
@@
     \end{subfigure}
+    \caption{Sample solutions from the data-sets of three of the six synthetic cases.}
+    \label{fig:synthetic cases}
+\end{figure}
+\begin{figure}
+    \centering
     \begin{subfigure}[b]{0.47\textwidth}
@@
     \end{subfigure}
-    \caption{(a-c) Sample solutions from the data-sets of three of the six synthetic cases.
-(d) Residual reduction over a single Multi-grid V-cycle on the `test' cases after tuning using the `train' case.
+    \caption{a) Residual reduction over a single Multi-grid V-cycle on the `test' cases after tuning using the `train' case.
 Training case `union' refers to the smoother trained on all of the synthetic cases.
@@
 Time is relative to the time of a single V-cycle using the Jacobi smoother.}
-    \label{fig:synthetic cases}
+    \label{fig:synthetic results}
 \end{figure}
 
-\section{Synthetic Projection Systems and Results}
+\section{Synthetic Discrete Poisson System Results}
 
 A set of six synthetic projection cases were constructed to establish the characteristics of the parameterized smoother.
-The three 2D cases are shown in Figure~\ref{fig:2D-box}-\ref{fig:2D-sphere}, and each has a matching 3D case.
+The three 2D cases are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
 The `static' cases have a hydrostatic gradient throughout the domain, with the direction and magnitude randomized.
-The `dipole' cases have a localized dipole within a quiescent flow with randomized placement, direction and magnitude.
-The `sphere' cases have a moving sphere immersed within a quiescent flow with randomized radius, location, and velocity direction.
+The `dipole' and `sphere' cases have a randomized dipole/sphere within a quiescent flow.
 All cases are initialized with $x^0=0$.
@@
 $r^0\ne0$ only in a fraction of the cells, but $x$ must be updated throughout the domain, starkly illustrating the elliptic nature of the projection step.
-Neumann boundary conditions are applied on all boundaries, including the immersed sphere, through adjustment of the $A$ matrix coefficients which are otherwise uniform.
+Neumann boundary conditions are applied on all boundaries, including the boundary of the immersed sphere, through adjustment of the $A$ matrix coefficients which are otherwise uniform.
 
@@
 Each example uses a grid size of $n=32^M$ points ($N=32^2$ in 2D and $N=32^3$ in 3D) as testing with other resolutions found essentially no change in the performance.
+Two inner loops are used throughout to optimize residual reduction.
 As expected, the performance is best when testing and training on the same case, with a single V-cycle reducing the residual from $10^{-1.17}$ on the 2D-sphere case down to $10^{-1.58}$ on the 3D-box case.
 While the performance for the simplest cases generalizes poorly, the 2D-sphere smoother generalizes essentially as well as the `union' smoother trained on all of the data.
-%The performance of the `union' smoother is only 1-4\% lower than the smoother trained on the test case for the dipole and sphere cases.
 
 Finally, the acceleration of the `union' data-driven smoother is evaluated on new example data of a different size, $n=64^M$ points.
-Figure~\ref{fig:synthetic time} shows the time to reduce the residual of each case by $10^{-3}$ relative to the time to run a single V-cycle using a Jacobi smoother, but the results for the Jacobi smoother are not shown since hundreds or even thousands of V-cycles are required to converge.
-Remarkably, the Jacobi-like parameterized smoother is only around 33\% slower per V-cycle, and yet converges in only 1-3 V-cycles in all cases.
-This results in a 80-175\% speed-up relative to optimized serial Gauss-Sidel and SOR smoothers.
+Figure~\ref{fig:synthetic time} shows the time to reduce the residual of each case by $10^{-3}$ relative to the time to run a single V-cycle using a Jacobi smoother.
+While a Jacobi smoother take  hundreds or even thousands of V-cycles to converge, the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, and yet converges in only 1-3 V-cycles in all cases.
+This results in a 80-174\% speed-up (mean: 119\%) relative to optimized serial Gauss-Sidel and SOR smoothers.
 This speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any need for additional communication.
@@
     \end{subfigure}
-    \begin{minipage}{0.47\textwidth}
-        \begin{subfigure}{\textwidth}
+    % \begin{minipage}{0.47\textwidth}
+        \begin{subfigure}{0.47\textwidth}
         \centering
@@
         \end{subfigure}
-        \begin{subfigure}{\textwidth}
+        \hfill
+        \begin{subfigure}{0.47\textwidth}
         \centering
         \caption{swimming shark}
-        \label{fig:donut}
+        \label{fig:shark}
         \end{subfigure}
-    \end{minipage}
+    % \end{minipage}
     \hfill
-    \begin{subfigure}[b]{0.47\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/compareloss.png}
-        \caption{single-cycle residual reduction}
-        \label{fig:simulation residual}
-    \end{subfigure}
+    % \begin{subfigure}[b]{0.47\textwidth}
+    %     \centering
+    %     \includegraphics[width=\textwidth]{figures/compareloss.png}
+    %     \caption{single-cycle residual reduction}
+    %     \label{fig:simulation residual}
+    % \end{subfigure}
     \caption{(a-e) Snapshots from the five flow simulation cases.
-The Taylor-Green Vortex and torus flow are 3D cases, and the flapping wing and swimming shark have dynamic geometries.
-(f) Residual reduction over a single Multi-grid V-cycle for classical and parameterized smoothers on each case.
-The `transfer' smoother has been trained on the union of the synthetic data sets from Figure~\ref{fig:synthetic cases}.}
+The Taylor-Green Vortex and torus flow are 3D, the flapping wing is dynamic without a background flow and the swimming shark is a deforming geometry.}
     \label{fig:simulation cases}
@@
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.47\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/diag_fun.png}
-        \caption{diagonal functions}
-        \label{fig:scaled loss}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.47\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/lower_fun.png}
-        \caption{off-diagonal functions}
-        \label{fig:simulation time}
-    \end{subfigure}
-        \caption{(a) Diagonal and (b) off-diagonal parameterized functions after optimization on each simulation case.
-The `transfer' smoother was tuned on the synthetic cases and `Jacobi' is shown for comparison.}
-        \label{fig:tuned simulation}
-\end{figure}
+Five unsteady incompressible simulation cases were used to further characterize the accelerated project method, Figure \ref{fig:simulation cases}.
+All simulations use the same validated Cartesian-grid flow simulator but feature significantly different physics, i.e.
+2D and 3D simulations with and without background flows, immersed geometries, body motion, and body deformation.
 
@@
 
+The parameterized smoother from the synthetic cases of the previous section is effective at reducing the residual on the unseen simulation cases, Figure \ref{fig:scaled loss}.
+This `transfer' smoother achieves 85-95\% of the residual reduction of a smoother optimized for each case.
+Even more promising is that training on reduced-size simulations closes that small gap almost completely.
+Training on a $1/4^\text{th}$-scale simulation is fast, requiring only $N_{1/4} = N/4^M$ points (N/16 in 2D and N/64 in 3D) and $\approx 1/4$ the number of time steps, while achieving 99-100\% of the residual reduction of training with full-scale data.
+Such an \textit{auto-tuning} approach enables a highly effective data-driven projection method to be developed for any simulation approach with very little overhead.
+
+The relative speed-up of this approach is compared to classic MG methods and the transfer smoother in Figure \ref{fig:simulation time}.
+As with the synthetic cases of the previous section, the data-driven methods are much faster, with the auto-tuned approach accelerating the projection step by 66-120\%.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/diag_fun.png}
+        \caption{diagonal functions}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/lower_fun.png}
+        \caption{off-diagonal functions}
+    \end{subfigure}
+        \caption{(a) Diagonal and (b) off-diagonal parameterized functions after optimization on each simulation case.
+The `transfer' smoother was tuned on the synthetic cases and `Jacobi' is shown for comparison.}
+        \label{fig:tuned inverse}
+\end{figure}
+
+Finally, the parameterized $f_d,\,f_o$ functions used in the approximate inverse equation \ref{eq:approxinv} are shown in Figure \ref{fig:tuned inverse}.
+It is interesting to note that the diagonal functions are all somewhat centered on one and the off-diagonal values all have an essentially zero intercept as these are the values for the Jacobi smoother.
+We also note that the `wing' and `shark' cases produce parameterizations which are similar to each other but significantly different than the others cases.
+This is reasonable as dynamic and deforming geometries put unique burdens on the pressure projection step, as shown in the longer convergence times for these cases shown in Figure \ref{fig:simulation time}.
+Adopting a data-driven and auto-tuned approach enables these pressure-projection dominated cases to achieve significant accelerations.
+
 \section{Conclusions}
 
-\section*{References}
+This manuscript developed
 

### 2021-10-03 src/candidate_smoothers.jl
Classic GS and SOR
Changed the initial GS and SOR loop to match the standard algorithms. It's very slightly slower and better at reducing the loss.

@@ -2,21 +2,28 @@ using GeometricMultigrid
 using GeometricMultigrid: multL, multU, mult, increment!, δ
 
 # Classical smoothers
-@fastmath function GS!(st;inner=2,kw...) # copied from GeometricMultigrid
-    @loop st.ϵ[I] = st.r[I]*st.iD[I]
-    @inbounds for _ ∈ 1:inner, I ∈ st.iD.R
+@fastmath function GS!(st;inner=3,kw...)
+    @inbounds for I ∈ st.iD.R  # optimized first iteration  
+        st.ϵ[I] = st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ))
+    end
+    @inbounds for _ ∈ 2:inner, I ∈ st.iD.R
         st.ϵ[I] = st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ)-multU(I,st.A.L,st.ϵ))
     end
     increment!(st;kw...)
 end
-@fastmath function SOR!(st;inner=2,ω=1.05,kw...)
-    @loop st.ϵ[I] = ω*st.r[I]*st.iD[I]
-    @inbounds for _ ∈ 1:inner, I ∈ st.iD.R
+@fastmath function SOR!(st;inner=3,ω=1.15,kw...)
+    @inbounds for I ∈ st.iD.R  # optimized first iteration
+        st.ϵ[I] = ω*st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ))
+     end
+     @inbounds for _ ∈ 2:inner, I ∈ st.iD.R
        st.ϵ[I] = (1-ω)*st.ϵ[I]+ω*st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ)-multU(I,st.A.L,st.ϵ))
     end
     increment!(st;kw...)
 end
-Jacobi!(st;kw...) = GS!(st,inner=0)
+@fastmath function Jacobi!(st;kw...)
+    @loop st.ϵ[I] = st.r[I]*st.iD[I]
+    increment!(st;kw...)
+end
 
 # Parameterized approximate inverse matrix P
 function PseudoInv(A::FieldMatrix; scale=maximum(A.L),

### 2021-10-03 src/candidate_smoothers.jl
add kw... to a few functions

@@ -28,7 +28,7 @@ end
 # Parameterized approximate inverse matrix P
 function PseudoInv(A::FieldMatrix; scale=maximum(A.L),
     p::AbstractVector{T}=Float32[-0.1449,-0.0162,0.00734,0.3635,-0.2018],
-    models=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5]))) where T
+    models=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5])),kw...) where T
 
     L,D,N = zeros(T,size(A.L)),zeros(T,size(A.D)),length(size(A.D))
     Dm,Lm = models(p)

### 2021-10-03 src/metrics.jl

@@ -8,7 +8,7 @@ avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
 # measure average residual reduction after it V-cycles
 Δresid(st;it=1,kw...) = (resid = mg!(st;mxiter=it,log=true,kw...);
                         log10(resid[end]/resid[1])/it)
-loss(data;p=p₀,kw...) = sum(Δresid(state(d...;p);kw...) for d ∈ data)/length(data)
+loss(data;p=p₀,kw...) = sum(Δresid(state(d...;p,kw...);kw...) for d ∈ data)/length(data)
 
 # optimize parameters to minimize loss
 fit(data,p₀=zeros(Float32,5);smooth! = pseudo!,kw...) = Optim.minimizer(

### 2021-10-04 src/metrics.jl
more kw missing

@@ -2,7 +2,7 @@ using GeometricMultigrid: mg!
 using Optim
 
 # count average V-cycles to get reltol 1e-3
-itcount(d,s;kw...) = mg!(state(d...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
+itcount(d,s;kw...) = mg!(state(d...;kw...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
 avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
 
 # measure average residual reduction after it V-cycles

### 2021-10-04 tex/article.tex
Updates from Overleaf

@@
 
-\title{Auto-tuned Multi-grid Solver for Accelerated \\ Pressure Projection}
+\title{Data-Driven Multi-grid Solver for Accelerated \\ Pressure Projection}
 
@@
 Pressure projection is the single most computationally expensive step in an unsteady incompressible fluid simulation.
-This work discusses the potential of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection, linking Multigrid methods to Convolutional Neural Networks.
+This work discusses the potential of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection, linking Multi-grid methods to convolutional encoder-decoder networks.
 Required to maintain linearity in pressure, the best option for data-driven acceleration is in the smoothing step.
-Using automatic differentiation, a high-speed parameterized smoother is developed which out-performs classic Multi-grid methods by 66-185\% on eleven 2D and 3D benchmarks.
-The tuned parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of any flow.
+Using automatic differentiation, a high-speed parameterized smoother is developed which accelerates classic Multi-grid methods by 66-185\% on eleven 2D and 3D benchmarks with no loss of accuracy.
+The tuned parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of general flows.
 \end{abstract}
@@
 Pressure projection is a bottleneck in high-speed unsteady incompressible flow solvers.
-Constructing approximate solutions the discrete pressure Poisson system typically makes up 25-50\% of the solution cost even in serial simulations, and the proportional cost grows in massively parallel simulations as the elliptic equation requires communication throughout the computational domain instead of being confined to a local characteristic.
-Methods such as artificial-compressibility, smooth-particle-hydrodynamics, and particle-in-cell attempt to side-step this computational cost by modelling or otherwise under-resolving the pressure evolution compared to the fluid's momentum.
-However, these approaches lead to significant errors in pressure forces, thereby making them unsuitable for many applications or requiring explicit pressure corrections.
+Constructing approximate solutions the discrete pressure Poisson system is the most expensive part of each time-step as the elliptic equation requires communication throughout the computational domain instead of being confined to a local characteristic.
+As such, the proportional cost only grows in massively parallel simulations due to the required communication across processes.
+Methods such as artificial-compressibility \cite{he2002comparison}, smooth-particle-hydrodynamics \cite{kiara2013sph}, and particle-in-cell \cite{jiang2017angular} attempt to side-step this computational cost by modelling or otherwise under-resolving the pressure evolution compared to the fluid's momentum.
+However, these approaches lead to significant errors in pressure forces, thereby making them unsuitable for many applications or requiring explicit pressure corrections, \cite{kiara2013sph}.
 
 Recent advances in data-driven acceleration of flow solvers have mainly focused on data-assimilation methods and data-driven turbulence closures.
-Data-assimilation methods typically avoid the expensive pressure projection step entirely, focusing on applications where time-accurate pressure forces are not important.
-Data-driven closures for Large Eddy Simulation (LES) and Unsteady Reynolds Averaged Navier-Stokes (unRANS) and even Spanwise Averaged Navier-Stokes (SANS) simulations have seen growing success and are capable of accurate force prediction.
-Deep learning Convolutional Neural Networks (CNN) have enabled many of these turbulence closures as well as other fluids applications such as super-resolution and generative models.
-CNN architectures have inherent translational symmetry and often use a restriction phase, where the size of the network is reduced before expanding again, both of which help generalize the trained networks to unseen prediction cases.
+Data-assimilation methods typically avoid the expensive pressure projection step entirely, focusing on applications where time-accurate pressure forces are not important \cite{asch2016data}.
+Deep learning closures for Large Eddy Simulation (LES) \cite{BECK2019108910,maulik_san_rasheed_vedula_2019}, Unsteady Reynolds Averaged Navier-Stokes (unRANS) \cite{ling_kurzawski_templeton_2016}, and even Spanwise Averaged Navier-Stokes (SANS) \cite{font2021deep} simulations have seen growing success and are capable of accurate force prediction.
 
-However, none of these studies have applied data-driven techniques to accelerate the critical projection step itself.
-Some recent work has focused on the pressure projection step explicitly.
-Chaotic projection methods for massively parallel systems; not data driven.
-Multi-grid data-driven decomposition; high errors and unclear speed-up.
-This work develops a high-speed data-driven project method which outperforms classic methods on eleven 2D and 3D benchmarks.
-Moreover, as the approach in linear in the pressure and scale-invariant, the parameters can be tuned on a coarse simulation and maintain their accelerated performance on unseen fine-grid simulations.
+\begin{figure}
+    \caption{Sketch of a Convolutional Neural Networks (CNN) and/or a Multi-grid V-cycle.}
+    \label{fig:multigrid}
+\end{figure}
+
+Many of these turbulence closures as well as other fluids applications such as super-resolution \cite{ferdian20204dflownet,liu2020deep} and full field regression models \cite{duru2021cnnfoil,bhatnagar2019prediction} are based on Convolutional Neural Networks (CNN) and encoder-decoder architectures.
+CNNs have inherent translational symmetry and encoder-decoder architectures reduce the number of variables before expanding again, Figure \ref{fig:multigrid}, both of which help constrain learning capacity and generalize the trained networks to unseen prediction cases.
+
+A few studies have applied machine-learning to accelerate the critical projection step itself, \cite{ozbay2021poisson,Xiao2020,ajuria2020}.
+All of these approaches use CNNs, attempting to predict the pressure field given the projection source term on a uniform grid, meaning they are limited to cases without internal solid geometries.
+While \cite{ozbay2021poisson} uses a decomposition to handle different \textit{domain} boundary conditions and grid aspect ratios in 2D and sees a significant speed-up over traditional Multi-grid methods, the results are still somewhat qualitative, with pressure errors greater than 10\% throughout much of the domain.
+
+The primary insight of this paper is that Multi-grid methods are \textit{already} convolutional encoder-decoder networks with optimal $O(N\log N)$ scaling, prime for data-driven acceleration without any loss of accuracy in the resulting pressure field.
+This work develops a high-speed data-driven projection method which outperforms classic Multi-grid on eleven 2D and 3D benchmarks including those with immersed solid boundaries.
+Moreover, since the approach is linear in the pressure and the nonlinear dependence on the matrix coefficients are scale-invariant, the data-optimized parameters generalize extremely well to new flows and simulation resolutions.
 
@@
 
-Multi-grid (MG) methods are among the fastest iterative solution approaches for variable coefficient discrete pressure Poisson equations.
-The MG operator is effectively a \textit{linear} convolutional architecture where the system is preconditioned before the residual is restricted down to a reduced-size problem and the correction is prolongated back up.
+Multi-grid (MG) methods are among the fastest iterative solution approaches for variable coefficient discrete pressure Poisson equations because the MG operator is effectively a \textit{linear} convolutional encoder-decoder network, Figure \ref{fig:multigrid}.
+The system is preconditioned before the residual is restricted down to a reduced-size problem and the correction is prolongated back up.
 % \begin{equation}
@@
 % where $R$ is the $N_c \times N$ restriction operator, $P$ is the $N \times N_c$ prolongation operator 
-The restriction-solve-prolongation process, a V-cycle, distributes the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to \textit{smooth} the local high-frequency error in the projected solution.
+The restriction-solve-prolongation process, a V-cycle, distributes the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to smooth the local error in the projected solution.
 The MG architecture proceeds recursively on the reduced-size problems until a small linear algebra problem is reached which can be approximated with minimal cost.
-This recursive approach results in only $O(N\log N)$ computational cost.
+This recursive approach results in $O(N\log N)$ computational cost.
 
@@
 
-As \textit{any} element of the residual of the elliptic system potentially influences \textit{every} element of the update, $O(N\log N)$ is the best possible solution time scaling.
+As \textit{any} element of the residual of the elliptic Poisson system potentially influences \textit{every} element of the update, $O(N\log N)$ is the best possible solution time scaling.
 However, data-driven methods can still be used to accelerate pressure projection methods by speeding-up and increasing the residual reduction of each V-cycle iteration.
 
-The linearity of equation \ref{eq:aer} is a critical property which the data-driven method must maintain in order to be useful in practise, but this linearity is only with respect to the update and residual fields.
-The operators of the ``MG network'' can all potentially be optimized for a specific sub-class of problems.
+The linearity of equation \ref{eq:aer} is a critical property which the data-driven method must maintain.
+Not only will this increase generality, but a nonlinear method could not be used iteratively since the modes of the residual will change as the solver converges.
+However, this linearity is only with respect to the update and residual fields.
+The operators of the MG method can all potentially be optimized for a specific sub-class of problems.
 In particular, those operators can be made into parameterized nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
@@
 Which MG operation is the best candidate for such an approach?
-The prolongation operator (restriction simply being its transpose) is not inherently a function of $A$, and while related super-resolution operators have seen improvements in the literature, these are always nonlinear functions of the field.
+The prolongation operator (restriction simply being its transpose) is not inherently a function of $A$, and while related super-resolution operators have seen use in the literature, these are always nonlinear functions of the field.
 The precondition operator is an option, but a simple Jacobi preconditioner
@@
 where $D$ is the diagonal of $A$, is as fast as possible and is sufficient for the V-cycle to distribute the residual throughout the domain.
-Therefore, for the remainder of the paper we will focus on the smoother as the best candidate for acceleration, using a simple Jacobi preconditioner and uniform pooling/distribution for restriction/prolongation.
+Therefore, for the remainder of the paper we will focus on the smoother as the best candidate for parameterization, using a simple Jacobi preconditioner and uniform pooling/distribution for restriction/prolongation.
 
@@
 and determined using Newton's method.
-Automatic differentiation (AD) is used to determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$, avoiding inaccurate and potentially unstable finite differences of the nonlinear recursive loss function.
+Automatic differentiation (AD) is used to determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ \cite{RevelsLubinPapamarkou2016}, avoiding inaccurate and potentially unstable finite differences of the nonlinear recursive loss function.
 
-The data-driven solver and all the test cases and figures presented in the following sections are implemented in Julia and available for reproduction.
+The data-driven solver and all test cases presented in the following sections are implemented in Julia and available for reproduction \cite{bezanson2017julia,weymouth2021julia}.
 
@@
 Figure~\ref{fig:synthetic time} shows the time to reduce the residual of each case by $10^{-3}$ relative to the time to run a single V-cycle using a Jacobi smoother.
-While a Jacobi smoother take  hundreds or even thousands of V-cycles to converge, the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, and yet converges in only 1-3 V-cycles in all cases.
+While a Jacobi smoother requires  hundreds or even thousands of V-cycles to converge, the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, and yet converges in only 1-3 V-cycles in all cases.
 This results in a 80-174\% speed-up (mean: 119\%) relative to optimized serial Gauss-Sidel and SOR smoothers.
-This speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any need for additional communication.
+This speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any additional communication.
 
@@
         \caption{flapping wing}
-        \label{fig:donut}
+        \label{fig:wing}
     \end{subfigure}
@@
 
-Five unsteady incompressible simulation cases were used to further characterize the accelerated project method, Figure \ref{fig:simulation cases}.
-All simulations use the same validated Cartesian-grid flow simulator but feature significantly different physics, i.e.
+Five unsteady incompressible simulation cases were used to further characterize the accelerated projection method, Figure \ref{fig:simulation cases}.
+All simulations use the same validated Cartesian-grid method \cite{maertens2015accurate} but feature significantly different physics, i.e.
 2D and 3D simulations with and without background flows, immersed geometries, body motion, and body deformation.
@@
 
-This manuscript developed
+This manuscript develops a successful data-driven method to accelerate the solution of discrete pressure Poisson systems found in incompressible flow simulations.
+Mathematical constraints are used to focus the learning capacity to a parameterized Jacobi-like Multi-grid smoother.
+Being a sparse matrix-vector multiplication, this function is nearly as fast as a trivial Jacobi smoother, and much faster than Gauss-Sidel or SOR smoothing.
+After using automatic-differentiation for training, the data-driven MG method is found to accelerate projection by 66-185\% on eleven simulation cases.
+Because of the reduced learning capacity, the generalization is excellent, enabling 90\% effective transfer learning from a synthetic data-set and essentially perfect transfer from reduced resolution simulations.
+
+The potential of machine learning and computer science advances to improve fluid dynamics is vast, but well-applied classical methods and constraints only helps to focus this effort.
+Wherever possible, this work has made the simplest choice in parameterization, leaving significant opportunities for future improvements.
+Many other flow solvers and linear systems are yet to be explored, and extensions to this basic data-driven approach could accelerate solutions for a wide array of discrete partial differential equations.
 

### 2021-10-04 src/candidate_smoothers.jl
tune jacobi

@@ -21,43 +21,46 @@ end
     increment!(st;kw...)
 end
 @fastmath function Jacobi!(st;kw...)
-    @loop st.ϵ[I] = st.r[I]*st.iD[I]
+    @loop st.ϵ[I] = st.r[I]*st.iD[I] # hacked by TunedJacobi!
     increment!(st;kw...)
 end
 
 # Parameterized approximate inverse matrix P
-function PseudoInv(A::FieldMatrix; scale=maximum(A.L),
-    p::AbstractVector{T}=Float32[-0.1449,-0.0162,0.00734,0.3635,-0.2018],
+p₀ = Float32[-0.100887, -0.00164709, 0.00833292, 0.418425, -0.260235, 0., 0., 0., 0.] # result from tune_synthetic
+function PseudoInv(A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
     models=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5])),kw...) where T
 
     L,D,N = zeros(T,size(A.L)),zeros(T,size(A.D)),length(size(A.D))
     Dm,Lm = models(p)
     for I ∈ A.R
-        invD = (abs(A.D[I])<1e-8) ? 0. : 1.0/A.D[I]
+        invD = (abs(A.D[I])<1e-8) ? 0. : inv(A.D[I])
         D[I] = invD*Dm(A.D[I]/scale)
         for i ∈ 1:N
             J = I-δ(i,N)
-            invD = (abs(A.D[I]+A.D[J])<2e-8) ? 0. : 2.0/(A.D[I]+A.D[J])
+            invD = (abs(A.D[I]+A.D[J])<2e-8) ? 0. : 2inv(A.D[I]+A.D[J])
             L[I,i] = invD*Lm(A.L[I,i]/scale)
         end
     end
     FieldMatrix(L,D,A.R)
 end
+function TunedJacobi!(iD::FieldVector{T},A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
+    models=p->(D->1+p[1]+D*(p[2]+D*(p[3]+D*p[4]))),pindex=6,kw...) where T
+    Dm = models(p[pindex:end])
+    @loop iD[I] = (abs(A.D[I])<1e-8) ? 0. : inv(A.D[I])*Dm(A.D[I]/scale)
+end
 
 # Create MG state with st.P
[…]

### 2021-10-04 tune_synthetic.jl

@@ -1,11 +1,12 @@
 using TunedSmoother, Plots, DataStructures
 using GeometricMultigrid: mg!
+using TunedSmoother: p₀
 
 # create synthetic example systems
 begin
-    data = make_data()
-    opt = OrderedDict(name=>zeros(Float32,5) for name ∈ keys(data))
-    opt["union"] = zeros(Float32,5)
+    data = create_synthetic(len=25)
+    opt = OrderedDict(name=>p₀ for name ∈ keys(data))
+    opt["union"] = p₀
 end
 
 # optimize Parameterized smoother
@@ -18,35 +19,46 @@ begin
     opt["union"] = fit(vcat((d for (_,d) in data)...),opt["union"])
     opt
 end
+begin # more training?
+    name = "3D-static"
+    opt[name] = fit(data[name],opt[name])        
+end
 begin
-    # opt = OrderedDict(
-    #     "2D-static" => [-2.36056, -1.40822, -0.203578, 0.271696, -5.47975f-7],
-    #     "3D-static" => [0.206214, 0.0214632, -0.00525863, 0.315253, 0.0135281],
-    #     "2D-dipole" => [-1.71116, -0.902871, -0.114227, 0.166726, 3.14462f-7],
-    #     "3D-dipole" => [-0.663327, -0.199177, -0.00915381, 0.149958, -1.54752f-7],
-    #     "2D-sphere" => [-0.003891, 0.047247, 0.0149267, 0.377898, -0.217221],
-    #     "3D-sphere" => [-0.0966329, -0.0967704, -0.00862894, 0.432134, -0.271047],
-    #     "union"  => [-0.144944, -0.0162348, 0.00734042, 0.363533, -0.201831])
     opt = OrderedDict(
-        "2D-static" => Float32[-2.46273, -1.32142, -0.175033, 0.145184, 0],
-        "3D-static" => Float32[0.93542, 0.210713, 0.00503395, 0.309537, 0.0135281],
-        "2D-dipole" => Float32[-2.56297, -1.41248, -0.188902, 0.163554, 0],
-        "3D-dipole" => Float32[-0.752343, -0.258171, -0.0168188, 0.145254, 0],
-        "2D-sphere" => Float32[0.0406717, 0.0436037, 0.0111401, 0.470527, -0.310894],
-        "3D-sphere" => Float32[-0.0483643, -0.0815794, -0.00751761, 0.54353, -0.381655],
[…]

### 2021-10-04 benchmark.jl
update figures with tunedjacobi

@@ -6,26 +6,25 @@ begin
     smoothers = [Jacobi!,GS!,SOR!,pseudo!]
     suite = BenchmarkGroup()
     for s ∈ smoothers, (name,d) ∈ data
-        suite[name,s] = @benchmarkable Vcycle!(st;smooth! = $s) setup=(st=state($d[1]...))
+        suite[name,s] = @benchmarkable Vcycle!(st;smooth! = $s) setup=(st=state($d[1]...;smooth! = $s))
     end
 end
 begin # run benchmarks and count iterations
     results = run(suite)
     times = [minimum(results[name,s]).time for s ∈ smoothers, name ∈ keys(data)]
     time_factor = times[2:end,:]./times[1,:]'
-    counts = [avecount(d,s) for s in smoothers[2:end], (name,d) ∈ data]
 end
 
+p = Float32[-0.14102, -0.0149183, 0.00704117, 0.39624, -0.242721, 1.41382, 1.70377, 0.558954, 0.0511064]
+counts = [avecount(d,pseudo!;p) for (_,d) ∈ data]
+
 begin # results from block above
-    time_factor = [ 2.26743  2.29541  2.25677  2.24512  2.27092  2.30344
-                    2.87374  2.46019  2.86748  2.52186  2.87211  2.44708
-                    1.37096  1.56152  1.36767  1.54179  1.36671  1.54011]
-    time_factor = [ 2.397728501892915
-                    2.5168063818280153
-                    1.3297458085451594]
+    time_factor = [ 3.50716   2.72302   3.5       2.73946   3.51437   2.71142
+                    4.75072   3.24036   4.74      3.21826   4.76437   3.19066
+                    1.37096   1.56152   1.36767   1.54179   1.36671   1.54011]
     counts = [ 3.0  4.0  1.5   1.17  3.98  3.55
                 4.0  3.0  1.55  1.16  3.96  3.0
-                3.0  3.0  1.07  1.14  3.18  3.0]
+                2.0  3.0  1.04  1.04  3.18  3.0]
     rel_time = counts.*time_factor
     accel = rel_time[1:2,:]./rel_time[3,:]' # speed up!!
 end
@@ -38,7 +37,7 @@ begin # plot
     ctg = CategoricalArray(repeat(cats,inner=n))
     levels!(ctg,cats)
     groupedbar((counts.*time_factor)',size=(400,350),
-                group=ctg, legend=:bottomright,c=colors,
+                group=ctg,c=colors,
[…]

### 2021-10-04 src/metrics.jl

@@ -2,7 +2,7 @@ using GeometricMultigrid: mg!
 using Optim
 
 # count average V-cycles to get reltol 1e-3
-itcount(d,s;kw...) = mg!(state(d...;kw...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
+itcount(d,s;kw...) = mg!(state(d...;smooth! = s,kw...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
 avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
 
 # measure average residual reduction after it V-cycles

### 2021-10-04 tune_synthetic.jl

@@ -1,5 +1,4 @@
 using TunedSmoother, Plots, DataStructures
-using GeometricMultigrid: mg!
 using TunedSmoother: p₀
 
 # create synthetic example systems
@@ -52,18 +51,19 @@ begin
                     -1.07719   -0.969893  -1.19038   -0.711357  -1.18484   -1.04052
                     -0.584837  -1.11636   -1.10983   -1.06949   -0.865098  -1.30172
                     -1.60192   -1.48928   -1.32291   -1.33769   -1.09491   -1.21621]
-    # crossloss = [ -1.55321    0.640369  -1.46382   -0.0151795   0.648754   0.390737
-    #             -0.499447  -1.58266   -0.481403  -0.050292   -0.115627  -0.165515
-    #             -1.37756    0.671862  -1.48931    0.0606938   0.706572   0.473284
-    #             -1.40851   -1.19475   -1.44604   -1.21932    -0.766175  -0.962715
-    #             -1.32879   -1.22121   -1.47734   -1.17385    -1.17231   -1.20132
-    #             -0.604588  -1.24316   -1.2717    -1.14473    -0.881098  -1.23876
-    #             -1.42622   -1.22249   -1.47834   -1.20185    -1.15029   -1.17799]
+    crossloss = [ -1.87665    1.16439   -1.13973   1.65732   -0.0803689   1.39344
+    -0.622401  -1.8119    -0.56231   0.28911   -0.428983   -0.261036
+    -1.36738    1.58017   -1.66168   2.09321    0.170027    1.68013
+    -0.576945  -1.086     -1.33573  -1.60083   -0.964724   -1.15003
+    -1.07719   -0.972905  -1.4157   -0.808376  -1.28669    -1.04982
+    -0.584835  -1.11912   -1.32193  -1.14577   -1.11273    -1.27706
+    -1.60193   -1.48923   -1.58166  -1.52131   -1.21837    -1.16797
+   ]
 end
 
 using Plots.PlotMeasures
 begin
-    lim = maximum(abs.(crossloss))
+    lim = -minimum(crossloss)
     names(d) = (1:length(d),keys(d))
     plot(size=(400,350))
     display(heatmap!(crossloss',c=palette([:green,:white,:red],13),clims=(-lim,lim),

### 2021-10-04 src/candidate_smoothers.jl
Correct wing source error and make waterlily plots

@@ -53,6 +53,8 @@ end
 function state(A,x,b;p=p₀,xT::Type=eltype(p),smooth! =GS!,kw...)
     y = zero(x,xT)     # make FieldVector of type xT
     @loop y[I] = x[I]  # copy values
+    err = sum(b)/length(b)
+    @loop b[I] -= err
     st = mg_state(A,y,b)
     smooth! == pseudo! && fill_pseudo!(st;p,kw...)
     st

### 2021-10-04 src/create_waterlily.jl

@@ -20,7 +20,7 @@ function sim_collect_poisson!(sim;Δt=0.1,remeasure)
 end
 
 function circle(p=6;Re=250,n=16,m=8,T=Float64)
-    radius = 2^(p-3)
+    radius = 2^(p-2)
     center, ν = radius*m/2, radius/Re
     body = AutoBody((x,t)->norm2(x .- center) - radius)
     return Simulation((n*radius+2,m*radius+2), [1.,0.], radius; ν, body, T)
@@ -49,7 +49,7 @@ function donut(p=6;Re=1e3,T=Float64)
 end
 
 using StaticArrays: SVector, @SMatrix
-function wing(p=6;Re=250,U=1,amp=π/4,ϵ=1,thk=2ϵ+√2,T=Float64)
+function wing(p=6;Re=250,U=1,amp=π/4,ϵ=0.5,thk=2ϵ+√2,T=Float64)
     L = 2^(p-1)
     sdf(x,t) = norm2(x .- SVector(0.,clamp(x[2],-L/2,L/2)))-thk/2
     function map(x,t)
@@ -84,6 +84,7 @@ function create_waterlily(;len=100,Δt=0.1,cases=[circle,TGV,donut,wing,shark],p
         @show case
         remeasure = case ∈ (wing,shark)
         sim = case(p;kw...)
+        case == circle && WaterLily.sim_step!(sim,15)
         data[case] = [sim_collect_poisson!(sim;Δt,remeasure) for i ∈ 1:len]
     end
     return data

### 2021-10-04 test_waterlily.jl

@@ -1,82 +1,16 @@
-using GeometricMultigrid
-import GeometricMultigrid: GS!,pseudo!,SOR!
+using TunedSmoother,BenchmarkTools,Plots
+using TunedSmoother: p₀
 
 # Generate WaterLily simulation data
-begin # this block takes a few minutes...
-    include("create_waterlily.jl")
-    data = create_waterlily(;len=1,p=4)
-end
-
-# Set up a custom mg_state
-begin
-    fill_pseudo!(st;kw...) = fill_pseudo!(st,st.child;kw...)
-    fill_pseudo!(st,child;kw...) = (fill_pseudo!(st,nothing;kw...);fill_pseudo!(child;kw...))
-    fill_pseudo!(st,::Nothing;kw...) = st.P=PseudoInv(st.A;kw...)
-
-    p₀ = Float32[-0.1449,-0.0162,0.00734,0.3635,-0.2018] # result from tune_synthetic
-    function state(x,L,b;p=p₀,xT::Type=eltype(p))
-        xv = FieldVec(zeros(xT,size(x)))
-        @loop xv[I] = x[I]
-        st=mg_state(GeometricMultigrid.Poisson(L),xv,FieldVec(b))
-        s = sum(st.r[I] for I ∈ st.r.R)
-        st.r .-= s/length(st.r.R)
-        fill_pseudo!(st;p)
-        st
-    end
-end
-
-# Filter diverging examples
-begin
-    itcount(data;p=p₀,kw...) = mg!(state(data...;p);reltol=1e-3,inner=2,kw...)
-    avecount(data;kw...) = sum(itcount(d;kw...) for d ∈ data)/length(data)
-    data[wing] = filter(d->itcount(d;smooth! =GS!)<32,data[wing])
-end
-
-# Define loss as average drop in residual after `it` number of Vcycles
-begin
-    Δresid(st;it=1,kw...) = (resid = mg!(st;mxiter=it,inner=2,log=true,kw...);
-                             log10(resid[end]/resid[1])/it)
-    loss(data;p=p₀,kw...) = sum(Δresid(state(d...;p);kw...) for d ∈ data)/length(data)
-end
-
-# Define smoother options and get loss across smoothers
-begin
-    Jacobi!(st;kw...) = GS!(st;inner=0,kw...)
-    smoothers = [Jacobi!,GS!,pseudo!]
-end
-compareloss = [loss(d;smooth!) for smooth! ∈ smoothers, (_,d) ∈ data]
-
-begin # results
[…]

### 2021-10-04 tune_synthetic.jl

@@ -31,33 +31,18 @@ begin
         "2D-sphere" => [0.0915379, 0.0833613, 0.017635, 0.447855, -0.291, 0.687612, 1.31916, 0.695357, 0.0940616],
         "3D-sphere" => [-0.00827322, -0.0546565, -0.00438196, 0.53397, -0.377591, 0.446063, -0.0336524, -0.0570324, -0.0110678],
         "union"     => [-0.14102, -0.0149183, 0.00704117, 0.39624, -0.242721, 1.41382, 1.70377, 0.558954, 0.0511064])
-    # opt = OrderedDict(
-    #     "2D-static" => Float32[-2.46273, -1.32142, -0.175033, 0.145184, 0],
-    #     "3D-static" => Float32[0.93542, 0.210713, 0.00503395, 0.309537, 0.0135281],
-    #     "2D-dipole" => Float32[-2.56297, -1.41248, -0.188902, 0.163554, 0],
-    #     "3D-dipole" => Float32[-0.752343, -0.258171, -0.0168188, 0.145254, 0],
-    #     "2D-sphere" => Float32[0.0406717, 0.0436037, 0.0111401, 0.470527, -0.310894],
-    #     "3D-sphere" => Float32[-0.0483643, -0.0815794, -0.00751761, 0.54353, -0.381655],
-    #     "union"     => Float32[-0.100887, -0.00164709, 0.00833292, 0.418425, -0.260235])
 end
 
 # compare across example types
 crossloss = [loss(test;p,smooth! = pseudo!) for (_,p) ∈ opt, (_,test) ∈ data]
 begin
-    crossloss = [   -1.87665    1.16437   -0.932718   1.47818    0.514677   1.36797
-                    -0.622406  -1.81191   -0.473679   0.145313  -0.233023  -0.254706
-                    -1.36729    1.58016   -1.39741    1.86527    1.02292    1.77555
-                    -0.576947  -1.08601   -1.12405   -1.39806   -0.750951  -1.19397
-                    -1.07719   -0.969893  -1.19038   -0.711357  -1.18484   -1.04052
-                    -0.584837  -1.11636   -1.10983   -1.06949   -0.865098  -1.30172
-                    -1.60192   -1.48928   -1.32291   -1.33769   -1.09491   -1.21621]
-    crossloss = [ -1.87665    1.16439   -1.13973   1.65732   -0.0803689   1.39344
-    -0.622401  -1.8119    -0.56231   0.28911   -0.428983   -0.261036
[…]

### 2021-10-05 test_waterlily.jl
opt block in test_waterlily

@@ -3,31 +3,33 @@ using TunedSmoother: p₀
 
 # Generate WaterLily simulation data
 data = create_waterlily()
-
 # Optimize the psuedo-inverse functions
 begin # this block takes around 30 minutes. the next block has the results
+    smooth! = pseudo!
     opt = OrderedDict(name=>p₀ for name ∈ keys(data))
-    scaleloss = zeros(4,length(opt))
+    scaleloss = zeros(5,length(opt))
+    scaleloss[1,:] .= [loss(test;p=p₀,smooth!) for (name,test) ∈ data]
     for scale ∈ 1:4
         @show scale
-        scaledata = scale==4 ? data : make_data(p=scale+2)
-        opt = OrderedDict(name=>fit(train;p₀=opt[name]) for (name,train) ∈ scaledata)
-        scaleloss[scale,:] .= [loss(test;p=opt[name]) for (name,test) ∈ data]
+        scaledata = scale==4 ? data : create_waterlily(p=scale+2)
+        opt = OrderedDict(name=>fit(train,opt[name]) for (name,train) ∈ scaledata)
+        scaleloss[scale+1,:] .= [loss(test;p=opt[name],smooth!) for (name,test) ∈ data]
     end
 end
 
 begin # output from the block above
     opt = OrderedDict(
-        circle => [0.266145, 0.176086, 0.0344038, 0.453681, -0.27995],
-        TGV    => [-0.150537, -0.0375542, 0.00201316, 0.329784, -0.201799],
-        donut  => [0.20243, 0.0752068, 0.0116999, 0.323697, -0.189171],
-        wing   => [-0.108999, -0.193017, -0.0354521, 0.532743, -0.340341],
-        shark  => [-0.282117, -0.283407, -0.0472922, 0.577397, -0.402278])
+        circle => [0.0271442, -0.0248311, -0.000622211, 0.651889, -0.476478, 1.9026, 1.28664, 0.24255, 0.0105331],
+        TGV    => [-0.188616, -0.0378252, 0.00345329, 0.39165, -0.260235, -3.87929, -2.60139, -0.538449, -0.0352438],
+        donut  => [-0.116905, -0.0244976, 0.00293478, 0.274545, -0.148386, -0.579809, -0.771899, -0.19491, -0.0143433],
+        wing   => [-0.21447, -0.245247, -0.041811, 0.790682, -0.613002, -0.101302, -0.447094, -0.350419, -0.0669029],
[…]

### 2021-10-05 src/create_waterlily.jl
update triple figs

@@ -84,25 +84,9 @@ function create_waterlily(;len=100,Δt=0.1,cases=[circle,TGV,donut,wing,shark],p
         @show case
         remeasure = case ∈ (wing,shark)
         sim = case(p;kw...)
+        case==circle && WaterLily.sim_step!(sim,20)
         case == circle && WaterLily.sim_step!(sim,15)
         data[case] = [sim_collect_poisson!(sim;Δt,remeasure) for i ∈ 1:len]
     end
     return data
 end
-
-using Plots
-function gifit(data,j,center)
-    if center
-        for d ∈ data
-            d[j] .-= d[j][2,2]
-        end
-    end
-    R = inside(data[1][j])
-    lim = maximum(maximum(abs.(d[j][R])) for d ∈ data)
-    gr(show=false)
-    @gif for d ∈ data
-        heatmap(d[j][R]',aspect_ratio=:equal,c=palette(:RdBu_11),clims=(-lim/10,lim/10))
-    end
-end
-gifp(data) = gif(data,1,true)
-gifσ(data) = gif(data,3,false)

### 2021-10-05 test_waterlily.jl

@@ -124,16 +124,24 @@ end
 savefig("crosscount.png")
 
 begin
-    for (name,h) in ((circle,160),(wing,300),(shark,160))
-        st = state(data[name][end]...)
-        lim = maximum(st.r)
-        st.x.data .-= st.x[1]
-        plot(heatmap(st.A.D[st.x.R]',legend=false,c=:Blues),
-            heatmap(st.x.data[st.x.R]',legend=false,clims=(-1,1)),
-            heatmap(st.r.data[st.x.R]',legend=false,c=:RdBu_11,clims=(-0.1*lim,0.1*lim)),
-            layout = (1,3),size=(900,h),axis=nothing)
+    using GeometricMultigrid: Vcycle!
+    for (name,h) in ((circle,160),(wing,400),(shark,160))
+        smooth! = pseudo!
+        st = state(data[name][end]...;smooth!)
+        x = copy(st.x.data)
+        x .-= st.x[1]
+        x[st.A.D .> -1.5] .= NaN
+        r = copy(st.r)
+        f(x) = @. log10(clamp(abs(x),1e-6,Inf64))
+        Vcycle!(st;smooth!)
+        plot(heatmap(x[st.x.R]',legend=false,clims=(-1,1)),
+        heatmap(f(r.data[st.x.R]'),legend=false,c=:Reds,clims=(-6,-1)),
+        heatmap(f(st.r.data[st.x.R]'),legend=false,c=:Reds,clims=(-6,-1)),
+        layout = (1,3),size=(900,h),axis=nothing)
         savefig(string(name)*"triple.png")
     end
+end
+begin
     for (name,h,i) in ((TGV,300,25),)
         st = state(data[name][i]...)
         lim = maximum(st.r)

### 2021-10-05 src/create_waterlily.jl
improve wing data + image

@@ -49,7 +49,7 @@ function donut(p=6;Re=1e3,T=Float64)
 end
 
 using StaticArrays: SVector, @SMatrix
-function wing(p=6;Re=250,U=1,amp=π/4,ϵ=0.5,thk=2ϵ+√2,T=Float64)
+function wing(p=6;Re=250,U=1,amp=π/4,thk=2+√2,T=Float64)
     L = 2^(p-1)
     sdf(x,t) = norm2(x .- SVector(0.,clamp(x[2],-L/2,L/2)))-thk/2
     function map(x,t)
@@ -57,7 +57,7 @@ function wing(p=6;Re=250,U=1,amp=π/4,ϵ=0.5,thk=2ϵ+√2,T=Float64)
         R * (x.-SVector(3L+L*sin(t*U/L)+0.01,4L))
     end
     body = AutoBody(sdf,map)
-    Simulation((6L+2,6L+2),zeros(2),L;U,ν=U*L/Re,body,ϵ,T)
+    Simulation((6L+2,6L+2),zeros(2),L;U,ν=U*L/Re,body,T)
 end
 
 using Interpolations

### 2021-10-05 test_waterlily.jl

@@ -125,7 +125,7 @@ savefig("crosscount.png")
 
 begin
     using GeometricMultigrid: Vcycle!
-    for (name,h) in ((circle,160),(wing,400),(shark,160))
+    for (name,h) in ((circle,160),(wing,300),(shark,160))
         smooth! = pseudo!
         st = state(data[name][end]...;smooth!)
         x = copy(st.x.data)

### 2021-10-05 src/create_waterlily.jl
Update 3D images

@@ -49,7 +49,7 @@ function donut(p=6;Re=1e3,T=Float64)
 end
 
 using StaticArrays: SVector, @SMatrix
-function wing(p=6;Re=250,U=1,amp=π/4,thk=2+√2,T=Float64)
+function wing(p=6;Re=250,U=1,amp=π/4,ϵ=0.5,thk=2ϵ+√2,T=Float64)
     L = 2^(p-1)
     sdf(x,t) = norm2(x .- SVector(0.,clamp(x[2],-L/2,L/2)))-thk/2
     function map(x,t)
@@ -57,7 +57,7 @@ function wing(p=6;Re=250,U=1,amp=π/4,thk=2+√2,T=Float64)
         R * (x.-SVector(3L+L*sin(t*U/L)+0.01,4L))
     end
     body = AutoBody(sdf,map)
-    Simulation((6L+2,6L+2),zeros(2),L;U,ν=U*L/Re,body,T)
+    Simulation((6L+2,6L+2),zeros(2),L;U,ν=U*L/Re,body,ϵ,T)
 end
 
 using Interpolations

### 2021-10-05 test_waterlily.jl

@@ -1,4 +1,4 @@
-using TunedSmoother,BenchmarkTools,Plots
+using TunedSmoother,BenchmarkTools,Plots,DataStructures
 using TunedSmoother: p₀
 
 # Generate WaterLily simulation data
@@ -11,7 +11,7 @@ begin # this block takes around 30 minutes. the next block has the results
     scaleloss[1,:] .= [loss(test;p=p₀,smooth!) for (name,test) ∈ data]
     for scale ∈ 1:4
         @show scale
-        scaledata = scale==4 ? data : create_waterlily(p=scale+2)
+        scaledata = scale==4 ? data : create_waterlily(p=scale+2,cases=keys(data))
         opt = OrderedDict(name=>fit(train,opt[name]) for (name,train) ∈ scaledata)
         scaleloss[scale+1,:] .= [loss(test;p=opt[name],smooth!) for (name,test) ∈ data]
     end
@@ -123,10 +123,14 @@ begin
 end
 savefig("crosscount.png")
 
+data = create_waterlily(cases=[TGV,donut])
 begin
     using GeometricMultigrid: Vcycle!
-    for (name,h) in ((circle,160),(wing,300),(shark,160))
+    # for (name,h) in ((circle,160),(wing,300),(shark,160))
+    # for (name,h) in ((TGV,300),)
+    for (name,h) in ((donut,160),)
         smooth! = pseudo!
+        # st = state(data[name][25]...;smooth!)
         st = state(data[name][end]...;smooth!)
         x = copy(st.x.data)
         x .-= st.x[1]
@@ -134,32 +138,14 @@ begin
         r = copy(st.r)
         f(x) = @. log10(clamp(abs(x),1e-6,Inf64))
         Vcycle!(st;smooth!)
-        plot(heatmap(x[st.x.R]',legend=false,clims=(-1,1)),
-        heatmap(f(r.data[st.x.R]'),legend=false,c=:Reds,clims=(-6,-1)),
-        heatmap(f(st.r.data[st.x.R]'),legend=false,c=:Reds,clims=(-6,-1)),
+        # plot(heatmap(x[st.x.R]',legend=false,clims=(-1,1)),
+        # heatmap(f(r.data[st.x.R]'),legend=false,c=:Reds,clims=(-6,-1)),
[…]

### 2021-10-14 src/TunedSmoother.jl
Bug in tuned results
Can't hack iD since the lowest level is solved with GS. Now using the same coefficients for precond! and smooth!

@@ -1,7 +1,7 @@
 module TunedSmoother
 
 include("candidate_smoothers.jl")
-export Jacobi!,GS!,SOR!,pseudo!,state
+export Jacobi!,GS!,SOR!,pseudo!,state,precond!
 
 include("create_synthetic.jl")
 export create_synthetic

### 2021-10-14 src/candidate_smoothers.jl

@@ -20,8 +20,8 @@ end
     end
     increment!(st;kw...)
 end
-@fastmath function Jacobi!(st;kw...)
-    @loop st.ϵ[I] = st.r[I]*st.iD[I] # hacked by TunedJacobi!
+@fastmath Jacobi!(st;inner=1,kw...) = for _ ∈ 1:inner
+    @loop st.ϵ[I] = st.r[I]*st.iD[I]
     increment!(st;kw...)
 end
 
@@ -43,11 +43,6 @@ function PseudoInv(A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
     end
     FieldMatrix(L,D,A.R)
 end
-function TunedJacobi!(iD::FieldVector{T},A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
-    jmodel=p->(D->1+p[6]+D*(p[7]+D*p[8])),kw...) where T
-    Dm = jmodel(p)
-    @loop iD[I] = (abs(A.D[I])<1e-8) ? 0. : inv(A.D[I])*Dm(A.D[I]/scale)
-end
 
 # Create MG state with st.P
 function state(A,x,b;p=p₀,xT::Type=eltype(p),smooth! =GS!,kw...)
@@ -62,15 +57,21 @@ end
 state(A,b;kw...) = state(A,zero(b),b;kw...)
 fill_pseudo!(st;kw...) = fill_pseudo!(st,st.child;kw...)
 fill_pseudo!(st,child;kw...) = (fill_pseudo!(st,nothing;kw...);fill_pseudo!(child;kw...))
-fill_pseudo!(st,::Nothing;kw...) = (st.P=PseudoInv(st.A;kw...); TunedJacobi!(st.iD,st.A;kw...))
+fill_pseudo!(st,::Nothing;kw...) = (st.P=PseudoInv(st.A;kw...))
 
 # Apply smoother
-pseudo!(st;kw...) = pseudo!(st,st.P;kw...)
-pseudo!(st,nothing;kw...) = nothing # Can't use pseudo! without st.P
+@inline pseudo!(st;kw...) = pseudo!(st,st.P;kw...)
 @fastmath pseudo!(st,P::FieldMatrix;inner=2,kw...) = for _=1:inner
     @loop st.ϵ[I] = mult(I,P.L,P.D,st.r)
     increment!(st)
 end
+# @inline precond!(st;kw...) = Jacobi!(st;kw...)
[…]

### 2021-10-14 tune_synthetic.jl

@@ -2,12 +2,11 @@ using TunedSmoother, Plots, DataStructures
 
 # create synthetic example systems
 data = create_synthetic()
-
+udata = vcat((d[1:17] for (_,d) in data)...)
 # create Parameterized preconditioner and smoother 
 begin
-    pmodels(p) = (D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5]))
-    jmodel(p) = D->1+p[6]+D*(p[7]+D*p[8])
-    p₀ = zeros(Float32,8)
+    pmodels(p) = (D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]*(L-2)+p[5]*(L-1)))
+    p₀ = zeros(Float32,5)
     opt = OrderedDict(name=>p₀ for name ∈ keys(data))
     opt["union"] = p₀
 end
@@ -16,28 +15,11 @@ end
 begin
     for (name,train) ∈ data
         @show name
-        opt[name] = fit(train,opt[name];pmodels,jmodel)
+        opt[name] = fit(train,opt[name];pmodels,precond!)
     end
     @show "union"
-    opt["union"] = fit(vcat((d[1:17] for (_,d) in data)...),opt["union"];pmodels,jmodel)
+    opt["union"] = fit(udata,opt["union"];pmodels,precond!)
     opt
-end
-begin
-    opt = OrderedDict(
-        "2D-static" => Float32[-2.26078, -1.35812, -0.198978, 0.207148, -2.52246f-7, 0.380395, 0.273338, 0.0192435],
-        "3D-static" => Float32[0.806225, 0.190341, 0.00662217, 0.294064, -9.57746f-8, -0.437093, -0.075387, 0.019219],
-        "2D-dipole" => Float32[-1.69299, -0.909276, -0.117421, 0.16275, -4.51364f-8, -0.554424, -0.328334, -0.0425878],
-        "3D-dipole" => Float32[9.18217f-5, -0.000531712, 0.00308433, 0.0623805, 0.0623805, 0.00022871, -0.00152921, 0.00964473],
-        "2D-sphere" => Float32[0.0402841, 0.052108, 0.0132633, 0.447416, -0.290573, -0.144877, -0.137151, -0.00147627],
-        "3D-sphere" => Float32[-0.0343149, -0.0675936, -0.00572602, 0.517866, -0.372514, 0.358447, 0.12475, 0.0276228],
[…]

### 2021-10-17 src/TunedSmoother.jl
update

@@ -1,7 +1,7 @@
 module TunedSmoother
 
 include("candidate_smoothers.jl")
-export Jacobi!,GS!,SOR!,pseudo!,state,precond!
+export Jacobi!,GS!,SOR!,pseudo!,state,precond!,tunedJ!
 
 include("create_synthetic.jl")
 export create_synthetic

### 2021-10-17 src/candidate_smoothers.jl

@@ -11,7 +11,7 @@ using GeometricMultigrid: multL, multU, mult, increment!, δ
     end
     increment!(st;kw...)
 end
-@fastmath function SOR!(st;inner=3,ω=1.15,kw...)
+@fastmath function SOR!(st;inner=3,ω=0.9,kw...)
     @inbounds for I ∈ st.iD.R  # optimized first iteration
         st.ϵ[I] = ω*st.iD[I]*(st.r[I]-multL(I,st.A.L,st.ϵ))
      end
@@ -26,9 +26,9 @@ end
 end
 
 # Parameterized approximate inverse matrix P
-p₀ = Float32[-0.0162363, 0.0304057, 0.0112845, 0.0812823, 0.0784739, -0.00240444, 0.00291828, 0.0062895] # result from tune_synthetic
+p₀ = Float32[-0.191646, -0.0427722, 0.00370673, -0.161197, -0.10299] # result from tune_synthetic
 function PseudoInv(A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
-    pmodels=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5])),kw...) where T
+    pmodels=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]*(L-2)+p[5]*(L-1))),kw...) where T
 
     L,D,N = zeros(T,size(A.L)),zeros(T,size(A.D)),length(size(A.D))
     Dm,Lm = pmodels(p)
@@ -65,12 +65,11 @@ fill_pseudo!(st,::Nothing;kw...) = (st.P=PseudoInv(st.A;kw...))
     @loop st.ϵ[I] = mult(I,P.L,P.D,st.r)
     increment!(st)
 end
-# @inline precond!(st;kw...) = Jacobi!(st;kw...)
-# @inline precond!(st;kw...) = precond!(st,st.P;kw...)
-# @fastmath function precond!(st,P::FieldMatrix;kw...)
-#     @loop st.ϵ[I] = st.r[I]*P.D[I] # pseudo
-#     increment!(st;kw...)
-# end
+@inline tunedJ!(st;kw...) = tunedJ!(st,st.P;kw...)
+@fastmath function tunedJ!(st,P::FieldMatrix;kw...)
+    @loop st.ϵ[I] = st.r[I]*P.D[I] # pseudo
+    increment!(st;kw...)
[…]

### 2021-10-17 tune_synthetic.jl

@@ -55,44 +55,6 @@ begin # precond! = Jacobi!
                 -1.43735   -1.24425    -1.5742   -1.29866    -1.14238   -1.16273  
     ]
 end
-begin # precond! = diagonal only
-    opt = OrderedDict(
-        "2D-static" => Float32[-1.03953, -0.393951, 0.00262573, 0.00874249, -0.14665, 0.0],
-        "3D-static" => Float32[-3.00862, -2.22623, -0.489721, -0.0330752, -0.32141, 0.0],
-        "2D-dipole" => Float32[-1.25025, -0.459942, 0.0290695, 0.0153954, -0.163855, 0.0],
-        "3D-dipole" => Float32[-0.286709, -0.0252308, 0.0206485, 0.00199961, -0.140484, 0.0],
-        "2D-sphere" => Float32[-0.0983752, -0.226187, -0.108934, -0.0154183, -0.160565, -0.196976],
-        "3D-sphere" => Float32[-0.0908512, -0.173352, -0.039595, -0.00301273, -0.158848, -0.219527],
-        "union"     => Float32[0.282169, 0.371521, 0.11341, 0.00893918, -0.151586, -0.092342]
-    )
-    crossloss = [ -1.70152   -0.134349  -1.56018   -0.728549  -0.304495  -0.404324
-                -0.507682  -1.57548   -0.528379  -0.201006  -0.259648  -0.231753
-                -1.27355    1.01485   -1.60315    0.896996   0.605993   0.957853
-                -1.6071    -1.21253   -1.54016   -1.32706   -0.869969  -1.01347
-                -1.28313   -1.28115   -1.58882   -1.20861   -1.17523   -1.19899
-                -0.557009  -1.29971   -1.32476   -1.2153    -0.862389  -1.2427
-                -1.49448   -1.27351   -1.58144   -1.29748   -1.11844   -1.15658
-   ]
-end
-begin # precond! = pseudo!(inner=1)
-    opt = OrderedDict(
-        "2D-static" => Float32[-2.12829, -1.7026, -0.484515, -0.0482328, -0.144186, 0.0],
-        "3D-static" => Float32[-3.61556, -2.39375, -0.504541, -0.0346249, -0.230586, 0.0],
-        "2D-dipole" => Float32[-1.56016, -0.796701, -0.0842826, 0.00336884, -0.166041, 0.0],
-        "3D-dipole" => Float32[-0.173378, -0.0103099, 0.0155066, 0.00122721, -0.150223, 0.0],
[…]

### 2021-10-17 tex/article.tex
Updates from Overleaf

@@
 Deep learning closures for Large Eddy Simulation (LES) \cite{BECK2019108910,maulik_san_rasheed_vedula_2019}, Unsteady Reynolds Averaged Navier-Stokes (unRANS) \cite{ling_kurzawski_templeton_2016}, and even Spanwise Averaged Navier-Stokes (SANS) \cite{font2021deep} simulations have seen growing success and are capable of accurate force prediction.
+However, none of these examples have accelerated the project step itself.
 
@@
 
-A few studies have applied machine-learning to accelerate the critical projection step itself, \cite{ozbay2021poisson,Xiao2020,ajuria2020}.
-All of these approaches use CNNs, attempting to predict the pressure field given the projection source term on a uniform grid, meaning they are limited to cases without internal solid geometries.
+A few studies have applied machine-learning to accelerate the critical projection step itself \cite{ozbay2021poisson,Xiao2020,ajuria2020}.
+All of these approaches use CNNs to predict the pressure field given the projection source term on a uniform grid, meaning they are limited to cases without internal solid geometries.
 While \cite{ozbay2021poisson} uses a decomposition to handle different \textit{domain} boundary conditions and grid aspect ratios in 2D and sees a significant speed-up over traditional Multi-grid methods, the results are still somewhat qualitative, with pressure errors greater than 10\% throughout much of the domain.
@@
 The primary insight of this paper is that Multi-grid methods are \textit{already} convolutional encoder-decoder networks with optimal $O(N\log N)$ scaling, prime for data-driven acceleration without any loss of accuracy in the resulting pressure field.
-This work develops a high-speed data-driven projection method which outperforms classic Multi-grid on eleven 2D and 3D benchmarks including those with immersed solid boundaries.
-Moreover, since the approach is linear in the pressure and the nonlinear dependence on the matrix coefficients are scale-invariant, the data-optimized parameters generalize extremely well to new flows and simulation resolutions.
+This work develops an accurate data-driven projection method which outperforms classic Multi-grid on eleven 2D and 3D benchmarks including those with immersed solid boundaries.
+Moreover, since the new approach is linear in the pressure and the nonlinear dependence on the matrix coefficients are scale-invariant, the data-optimized parameters generalize extremely well to new flows and simulation resolutions.
 
@@
 The matrix is also extremely sparse.
-Using a second-order scheme on structured grids in $M$ dimensions, $A$ has only $M$ non-zero sub-diagonals.
-While the solution vector size $N$ may easily be larger than $10^6$, the matrix-vector multiplication $Ax$ only has computational cost $O(NM)=O(N)$ instead of $O(N^2)$.
+While the solution vector size $N$ may easily be $10^6-10^8$, a second-order scheme on structured grids in $M$ dimensions result in only $M$ non-zero sub-diagonals.
 
@@
 where $r$ is the residual. In practise, only an approximate solution for $\epsilon$ is obtained, after which the solution and residual are incremented
-\begin{equation}
+\begin{equation}\label{eq:increment}
     x^{k+1} = x^k+\epsilon^k, \quad r^{k+1} = r^k-A\epsilon^k.
@@
 The restriction-solve-prolongation process, a V-cycle, distributes the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to smooth the local error in the projected solution.
-The MG architecture proceeds recursively on the reduced-size problems until a small linear algebra problem is reached which can be approximated with minimal cost.
-This recursive approach results in $O(N\log N)$ computational cost.
+The MG architecture proceeds recursively on the reduced-size problems until they are small enough to be solved directly, resulting in $O(N\log N)$ computational cost overall.
+The V-cycle can be repeated until convergence or used as an efficient preconditioner for another iterative solver such as Conjugate Gradient.
 
@@
 As \textit{any} element of the residual of the elliptic Poisson system potentially influences \textit{every} element of the update, $O(N\log N)$ is the best possible solution time scaling.
-However, data-driven methods can still be used to accelerate pressure projection methods by speeding-up and increasing the residual reduction of each V-cycle iteration.
+However, data-driven methods can still be used to accelerate pressure projection by speeding-up and increasing the residual reduction of each V-cycle iteration.
 
@@
 However, this linearity is only with respect to the update and residual fields.
-The operators of the MG method can all potentially be optimized for a specific sub-class of problems.
-In particular, those operators can be made into parameterized nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
+The operators of the MG method can all potentially be made into parameterized nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
 
 Which MG operation is the best candidate for such an approach?
-The prolongation operator (restriction simply being its transpose) is not inherently a function of $A$, and while related super-resolution operators have seen use in the literature, these are always nonlinear functions of the field.
+The prolongation operator (and its transpose restriction operator) is not inherently a function of $A$, and while related super-resolution operators have seen use in the literature, these are nonlinear functions of the field.
 The precondition operator is an option, but a simple Jacobi preconditioner
@@
 %The matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be computed and stored ahead of time.
-As with all stationary smoothers, equation \ref{eq:smooth} can be iterated (an inner loop) at each MG level.
+As with all stationary smoothers, equation \ref{eq:smooth} can be iterated with equation \ref{eq:increment} in an inner loop at each MG level.
 Unlike Gauss-Sidel or SOR smoothers, the matrix-vector multiplication smoother requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
@@
 and determined using Newton's method.
-Automatic differentiation (AD) is used to determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ \cite{RevelsLubinPapamarkou2016}, avoiding inaccurate and potentially unstable finite differences of the nonlinear recursive loss function.
+The residual loss function is a highly nonlinear recursive function of the parameters, but automatic differentiation (AD) is used to determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ \cite{RevelsLubinPapamarkou2016}, avoiding inaccurate and potentially unstable finite differences.
 
@@
 This manuscript develops a successful data-driven method to accelerate the solution of discrete pressure Poisson systems found in incompressible flow simulations.
-Mathematical constraints are used to focus the learning capacity to a parameterized Jacobi-like Multi-grid smoother.
-Being a sparse matrix-vector multiplication, this function is nearly as fast as a trivial Jacobi smoother, and much faster than Gauss-Sidel or SOR smoothing.
-After using automatic-differentiation for training, the data-driven MG method is found to accelerate projection by 66-185\% on eleven simulation cases.
-Because of the reduced learning capacity, the generalization is excellent, enabling 90\% effective transfer learning from a synthetic data-set and essentially perfect transfer from reduced resolution simulations.
+Multi-grid methods are identified as linear convolutional encoder-decoder networks with optimal ($N\log N$) scaling, and the matrix coefficients are identified as the critical nonlinear input, not the projection source-term, embedding information such as boundary conditions.
+Mathematical constraints are used to further focus the learning capacity to a parameterized Jacobi-like Multi-grid smoother.
+This resulting data-driven MG solver is with 33\% of the minimum computational cost per V-cycle, and shown to outperform classic Gauss-Sidel and SOR smoothers by 66-185\% on eleven simulation cases.
+Because of the focused learning capacity, the generalization is excellent, enabling 90\% effective transfer learning from a synthetic data-set and essentially perfect transfer from reduced resolution simulations.
 

### 2021-10-18 src/candidate_smoothers.jl
More careful with metrics

@@ -26,7 +26,7 @@ end
 end
 
 # Parameterized approximate inverse matrix P
-p₀ = Float32[-0.191646, -0.0427722, 0.00370673, -0.161197, -0.10299] # result from tune_synthetic
+p₀ = Float32[-0.104447, -0.00238399, 0.00841367, -0.158046, -0.115103] # result from tune_synthetic
 function PseudoInv(A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
     pmodels=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]*(L-2)+p[5]*(L-1))),kw...) where T
 

### 2021-10-18 src/metrics.jl

@@ -1,13 +1,16 @@
-using GeometricMultigrid: mg!
+using GeometricMultigrid: mg!,Vcycle!,norm
 using Optim
 
 # count average V-cycles to get reltol 1e-3
-itcount(d,s;kw...) = mg!(state(d...;smooth! = s,kw...);reltol=1e-3,smooth! = s, mxiter=32, kw...)
+itcount(d,s;kw...) = mg!(state(d...;smooth! = s,kw...);reltol=1e-3,abstol=0,smooth! = s, mxiter=32, kw...)
 avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
 
 # measure average residual reduction after it V-cycles
-Δresid(st;it=1,kw...) = (resid = mg!(st;mxiter=it,log=true,kw...);
-                        log10(resid[end]/resid[1])/it)
+function Δresid(st;it=1,kw...)
+    r₀ = norm(st.r)
+    for _ in 1:it; Vcycle!(st;kw...); end
+    return log10(norm(st.r)/r₀/it)
+end
 loss(data;p=p₀,kw...) = sum(Δresid(state(d...;p,kw...);p,kw...) for d ∈ data)/length(data)
 
 # optimize parameters to minimize loss

### 2021-10-18 tune_synthetic.jl

@@ -5,6 +5,7 @@ data = create_synthetic()
 udata = vcat((d[1:17] for (_,d) in data)...)
 # create Parameterized preconditioner and smoother 
 begin
+    pre = Jacobi!
     pmodels(p) = (D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]*(L-2)+p[5]*(L-1)))
     p₀ = zeros(Float32,5)
     opt = OrderedDict(name=>p₀ for name ∈ keys(data))
@@ -15,53 +16,62 @@ end
 begin
     for (name,train) ∈ data
         @show name
-        opt[name] = fit(train,opt[name];pmodels,precond!)
+        opt[name] = fit(train,opt[name];pmodels,precond! =pre)
     end
     @show "union"
-    opt["union"] = fit(udata,opt["union"];pmodels,precond!)
+    opt["union"] = fit(udata,opt["union"];pmodels,precond! =pre)
     opt
 end
-
-begin
-    using Plots
-    a,b = pmodels(opt["union"])
-    c = jmodel(opt["union"])
-    display(plot(0:0.01:1,b,label="smoother",size=(400,400),
-         xaxis=("aᵢⱼ"),yaxis=("fᵢⱼ"),legend=:bottomleft))
-    plot(-6:0.1:0,c,label="preconditioner",size=(400,400),
-         xaxis=("aᵢᵢ"),yaxis=("fᵢᵢ"),legend=:bottomleft)
-    plot!(-6:0.1:0,a,label="smoother")
-end
+# opt[name] = fit(data[name],opt[name];pmodels,precond! =pre)
 
 # compare across example types
-crossloss = [loss(test;p,smooth! = pseudo!,pmodels,precond!) for (_,p) ∈ opt, (_,test) ∈ data]
+crossloss = [loss(test;p,smooth! = pseudo!,pmodels,precond! = pre) for (_,p) ∈ opt, (_,test) ∈ data]
 
-begin # precond! = Jacobi!
+begin # pre = Jacobi!
     opt = OrderedDict(
-        "2D-static" => Float32[-2.46273, -1.32142, -0.175033, -0.145183, 0.0],
-        "3D-static" => Float32[0.935289, 0.210679, 0.00503365, -0.32304, 0.0],
-        "2D-dipole" => Float32[2.44271, 1.50327, 0.227535, -0.165192, 0.0],
[…]

### 2021-10-18 benchmark.jl
Redo benchmark

@@ -15,15 +15,15 @@ begin # run benchmarks and count iterations
     time_factor = times[2:end,:]./times[1,:]'
 end
 
-counts = [avecount(d,pseudo!;p) for (_,d) ∈ data]
+counts = [avecount(d,s;p=TunedSmoother.p₀) for s ∈ smoothers[2:end], (_,d) ∈ data]
 
 begin # results from block above
     time_factor = [ 3.50716   2.72302   3.5       2.73946   3.51437   2.71142
-                    4.75072   3.24036   4.74      3.21826   4.76437   3.19066
+                    3.19072   3.12036   3.19      3.12826   3.1877    3.13066
                     1.37096   1.56152   1.36767   1.54179   1.36671   1.54011]
-    counts = [  3.0  4.0  1.5   1.17  3.98  3.55
-                4.0  3.0  1.55  1.16  3.96  3.0
-                2.5  3.0  1.00  1.04  3.18  3.0]
+    counts = [  3.0  4.0  1.58  2.04  3.0  3.0
+                4.0  3.0  1.7   2.05  3.0  3.9
+                3.0  3.0  1.57  2.04  3.16  3.0]
     rel_time = counts.*time_factor
     accel = rel_time[1:2,:]./rel_time[3,:]' # speed up!!
 end
@@ -36,7 +36,7 @@ begin # plot
     ctg = CategoricalArray(repeat(cats,inner=n))
     levels!(ctg,cats)
     groupedbar((counts.*time_factor)',size=(400,350),
-                group=ctg,c=colors,
+                group=ctg,c=colors,legend=:bottomright, 
                 yaxis=("relative time"),
                 xaxis=("cases",(1:n,keys(data)),60))
 end

### 2021-10-19 test_waterlily.jl
Strict counting made a big change in the Waterlily results

@@ -73,22 +73,22 @@ begin
 end
 
 begin
-    scaledata = make_data(p=4)
-    scaledata[wing] = filter(d->itcount(d;smooth! =GS!)<32,scaledata[wing])
+    scaledata = create_waterlily(p=4)
+    scaledata[wing] = filter(d->itcount(d,GS!)<32,scaledata[wing])
     opt2 = OrderedDict(name=>fit(train;it=2) for (name,train) ∈ scaledata)
 end
 begin
     opt2 = OrderedDict(
-        circle => [0.412175, 0.288861, 0.0510388, 0.72032, -0.554927],
-        TGV    => [-0.447214, -0.169634, -0.00902928, 0.349716, -0.2018],
-        donut  => [0.162644, 0.0423348, 0.00964613, 0.347914, -0.198642],
-        wing   => [-0.433754, -0.436679, -0.0765471, 0.703688, -0.523553],
-        shark  => [0.124323, -0.063333, -0.0169111, 0.660478, -0.474286])
+        circle => [0.143874, 0.114321, 0.024359, -0.166979, -0.211477],
+        TGV    => [-0.445326, -0.175383, -0.0100868, -0.147759, 0.0],
+        donut  => [0.120699, 0.0239083, 0.00775287, -0.149375, -0.0753296],
+        wing   => [0.0259308, -0.123091, -0.0268147, -0.174569, -0.542901],
+        shark  => [0.0673034, -0.104414, -0.0241938, -0.182964, -0.298915]
+    )
 end
 
 # time a single Vcycle
 begin
-    using 
     temp!(st;kw...) = mg!(st;inner=2,mxiter=1,kw...)
     jacobi_time = @belapsed temp!(st;smooth! = Jacobi!) setup=(st=state($data[shark][1]...)) #
     gauss_time = @belapsed temp!(st;smooth! = GS!) setup=(st=state($data[shark][1]...)) #
@@ -98,16 +98,18 @@ begin
     sor_time /= jacobi_time
     pseudo_time /= jacobi_time
 end
+gauss_time = 3.5; sor_time = 3.2; pseudo_time = 1.37
 
 # Count the number of cycles needed
-crosscount = [[avecount(d;smooth! = GS!) for (_,d) ∈ data]'.*gauss_time
-              [avecount(d;smooth! = SOR!) for (_,d) ∈ data]'.*sor_time
[…]

### 2021-10-19 test_waterlily.jl
updated function figures

@@ -45,33 +45,6 @@ begin
 end
 savefig("scaleloss.png")
 
-# plot best pseudo-inverse functions across examples
-begin
-    using Plots
-    models=p->(D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]+L*p[5]))
-    a,_ = models(p₀)
-    plot(-6:0.1:0,a,label="transfer",size=(400,400),
-         xaxis=("aᵢᵢ"),yaxis=("fᵢᵢ"),legend=:bottomleft)
-    for (name,p) in opt
-        x = name ∈ (TGV,donut) ? (-6:0.1:0) : (-4:0.1:0)
-        a,_ = models(p)
-        plot!(x,a,label=name)
-    end
-    display(plot!(-6:0,i->1,label="jacobi",c=:grey))
-    savefig("diag_fun.png")
-
-    x = 0:0.02:1
-    _,a = models(p₀)
-    plot(x,a,label="transfer",size=(400,400),
-         xaxis=("aᵢⱼ"),yaxis=("fᵢⱼ"),legend=:bottomright)
-    for (name,p) in opt
-        _,a = models(p)
-        plot!(x,a,label=name)
-    end
-    display(plot!(x,i->0,label="jacobi",c=:grey))
-    savefig("lower_fun.png")
-end
-
 begin
     scaledata = create_waterlily(p=4)
     scaledata[wing] = filter(d->itcount(d,GS!)<32,scaledata[wing])
@@ -124,6 +97,34 @@ begin
                 xaxis=("cases",(1:length(data),keys(data))),)
 end
 savefig("crosscount.png")
+
+# plot best pseudo-inverse functions across examples
+begin
+    using Plots
+    p₀ = Float32[-0.104447, -0.00238399, 0.00841367, -0.158046, -0.115103]
+    pmodels(p) = (D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]*(L-2)+p[5]*(L-1)))
+    a,_ = pmodels(p₀)
+    plot(-6:0.1:0,a,label="transfer",size=(400,400),
+         xaxis=("aᵢᵢ"),yaxis=("fᵢᵢ"),legend=:bottomleft)
+    for (name,p) in opt2
+        x = name ∈ (TGV,donut) ? (-6:0.1:0) : (-4:0.1:0)
+        a,_ = pmodels(p)
+        plot!(x,a,label=name)
+    end
[…]

### 2021-10-19 tex/article.tex
Updates from Overleaf

@@
 \begin{figure}
-    \caption{Sketch of a Convolutional Neural Networks (CNN) and/or a Multi-grid V-cycle.}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/drawing}
+    \caption{Sketch of a Convolutional Neural Networks (CNN) encoder/decoder and/or a Multi-grid V-cycle.
+Data is restricted down to a reduced size for faster solving before being pushed back up to the full size.
+A single reduction is shown, but this process repeats recursively.}
     \label{fig:multigrid}
@@
 The linearity of equation \ref{eq:aer} is a critical property which the data-driven method must maintain.
-Not only will this increase generality, but a nonlinear method could not be used iteratively since the modes of the residual will change as the solver converges.
+Consider that the modes of the residual will change as the solver converges for even a single project case, meaning that a nonlinear method could not be applied iteratively.
 However, this linearity is only with respect to the update and residual fields.
@@
 Which MG operation is the best candidate for such an approach?
-The prolongation operator (and its transpose restriction operator) is not inherently a function of $A$, and while related super-resolution operators have seen use in the literature, these are nonlinear functions of the field.
+There is certainly scope for optimization in the prolongation operator (and its transpose restriction operator) in algebraic multi-grid methods.
+
+is not inherently a function of $A$, and while related super-resolution operators have seen use in the literature, these are nonlinear functions of the field.
 The precondition operator is an option, but a simple Jacobi preconditioner
@@
 where function inputs are scaled by the maximum off-diagonal $s=\max(A-D)$ and the outputs are scaled by the diagonal elements.
-Note a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal function $f_o=0$.
-With the learning problem now reduced to two normalized single-variable functions, the specific choice of parameterization is not critical and a simple quadratic polynomial $f(a) = \sum_{p=0}^2 a^p \theta_p$ is chosen for $f_o$ and $f_d$.
+Note a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal function $f_o=0$ and that $f_0(0)=0$ is required to maintain the sparsity of $\tilde A^{-1}$.
+With the learning problem now reduced to two normalized single-variable functions, the specific choice of parameterization is not critical and a simple cubic is chosen for $f_d$ and $f_o$.
 Using higher-order polynomials, splines, and interpolating kernels did not significantly change the results.
@@
 Figure~\ref{fig:synthetic time} shows the time to reduce the residual of each case by $10^{-3}$ relative to the time to run a single V-cycle using a Jacobi smoother.
-While a Jacobi smoother requires  hundreds or even thousands of V-cycles to converge, the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, and yet converges in only 1-3 V-cycles in all cases.
-This results in a 80-174\% speed-up (mean: 119\%) relative to optimized serial Gauss-Sidel and SOR smoothers.
+The Jacobi smoother is not sufficient to solve even these simple synthetic problems rapidly, requiring many hundreds o V-cycles.
+Yet, the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, and converges in only 1-3 V-cycles in all cases.
+This results in a 80-210\% speed-up (mean: 133\%) relative to optimized serial Gauss-Sidel and SOR smoothers.
 This speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any additional communication.
@@
     \centering
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[a]{\textwidth}
         \centering 
-        \caption{circle flow}
-        \label{fig:circle}
+        \includegraphics[width=\textwidth]{figures/circletriple.png}
+        \caption[-1mm]{Circle flow}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \centering
-        \caption{Taylor-Green Vortex}
-        \label{fig:TGV}
+        \includegraphics[width=\textwidth]{figures/donuttriple.png}
+        \caption{Torus flow (slice)}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[c]{0.6\textwidth}
         \centering
-        \caption{flapping wing}
-        \label{fig:wing}
+        \includegraphics[width=\textwidth]{figures/TGVtriple.png}
+        \caption{Taylor-Green Vortex (slice)}
     \end{subfigure}
-    % \begin{minipage}{0.47\textwidth}
-        \begin{subfigure}{0.47\textwidth}
+    \begin{subfigure}[c]{0.6\textwidth}
         \centering
-        \caption{torus flow}
-        \label{fig:donut}
+        \includegraphics[width=\textwidth]{figures/wingtriple.png}
+        \caption{Flapping wing}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/sharktriple.png}
+        \caption{Swimming shark}
     \end{subfigure}
     \hfill
-        \begin{subfigure}{0.47\textwidth}
-        \centering
-        \caption{swimming shark}
-        \label{fig:shark}
-        \end{subfigure}
-    % \end{minipage}
-    \hfill
-    % \begin{subfigure}[b]{0.47\textwidth}
-    %     \centering
-    %     \includegraphics[width=\textwidth]{figures/compareloss.png}
-    %     \caption{single-cycle residual reduction}
-    %     \label{fig:simulation residual}
-    % \end{subfigure}
-    \caption{(a-e) Snapshots from the five flow simulation cases.
-The Taylor-Green Vortex and torus flow are 3D, the flapping wing is dynamic without a background flow and the swimming shark is a deforming geometry.}
+    \caption{Snapshots from the five flow simulation cases showing the pressure solution (left), the initial residual (middle), and the residual after a single V-cycle (right).
+The Taylor-Green Vortex and torus flow are 3D, the flapping wing is dynamic without a background flow and the swimming shark is a deforming geometry.
+All residuals are visualized using $\log_{10}\text{abs}(r)$ on the same scale, $10^{-6} \ldots 10^{-1}$.}
     \label{fig:simulation cases}
@@
 Finally, the parameterized $f_d,\,f_o$ functions used in the approximate inverse equation \ref{eq:approxinv} are shown in Figure \ref{fig:tuned inverse}.
-It is interesting to note that the diagonal functions are all somewhat centered on one and the off-diagonal values all have an essentially zero intercept as these are the values for the Jacobi smoother.
+It is interesting to note that the diagonal functions are all somewhat centered on one, the value for the Jacobi smoother.
 We also note that the `wing' and `shark' cases produce parameterizations which are similar to each other but significantly different than the others cases.
@@
 
-The potential of machine learning and computer science advances to improve fluid dynamics is vast, but well-applied classical methods and constraints only helps to focus this effort.
+The potential of machine learning advances to improve fluid dynamics is vast, but well-applied classical methods and constraints are needed to focus this potential.
 Wherever possible, this work has made the simplest choice in parameterization, leaving significant opportunities for future improvements.

### 2021-10-19 test_waterlily.jl
Add shark.gif

@@ -70,8 +70,8 @@ begin
     gauss_time /= jacobi_time
     sor_time /= jacobi_time
     pseudo_time /= jacobi_time
+    # gauss_time = 3.5; sor_time = 3.2; pseudo_time = 1.37
 end
-gauss_time = 3.5; sor_time = 3.2; pseudo_time = 1.37
 
 # Count the number of cycles needed
 crosscount = [[avecount(d,GS!) for (_,d) ∈ data]'.*gauss_time
@@ -128,9 +128,8 @@ end
 
 begin
     using GeometricMultigrid: Vcycle!
-    # for (name,h) in ((circle,160),(wing,300),(shark,160))
+    for (name,h) in ((circle,160),(wing,300),(shark,160))
     # for (name,h) in ((TGV,300),)
-    for (name,h) in ((wing,300),)
     # for (name,h) in ((donut,160),)
             smooth! = pseudo!
         # st = state(data[name][25]...;smooth!)
@@ -152,3 +151,19 @@ begin
         savefig(string(name)*"triple.png")
     end
 end
+begin
+    name = shark
+    anim = @animate for d in data[name]
+        st = state(d...)
+        x = copy(st.x.data)
+        x .-= st.x[1]
+        x[st.A.D .> -1.5] .= NaN
+        r = copy(st.r)
+        f(x) = @. log10(clamp(abs(x),1e-6,Inf64))
+        plot(heatmap(x[st.x.R]', legend=false, c=:bluesreds, clims=(-1,1)),
+             heatmap(f(r.data[st.x.R]'), legend=false, c=:Reds, clims=(-6,-1)),
+             layout=(1,2), size=(1000,250), axis=nothing)
+    end
+    gif(anim,string(name)*".gif")
+end
+

### 2021-10-20 tune_synthetic.jl
Add jacobi back to crossloss

@@ -8,8 +8,7 @@ begin
     pre = Jacobi!
     pmodels(p) = (D->1+p[1]+D*(p[2]+D*p[3]),L->L*(p[4]*(L-2)+p[5]*(L-1)))
     p₀ = zeros(Float32,5)
-    opt = OrderedDict(name=>p₀ for name ∈ keys(data))
-    opt["union"] = p₀
+    opt = OrderedDict(name=>p₀ for name ∈ ["Jacobi" keys(data)... "union"])
 end
 
 # optimize Parameterized smoother
@@ -22,13 +21,14 @@ begin
     opt["union"] = fit(udata,opt["union"];pmodels,precond! =pre)
     opt
 end
-# opt[name] = fit(data[name],opt[name];pmodels,precond! =pre)
+# name = "3D-static"; opt[name] = fit(data[name],opt[name];pmodels,precond! =pre)
 
 # compare across example types
 crossloss = [loss(test;p,smooth! = pseudo!,pmodels,precond! = pre) for (_,p) ∈ opt, (_,test) ∈ data]
 
 begin # pre = Jacobi!
-    opt = OrderedDict(
+    opt = OrderedDict( 
+        "Jacobi"    => [0.0, 0.0, 0.0, 0.0, 0.0],
         "2D-static" => [-2.46273, -1.32142, -0.175033, -0.145183, 0.0],
         "3D-static" => [0.935464, 0.210724, 0.00503401, -0.323074, 0.0],
         "2D-dipole" => [-0.00244387, 0.00340375, 0.00547249, -0.164399, 0.0],
@@ -37,7 +37,8 @@ begin # pre = Jacobi!
         "3D-sphere" => [-0.0477943, -0.0800523, -0.00728708, -0.160163, -0.222702],
         "union"     => [-0.104447, -0.00238399, 0.00841367, -0.158046, -0.115103],
     )
-    crossloss = [ -1.55321    0.640408  -1.64163   -0.0148446   0.557276   0.427443
+    crossloss = [-0.149117  -0.0530345  -0.572381  -0.751236    -0.17155   -0.447677
+                 -1.55321    0.640408  -1.64163   -0.0148446   0.557276   0.427443
                 -0.499442  -1.58268   -0.519982   0.0663901  -0.159964  -0.137229
                 -1.17578   -1.2567    -1.68493   -1.42541    -1.15548   -1.18972
[…]

### 2021-10-20 test_waterlily.jl
Add Jacobi to scaleloss

@@ -6,14 +6,15 @@ data = create_waterlily()
 # Optimize the psuedo-inverse functions
 begin # this block takes around 30 minutes. the next block has the results
     smooth! = pseudo!
+    scaleloss = zeros(Float32,6,length(data))
+    scaleloss[1,:] .= [loss(test;p=zeros(Float32,5),smooth!) for (name,test) ∈ data]
+    scaleloss[2,:] .= [loss(test;p=p₀,smooth!) for (name,test) ∈ data]
     opt = OrderedDict(name=>p₀ for name ∈ keys(data))
-    scaleloss = zeros(5,length(opt))
-    scaleloss[1,:] .= [loss(test;p=p₀,smooth!) for (name,test) ∈ data]
     for scale ∈ 1:4
         @show scale
         scaledata = scale==4 ? data : create_waterlily(p=scale+2,cases=keys(data))
         opt = OrderedDict(name=>fit(train,opt[name]) for (name,train) ∈ scaledata)
-        scaleloss[scale+1,:] .= [loss(test;p=opt[name],smooth!) for (name,test) ∈ data]
+        scaleloss[scale+2,:] .= [loss(test;p=opt[name],smooth!) for (name,test) ∈ data]
     end
 end
 
@@ -25,21 +26,22 @@ begin # output from the block above
         wing   => [-0.229121, -0.253223, -0.042952, 0.782714, -0.604938, -0.00708945, 0.0287928, 0.00663962],
         shark  => [-0.279771, -0.281626, -0.0476559, 0.821296, -0.649919, -0.00109436, 0.055443, 0.00988565])
 
-    scaleloss= [-1.75374  -1.52343  -1.48713  -1.37156  -1.45274
+    scaleloss= [-0.46811  -0.63303  -0.64559  -0.52364  -0.58142
+                -1.75374  -1.52343  -1.48713  -1.37156  -1.45274
                 -1.7893   -1.69872  -1.63804  -1.42732  -1.46177
-                -1.81289  -1.73545  -1.64428  -1.42765  -1.46817
-                -1.80914  -1.73749  -1.65463  -1.43041  -1.48582
+                -1.81289  -1.73545  -1.64428  -1.42765  -1.48817
+                -1.80914  -1.73749  -1.65463  -1.43041  -1.49582
                 -1.82367  -1.73825  -1.65887  -1.4328   -1.50249]
 end
 
 # plot loss across examples and scales
 begin
     using StatsPlots,CategoricalArrays
[…]

### 2021-10-20 src/metrics.jl
fixed typo for it>1

@@ -9,11 +9,11 @@ avecount(data,s;kw...) = sum(itcount(d,s;kw...) for d ∈ data)/length(data)
 function Δresid(st;it=1,kw...)
     r₀ = norm(st.r)
     for _ in 1:it; Vcycle!(st;kw...); end
-    return log10(norm(st.r)/r₀/it)
+    return log10(norm(st.r)/r₀)/it
 end
 loss(data;p=p₀,kw...) = sum(Δresid(state(d...;p,kw...);p,kw...) for d ∈ data)/length(data)
 
 # optimize parameters to minimize loss
-fit(data,p₀=zeros(Float32,5);smooth! = pseudo!,kw...) = Optim.minimizer(
+fit(data,p₀;smooth! = pseudo!,kw...) = Optim.minimizer(
     optimize(p->loss(data;p,smooth!,kw...),p₀, Newton(),
     Optim.Options(time_limit=120,show_trace=true,f_tol=1e-4); autodiff = :forward))

### 2021-10-21 tex/article.tex
Updates from Overleaf

@@
 Pressure projection is the single most computationally expensive step in an unsteady incompressible fluid simulation.
-This work discusses the potential of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection, linking Multi-grid methods to convolutional encoder-decoder networks.
-Required to maintain linearity in pressure, the best option for data-driven acceleration is in the smoothing step.
-Using automatic differentiation, a high-speed parameterized smoother is developed which accelerates classic Multi-grid methods by 66-185\% on eleven 2D and 3D benchmarks with no loss of accuracy.
-The tuned parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of general flows.
+This work discusses the potential of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection, linking Multi-grid methods to linear convolutional encoder-decoder networks.
+A high-speed Jacobi-like parameterized smoother is developed and optimized using automatic differentiation on the recursive log-residual loss function.
+The new method is found to accelerate classic Multi-grid methods by a factor of 2-3 with no loss of accuracy on eleven 2D and 3D flow cases including cases with dynamic immersed solid boundaries.
+The optimal parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of general flows.
 \end{abstract}
@@
 
-Recent advances in data-driven acceleration of flow solvers have mainly focused on data-assimilation methods and data-driven turbulence closures.
-Data-assimilation methods typically avoid the expensive pressure projection step entirely, focusing on applications where time-accurate pressure forces are not important \cite{asch2016data}.
-Deep learning closures for Large Eddy Simulation (LES) \cite{BECK2019108910,maulik_san_rasheed_vedula_2019}, Unsteady Reynolds Averaged Navier-Stokes (unRANS) \cite{ling_kurzawski_templeton_2016}, and even Spanwise Averaged Navier-Stokes (SANS) \cite{font2021deep} simulations have seen growing success and are capable of accurate force prediction.
-However, none of these examples have accelerated the project step itself.
-
 \begin{figure}
@@
     \includegraphics[width=0.8\textwidth]{figures/drawing}
-    \caption{Sketch of a Convolutional Neural Networks (CNN) encoder/decoder and/or a Multi-grid V-cycle.
-Data is restricted down to a reduced size for faster solving before being pushed back up to the full size.
-A single reduction is shown, but this process repeats recursively.}
+    \caption{Sketch of a convolutional encoder-decoder network and/or a geometric multi-grid V-cycle.
+Data is restricted down to a reduced size for faster processing before being pushed back up to the full size.
+A two-level V-cycle is shown, but this process repeats recursively between the largest and smallest grid levels.}
     \label{fig:multigrid}
@@
 
-Many of these turbulence closures as well as other fluids applications such as super-resolution \cite{ferdian20204dflownet,liu2020deep} and full field regression models \cite{duru2021cnnfoil,bhatnagar2019prediction} are based on Convolutional Neural Networks (CNN) and encoder-decoder architectures.
-CNNs have inherent translational symmetry and encoder-decoder architectures reduce the number of variables before expanding again, Figure \ref{fig:multigrid}, both of which help constrain learning capacity and generalize the trained networks to unseen prediction cases.
+Advances in data-driven acceleration of flow solvers have mainly focused on reducing simulation resolution using data-assimilation and data-driven turbulence closures \cite{asch2016data,BECK2019108910,maulik_san_rasheed_vedula_2019,ling_kurzawski_templeton_2016,font2021deep} without focusing on projection explicitly.
+Many of these approaches utilize Convolutional Neural Networks (CNN), Figure \ref{fig:multigrid}, which have been successfully applied in other fluids applications such as super-resolution \cite{liu2020deep} and full field regression models \cite{bhatnagar2019prediction}.
+CNNs have inherent translational symmetry and encoder-decoder architectures reduce the number of variables before expanding again, both of which help constrain learning capacity and generalize the trained networks to unseen prediction cases.
 
-A few studies have applied machine-learning to accelerate the critical projection step itself \cite{ozbay2021poisson,Xiao2020,ajuria2020}.
-All of these approaches use CNNs to predict the pressure field given the projection source term on a uniform grid, meaning they are limited to cases without internal solid geometries.
-While \cite{ozbay2021poisson} uses a decomposition to handle different \textit{domain} boundary conditions and grid aspect ratios in 2D and sees a significant speed-up over traditional Multi-grid methods, the results are still somewhat qualitative, with pressure errors greater than 10\% throughout much of the domain.
+A few recent studies have applied machine-learning to accelerate the critical projection step itself \cite{ozbay2021poisson,Xiao2020,ajuria2020} using CNNs to predict the pressure field given the projection source term.
+All of these method assume a uniform grid without internal solid geometries, although \cite{ozbay2021poisson} uses a decomposition to handle different \textit{domain} boundary conditions and grid aspect ratios in 2D.
+Unfortunately, the methods can't be applied to most simulation problems and the results are still somewhat qualitative, with pressure errors greater than 10\% throughout much of the domain \cite{ozbay2021poisson}.
 
-The primary insight of this paper is that Multi-grid methods are \textit{already} convolutional encoder-decoder networks with optimal $O(N\log N)$ scaling, prime for data-driven acceleration without any loss of accuracy in the resulting pressure field.
-This work develops an accurate data-driven projection method which outperforms classic Multi-grid on eleven 2D and 3D benchmarks including those with immersed solid boundaries.
+A key insight is that classic Geometric Multi-Grid (GMG) methods \cite{briggs2000multigrid} are simply \textit{linear} convolutional encoder-decoder networks, Figure \ref{fig:multigrid}, prime for data-driven acceleration without any loss of accuracy in the resulting pressure field.
+While there is a long history of optimizing multi-grid methods (both geometric \cite{oosterlee2003genetic} and algebraic \cite{brezina2006adaptive}), few of these have taken a direct data-driven approach.
+Recent work \cite{KATRUTSA2020112524,greenfeld2019learning} has shown promising initial results in constructing data-driven restriction and prolongation operators, but both use idealized systems and do not show overall speed-up compared to classic methods, so their utility in accelerating real pressure projection problems is untested.
+
+Building on this foundation, this work develops a simple and accurate data-driven projection method which outperforms classic geometric multi-grid on eleven 2D and 3D benchmarks including those with immersed solid boundaries.
 Moreover, since the new approach is linear in the pressure and the nonlinear dependence on the matrix coefficients are scale-invariant, the data-optimized parameters generalize extremely well to new flows and simulation resolutions.
@@
 \end{equation}
-This process is iterated until the residual is reduced sufficiently, the required tolerance level being highly dependant on the application.
+This process is iterated until the residual is reduced to a specified level.
 
-Multi-grid (MG) methods are among the fastest iterative solution approaches for variable coefficient discrete pressure Poisson equations because the MG operator is effectively a \textit{linear} convolutional encoder-decoder network, Figure \ref{fig:multigrid}.
-The system is preconditioned before the residual is restricted down to a reduced-size problem and the correction is prolongated back up.
+Geometric Multi-Grid (GMG) methods are among the fastest iterative solution approaches for variable coefficient discrete pressure Poisson equations.
+A single iteration of GMG is called a V-cycle and consists of (i) a solution precondition step, (ii) residual restriction down to the reduced-size problem, (iii) approximate solution of this problem, (iv) solution prolongation back up to correct the fine grid, and (v) solution smoothing.
+This process is recursive, being applied to the reduced-size problems until they are small enough to be solved directly, resulting in $O(N\log N)$ computational cost overall.
 % \begin{equation}
@@
 % where $R$ is the $N_c \times N$ restriction operator, $P$ is the $N \times N_c$ prolongation operator 
-The restriction-solve-prolongation process, a V-cycle, distributes the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to smooth the local error in the projected solution.
-The MG architecture proceeds recursively on the reduced-size problems until they are small enough to be solved directly, resulting in $O(N\log N)$ computational cost overall.
+The first four steps of the V-cycle distribute the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to effectively smooth the local error in the projected solution.
 The V-cycle can be repeated until convergence or used as an efficient preconditioner for another iterative solver such as Conjugate Gradient.
@@
 The linearity of equation \ref{eq:aer} is a critical property which the data-driven method must maintain.
-Consider that the modes of the residual will change as the solver converges for even a single project case, meaning that a nonlinear method could not be applied iteratively.
+Consider that the modes of the residual will change as the solver converges, meaning that a nonlinear method could not be applied iteratively.
 However, this linearity is only with respect to the update and residual fields.
-The operators of the MG method can all potentially be made into parameterized nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
+The operators of the MG method can all potentially be (implicit or explicit) nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
 
 Which MG operation is the best candidate for such an approach?
-There is certainly scope for optimization in the prolongation operator (and its transpose restriction operator) in algebraic multi-grid methods.
+As discussed in the introduction, significant effort has focused on optimization of the prolongation operator and its transpose restriction operator.
+The prolongation operator is an \textit{implicit} function of $A$, making their construction difficult in algebraic settings and their optimization mathematically and numerically complex even in geometric settings \cite{KATRUTSA2020112524,greenfeld2019learning}.
+Note that super-resolution operators are related to prolongation, but would violate the linearity constraint.
 
-is not inherently a function of $A$, and while related super-resolution operators have seen use in the literature, these are nonlinear functions of the field.
-The precondition operator is an option, but a simple Jacobi preconditioner
+Another option is the precondition operator, but a simple Jacobi preconditioner
 \begin{equation}
@@
 \end{equation}
-where $D$ is the diagonal of $A$, is as fast as possible and is sufficient for the V-cycle to distribute the residual throughout the domain.
-Therefore, for the remainder of the paper we will focus on the smoother as the best candidate for parameterization, using a simple Jacobi preconditioner and uniform pooling/distribution for restriction/prolongation.
+where $D$ is the diagonal of $A$, is sufficient for the V-cycle to distribute the residual throughout the domain and is as fast as possible; being a single Schur (broadcasted) vector product.
+Therefore, for the remainder of the paper we will use a simple Jacobi preconditioner and uniform pooling/distribution for restriction/prolongation and focus on a parameterized smoothing operator.
 
@@
 where $\tilde A^{-1}=f(A\,|\theta)$ is an approximate matrix-inverse with the same sparsity as $A$ and parameter vector $\theta$.
-%The matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be computed and stored ahead of time.
-As with all stationary smoothers, equation \ref{eq:smooth} can be iterated with equation \ref{eq:increment} in an inner loop at each MG level.
-Unlike Gauss-Sidel or SOR smoothers, the matrix-vector multiplication smoother requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
+The matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be computed and stored ahead of time.
+And unlike Gauss-Sidel or SOR smoothers, the matrix-vector multiplication of equation \ref{eq:smooth} requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
 
@@
 where function inputs are scaled by the maximum off-diagonal $s=\max(A-D)$ and the outputs are scaled by the diagonal elements.
-Note a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal function $f_o=0$ and that $f_0(0)=0$ is required to maintain the sparsity of $\tilde A^{-1}$.
-With the learning problem now reduced to two normalized single-variable functions, the specific choice of parameterization is not critical and a simple cubic is chosen for $f_d$ and $f_o$.
+Note that $f_o(0)=0$ is required to maintain the sparsity of $\tilde A^{-1}$ and that a Jacobi smoother would use a diagonal function $f_d=1$ and off-diagonal function $f_o=0$.
+With the optimization problem now reduced to two normalized single-variable functions, the specific choice of parameterization is not critical and a simple quadratic is chosen for $f_d$ and $f_o$.
 Using higher-order polynomials, splines, and interpolating kernels did not significantly change the results.
@@
 \end{equation}
-and determined using Newton's method.
-The residual loss function is a highly nonlinear recursive function of the parameters, but automatic differentiation (AD) is used to determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ \cite{RevelsLubinPapamarkou2016}, avoiding inaccurate and potentially unstable finite differences.
+The residual loss function is a highly nonlinear recursive function of the parameters, but automatic differentiation (AD) is used to determine the gradient $\nabla_\theta L$ and Hessian $H_{\theta\theta} L$ in a Newton's method optimizer  \cite{mogensen2018optim,RevelsLubinPapamarkou2016}.
+The use of AD allows this data-driven solver to extend to an arbitrary number of grid levels, avoiding inaccurate and potentially unstable finite differences.
 
-The data-driven solver and all test cases presented in the following sections are implemented in Julia and available for reproduction \cite{bezanson2017julia,weymouth2021julia}.
+The data-driven solver and all test cases presented in the following sections are implemented in the Julia programming language \cite{bezanson2017julia} and available for reproduction \cite{weymouth2021julia}.
 
@@
     \end{subfigure}
-    \caption{a) Residual reduction over a single Multi-grid V-cycle on the `test' cases after tuning using the `train' case.
+    \caption{a) Residual reduction factor $|r_{k+1}|/|r_k|$ over a single Multi-grid V-cycle on the `test' case after tuning using the `train' case.
 Training case `union' refers to the smoother trained on all of the synthetic cases.
@@
 
-A set of six synthetic projection cases were constructed to establish the characteristics of the parameterized smoother.
+A set of six synthetic projection cases were constructed to establish the characteristics of the data-driven approach.
 The three 2D cases are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
@@
 Figure~\ref{fig:cross plot} characterizes the generalization of the parameterized smoother's residual reduction over a single V-cycle on 100 randomized `test' case examples after optimization using 100 examples of the `train' case.
-Each example uses a grid size of $n=32^M$ points ($N=32^2$ in 2D and $N=32^3$ in 3D) as testing with other resolutions found essentially no change in the performance.
-Two inner loops are used throughout to optimize residual reduction.
-As expected, the performance is best when testing and training on the same case, with a single V-cycle reducing the residual from $10^{-1.17}$ on the 2D-sphere case down to $10^{-1.58}$ on the 3D-box case.
-While the performance for the simplest cases generalizes poorly, the 2D-sphere smoother generalizes essentially as well as the `union' smoother trained on all of the data.
+Each example uses a grid size of $N=32^M$ points ($N=32^2$ in 2D and $N=32^3$ in 3D) as testing with other resolutions found essentially no change in the performance.
+V-cycle residual reduction using a Jacobi-smoother is shown for comparison, as this is the fastest option and the initial condition for the data-driven method.
+As expected, the performance is best when testing and training on the same case, with a single V-cycle reducing the residual by $|r_{k+1}|/|r_k|=10^{-1.19}$ on the 2D-sphere case down to $10^{-1.68}$ on the 2D-dipole case.
+Note that despite identical $A$ matrices in the static and dipole cases, the data-driven method find completely different optimal $\tilde A^{-1}$ matrices, as shown by their different generalization performance.
+While the performance for the simple static cases generalizes poorly, the solver trained on the 2D-sphere generalizes essentially as well as the solver trained on the `union' of the all data.
+The `union' data-driven solver improves the performance between 105\% (2D-circle) and 2205\% (3D-static) compared to the Jacobi-smoothed V-cycle.
 
-Finally, the acceleration of the `union' data-driven smoother is evaluated on new example data of a different size, $n=64^M$ points.
-Figure~\ref{fig:synthetic time} shows the time to reduce the residual of each case by $10^{-3}$ relative to the time to run a single V-cycle using a Jacobi smoother.
-The Jacobi smoother is not sufficient to solve even these simple synthetic problems rapidly, requiring many hundreds o V-cycles.
-Yet, the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, and converges in only 1-3 V-cycles in all cases.
+The acceleration of the `union'-trained data-driven projection method is evaluated on new example data of a different size, $n=64^M$ points.
+Figure~\ref{fig:synthetic time} shows the time required to reduce the residual by $10^{-3}$.
+The time is scaled by the time required to run a single V-cycle using a Jacobi smoother but the Jacobi smoother isn't a viable option since it can require hundreds of V-cycles to solve even these simple projection problems.
+While the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, it converges in only 1-3 V-cycles in all cases.
 This results in a 80-210\% speed-up (mean: 133\%) relative to optimized serial Gauss-Sidel and SOR smoothers.
@@
         \includegraphics[width=\textwidth]{figures/donuttriple.png}
-        \caption{Torus flow (slice)}
+        \caption{Slice of 3D torus (donut) flow}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{figures/TGVtriple.png}
-        \caption{Taylor-Green Vortex (slice)}
+        \caption{Slice of 3D Taylor-Green Vortex}
     \end{subfigure}
@@
     \hfill
-    \caption{Snapshots from the five flow simulation cases showing the pressure solution (left), the initial residual (middle), and the residual after a single V-cycle (right).
+    \caption{Snapshots from the five flow simulation cases showing the pressure solution (left), the initial residual (middle), and the residual after a single V-cycle (right) using the data-driven projection method.
 The Taylor-Green Vortex and torus flow are 3D, the flapping wing is dynamic without a background flow and the swimming shark is a deforming geometry.
@@
 2D and 3D simulations with and without background flows, immersed geometries, body motion, and body deformation.
+The computational grids are of different sizes and aspect ratios, and the V-cycle is extended recursively down to the smallest possible grid in all cases.
 
@@
 
-The parameterized smoother from the synthetic cases of the previous section is effective at reducing the residual on the unseen simulation cases, Figure \ref{fig:scaled loss}.
-This `transfer' smoother achieves 85-95\% of the residual reduction of a smoother optimized for each case.
+Figure \ref{fig:scaled loss} shows that the new data-driven method trained on the synthetic cases of the previous section reduces the residual on these unseen simulation cases more effectively than a V-cycle using Jacobi smoothing.
+Indeed, this `transfer' smoother achieves 85-95\% of the residual reduction of a smoother optimized for each case.
 Even more promising is that training on reduced-size simulations closes that small gap almost completely.
@@
 
-The relative speed-up of this approach is compared to classic MG methods and the transfer smoother in Figure \ref{fig:simulation time}.
-As with the synthetic cases of the previous section, the data-driven methods are much faster, with the auto-tuned approach accelerating the projection step by 66-120\%.
+Figure \ref{fig:simulation time} shows that this data-driven method greatly acceleration the projection step relative to the classic MG methods on these real flow cases.
+The solver tuned on the reduced resolution cases provides 112 - 230\% acceleration, and even the transfer case provides a mean acceleration of 120\%.
+The pressure solutions, initial residual field, and the residual after a single data-driven V-cycle are shown in \ref{fig:simulation cases}.
+The residual decreases throughout the domain, including at the external and internal boundaries.
+As such, the new data-driven method is shown to produce uniformly valid solutions despite being trained to optimize the global residual loss.
 
@@
         \includegraphics[width=\textwidth]{figures/diag_fun.png}
-        \caption{diagonal functions}
+        \caption{diagonal functions $f_d$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{figures/lower_fun.png}
-        \caption{off-diagonal functions}
+        \caption{off-diagonal functions $f_o$}
     \end{subfigure}
-        \caption{(a) Diagonal and (b) off-diagonal parameterized functions after optimization on each simulation case.
+        \caption{(a) Diagonal and (b) off-diagonal parameterized functions after optimization on the 1/4-resolution case.
 The `transfer' smoother was tuned on the synthetic cases and `Jacobi' is shown for comparison.}
@@
 Mathematical constraints are used to further focus the learning capacity to a parameterized Jacobi-like Multi-grid smoother.
-This resulting data-driven MG solver is with 33\% of the minimum computational cost per V-cycle, and shown to outperform classic Gauss-Sidel and SOR smoothers by 66-185\% on eleven simulation cases.
-Because of the focused learning capacity, the generalization is excellent, enabling 90\% effective transfer learning from a synthetic data-set and essentially perfect transfer from reduced resolution simulations.
+The resulting data-driven solver is within 33\% of the minimum computational cost per V-cycle, and shown to accelerate classic Gauss-Sidel and SOR smoothers by 80-233\% on eleven simulation cases.
+Because of the focused learning capacity, the generalization is excellent, enabling 90\% effective transfer learning from a synthetic data-set and nearly 100\% transfer from reduced resolution simulations.
 

### 2021-10-21 tex/article.tex

@@
     \caption{a) Residual reduction factor $|r_{k+1}|/|r_k|$ over a single Multi-grid V-cycle on the `test' case after tuning using the `train' case.
-Training case `union' refers to the smoother trained on all of the synthetic cases.
+`Jacobi` is the V-cycle performance using a classic Jacobi smoother, and `union' refers to the solver trained on all of the synthetic cases.
 (b) Time to reduce pressure residual by $10^{-3}$ for classical and parameterized smoothers on each synthetic case.
@@
 Figure~\ref{fig:cross plot} characterizes the generalization of the parameterized smoother's residual reduction over a single V-cycle on 100 randomized `test' case examples after optimization using 100 examples of the `train' case.
-Each example uses a grid size of $N=32^M$ points ($N=32^2$ in 2D and $N=32^3$ in 3D) as testing with other resolutions found essentially no change in the performance.
-V-cycle residual reduction using a Jacobi-smoother is shown for comparison, as this is the fastest option and the initial condition for the data-driven method.
-As expected, the performance is best when testing and training on the same case, with a single V-cycle reducing the residual by $|r_{k+1}|/|r_k|=10^{-1.19}$ on the 2D-sphere case down to $10^{-1.68}$ on the 2D-dipole case.
-Note that despite identical $A$ matrices in the static and dipole cases, the data-driven method find completely different optimal $\tilde A^{-1}$ matrices, as shown by their different generalization performance.
-While the performance for the simple static cases generalizes poorly, the solver trained on the 2D-sphere generalizes essentially as well as the solver trained on the `union' of the all data.
-The `union' data-driven solver improves the performance between 105\% (2D-circle) and 2205\% (3D-static) compared to the Jacobi-smoothed V-cycle.
+Each example uses a grid size of $N=32^M$ points, ie $N=32^2$ in 2D and $N=32^3$ in 3D.
+The V-cycle residual reduction using a Jacobi-smoother is shown for comparison, as this is the fastest option and the initial condition for the data-driven method.
+The data driven-method vastly outperforms the Jacobi-smoothed V-cycle, improving the residual loss from 105\% on the 3D-dipole case to 2880\% on the 3D-static case.
+
+As expected, the performance of the data-driven projection method is best when testing and training on the same case, with a single V-cycle reducing the residual by $|r_{k+1}|/|r_k|=10^{-1.19}$ on the 2D-sphere case down to $10^{-1.68}$ on the 2D-dipole case.
+Note that despite identical $A$ matrices in the static and dipole cases, the data-driven method finds completely different optimal $\tilde A^{-1}$ matrices, as shown by their different generalization performance.
+While the performance of the solver trained on the simple static cases generalizes poorly, the others cases generalize well and the solver trained on the 2D-sphere performs nearly as well as the solver trained on the `union' of the all data.
 
@@
 
-Figure \ref{fig:scaled loss} shows that the new data-driven method trained on the synthetic cases of the previous section reduces the residual on these unseen simulation cases more effectively than a V-cycle using Jacobi smoothing.
-Indeed, this `transfer' smoother achieves 85-95\% of the residual reduction of a smoother optimized for each case.
+Figure \ref{fig:scaled loss} shows that when the data-driven method trained on the synthetic cases of the previous section is transferred to these unseen simulation cases, it reduces the residual 2.5 to 3.9 times more effectively than a V-cycle using Jacobi smoothing.
+Indeed, without any further training this transfer solver achieves 85-95\% of the residual reduction of a smoother optimized for each new case.
 Even more promising is that training on reduced-size simulations closes that small gap almost completely.
-Training on a $1/4^\text{th}$-scale simulation is fast, requiring only $N_{1/4} = N/4^M$ points (N/16 in 2D and N/64 in 3D) and $\approx 1/4$ the number of time steps, while achieving 99-100\% of the residual reduction of training with full-scale data.
-Such an \textit{auto-tuning} approach enables a highly effective data-driven projection method to be developed for any simulation approach with very little overhead.
+Training on a $1/4^\text{th}$-scale simulation is fast, requiring only $N/4^M$ points (N/16 in 2D and N/64 in 3D) and $\approx 1/4$ the number of time steps, while achieving 99-100\% of the residual reduction of training with full-scale data.
+Such an \textit{auto-tuning} approach enables a highly effective data-driven projection method to be developed for any flow simulation case with very little overhead.
 
-Figure \ref{fig:simulation time} shows that this data-driven method greatly acceleration the projection step relative to the classic MG methods on these real flow cases.
-The solver tuned on the reduced resolution cases provides 112 - 230\% acceleration, and even the transfer case provides a mean acceleration of 120\%.
+Figure \ref{fig:simulation time} shows that this data-driven method greatly accelerates the projection step relative to the classic MG methods on these real flow cases.
+The solver tuned on the reduced resolution cases provides 112 - 230\% acceleration, and even the transferred solver provides a mean acceleration of 120\%.
 The pressure solutions, initial residual field, and the residual after a single data-driven V-cycle are shown in \ref{fig:simulation cases}.
 The residual decreases throughout the domain, including at the external and internal boundaries.
-As such, the new data-driven method is shown to produce uniformly valid solutions despite being trained to optimize the global residual loss.
+As such, the new data-driven method is shown to produce uniformly valid solutions despite only being trained to optimize the global residual loss.
 
@@
         \caption{(a) Diagonal and (b) off-diagonal parameterized functions after optimization on the 1/4-resolution case.
-The `transfer' smoother was tuned on the synthetic cases and `Jacobi' is shown for comparison.}
+The `transfer' smoother was tuned on the synthetic cases and the Jacobi smoother values are shown for comparison.}
         \label{fig:tuned inverse}

### 2021-10-24 src/candidate_smoothers.jl
forgot to push last commit

@@ -25,6 +25,28 @@ end
     increment!(st;kw...)
 end
 
+# Create parameterized MG state
+function state(A,x,b;p=p₀,xT::Type=eltype(p),smooth! =GS!,damp=false,kw...)
+    y = zero(x,xT)     # make FieldVector of type xT
+    @loop y[I] = x[I]  # copy values
+    err = sum(b)/length(b)
+    @loop b[I] -= err
+    st = mg_state(A,y,b)
+    smooth! == pseudo! && fill_pseudo!(st;p,kw...)
+    damp && adjust_iD!(st;p)
+    st
+end
+state(A,b;kw...) = state(A,zero(b),b;kw...)
+fill_pseudo!(st;kw...) = !isnothing(st.child) && (st.P=PseudoInv(st.A;kw...); fill_pseudo!(st.child;kw...))
+adjust_iD!(st;p) = !isnothing(st.child) && (@loop st.iD[I] *= p[end]; adjust_iD!(st.child;p))
+
+# Apply smoother
+@inline pseudo!(st;kw...) = pseudo!(st,st.P;kw...)
+@fastmath pseudo!(st,P::FieldMatrix;inner=2,kw...) = for _=1:inner
+    @loop st.ϵ[I] = mult(I,P.L,P.D,st.r)
+    increment!(st)
+end
+
 # Parameterized approximate inverse matrix P
 p₀ = Float32[-0.104447, -0.00238399, 0.00841367, -0.158046, -0.115103] # result from tune_synthetic
 function PseudoInv(A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
@@ -44,103 +66,3 @@ function PseudoInv(A::FieldMatrix; scale=maximum(A.L),p::AbstractVector{T}=p₀,
     FieldMatrix(L,D,A.R)
 end
 
-# Create MG state with st.P
-function state(A,x,b;p=p₀,xT::Type=eltype(p),smooth! =GS!,kw...)
-    y = zero(x,xT)     # make FieldVector of type xT
-    @loop y[I] = x[I]  # copy values
-    err = sum(b)/length(b)
-    @loop b[I] -= err
-    st = mg_state(A,y,b)
-    smooth! == pseudo! && fill_pseudo!(st;p,kw...)
-    st
-end
-state(A,b;kw...) = state(A,zero(b),b;kw...)
[…]

### 2021-10-24 test_waterlily.jl

@@ -50,16 +50,19 @@ savefig("scaleloss.png")
 begin
     scaledata = create_waterlily(p=4)
     scaledata[wing] = filter(d->itcount(d,GS!)<32,scaledata[wing])
-    opt2 = OrderedDict(name=>fit(train;it=2) for (name,train) ∈ scaledata)
+    opt2 = OrderedDict(name=>fit(train,p₀;it=2) for (name,train) ∈ scaledata)
 end
+
 begin
     opt2 = OrderedDict(
-        circle => [0.143874, 0.114321, 0.024359, -0.166979, -0.211477],
-        TGV    => [-0.445326, -0.175383, -0.0100868, -0.147759, 0.0],
-        donut  => [0.120699, 0.0239083, 0.00775287, -0.149375, -0.0753296],
-        wing   => [0.0259308, -0.123091, -0.0268147, -0.174569, -0.542901],
-        shark  => [0.0673034, -0.104414, -0.0241938, -0.182964, -0.298915]
+        circle => [0.143873, 0.114321, 0.0243589, -0.166979, -0.211476],
+        TGV    => [-0.445295, -0.175371, -0.0100856, -0.147759, 0.0],
+        donut  => [0.121331, 0.0259214, 0.00808, -0.149346, -0.0750463],
+        wing   => [0.0259344, -0.123088, -0.0268142, -0.174569, -0.542905],
+        shark  => [0.0673015, -0.104415, -0.024194, -0.182964, -0.298915]
     )
+    # c = [avecount(test,pseudo!;p=opt2[name]) for (name,test) ∈ data]
+    c = [2.0 2.11 2.99 5.99 6.9]
 end
 
 # time a single Vcycle
@@ -72,7 +75,6 @@ begin
     gauss_time /= jacobi_time
     sor_time /= jacobi_time
     pseudo_time /= jacobi_time
-    # gauss_time = 3.5; sor_time = 3.2; pseudo_time = 1.37
 end
 
 # Count the number of cycles needed

### 2022-04-05 tex/article.tex

@@
 \usepackage{amsmath}
+\usepackage{xcolor}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title{Data-Driven Multi-grid Solver for Accelerated \\ Pressure Projection}
+\title{Data-Driven Multi-Grid Solver for Accelerated \\ Pressure Projection}
 
@@
 Pressure projection is the single most computationally expensive step in an unsteady incompressible fluid simulation.
-This work discusses the potential of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection, linking Multi-grid methods to linear convolutional encoder-decoder networks.
-A high-speed Jacobi-like parameterized smoother is developed and optimized using automatic differentiation on the recursive log-residual loss function.
-The new method is found to accelerate classic Multi-grid methods by a factor of 2-3 with no loss of accuracy on eleven 2D and 3D flow cases including cases with dynamic immersed solid boundaries.
-The optimal parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of general flows.
+\textcolor{blue}{This work demonstrates the ability of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection.} Geometric Multi-Grid methods are identified as linear convolutional encoder-decoder networks and a data-driven smoother is developed using automatic differentiation to optimize the velocity-divergence projection.
+The new method is found to accelerate classic Multi-Grid methods by a factor of two to three with no loss of accuracy on eleven 2D and 3D flow cases including cases with dynamic immersed solid boundaries.
+The optimal parameters are found to transfer nearly 100\% effectiveness as the resolution is increased, providing a robust approach for accelerated pressure projection of unsteady flows.
 \end{abstract}
@@
 Pressure projection is a bottleneck in high-speed unsteady incompressible flow solvers.
-Constructing approximate solutions the discrete pressure Poisson system is the most expensive part of each time-step as the elliptic equation requires communication throughout the computational domain instead of being confined to a local characteristic.
+Constructing approximate solutions for the discrete pressure Poisson system is the most expensive part of each time-step as the elliptic equation requires communication throughout the computational domain instead of being confined to a local characteristic.
 As such, the proportional cost only grows in massively parallel simulations due to the required communication across processes.
@@
 Many of these approaches utilize Convolutional Neural Networks (CNN), Figure \ref{fig:multigrid}, which have been successfully applied in other fluids applications such as super-resolution \cite{liu2020deep} and full field regression models \cite{bhatnagar2019prediction}.
-CNNs have inherent translational symmetry and encoder-decoder architectures reduce the number of variables before expanding again, both of which help constrain learning capacity and generalize the trained networks to unseen prediction cases.
+The CNN's inherent translation symmetry and the encoder-decoder architecture's reduction and expansion of the array size both help constrain model learning capacity and generalize the trained networks to unseen prediction cases.
 
@@
 All of these method assume a uniform grid without internal solid geometries, although \cite{ozbay2021poisson} uses a decomposition to handle different \textit{domain} boundary conditions and grid aspect ratios in 2D.
-Unfortunately, the methods can't be applied to most simulation problems and the results are still somewhat qualitative, with pressure errors greater than 10\% throughout much of the domain \cite{ozbay2021poisson}.
+Unfortunately, the methods can't be applied to most simulation problems and even state-of-the-art results are still qualitative, with errors greater than 10\% throughout much of the domain \cite{ozbay2021poisson}.
 
-A key insight is that classic Geometric Multi-Grid (GMG) methods \cite{briggs2000multigrid} are simply \textit{linear} convolutional encoder-decoder networks, Figure \ref{fig:multigrid}, prime for data-driven acceleration without any loss of accuracy in the resulting pressure field.
-While there is a long history of optimizing multi-grid methods (both geometric \cite{oosterlee2003genetic} and algebraic \cite{brezina2006adaptive}), few of these have taken a direct data-driven approach.
-Recent work \cite{KATRUTSA2020112524,greenfeld2019learning} has shown promising initial results in constructing data-driven restriction and prolongation operators, but both use idealized systems and do not show overall speed-up compared to classic methods, so their utility in accelerating real pressure projection problems is untested.
+A key insight to accelerating pressure projection is that classic Geometric Multi-Grid (GMG) methods \cite{briggs2000multigrid} are simply \textit{linear} convolutional encoder-decoder networks, Figure \ref{fig:multigrid}.
+While there is a long history of optimizing multi-grid methods (both geometric \cite{tang2000sparse} and algebraic \cite{brezina2006adaptive}), few of these have taken a direct data-driven approach.
+\textcolor{blue}{\cite{tang2000sparse} construct a sparse approximate smoother by solving a series of least-square matrix equations instead of a data-driven approach.
+This improved the convergence properties on extremely skewed grids compared to Gauss-Sidel smoothers, but not on more regular grids or when using a very sparse (and therefore fast) approximate inverse.}
 
-Building on this foundation, this work develops a simple and accurate data-driven projection method which outperforms classic geometric multi-grid on eleven 2D and 3D benchmarks including those with immersed solid boundaries.
-Moreover, since the new approach is linear in the pressure and the nonlinear dependence on the matrix coefficients are scale-invariant, the data-optimized parameters generalize extremely well to new flows and simulation resolutions.
+Employing modern data-driven techniques could  further accelerate GMG without the loss of accuracy currently limiting CNN methods.
+Recent work has shown promising initial results in constructing data-driven restriction and prolongation operators \cite{KATRUTSA2020112524,greenfeld2019learning}.
+\textcolor{blue}{However, improving the architecture of these operators is a very challenging discrete optimization problem, limiting the results achieved thus far.
+Both \cite{KATRUTSA2020112524,greenfeld2019learning} show improved convergence spectra compared to classic GMG methods, but no overall speed-up.
+}
+
+\textcolor{blue}{Building on this foundation, this manuscript develops a novel data-driven smoother which is optimize using automatic differentiation to minimize the velocity-divergence over the full recursive GMG V-cycle.
+This new framework achieves 2 to 3-fold acceleration compared to standard GMG on eleven 2D and 3D benchmark projection problems including those derived from unsteady Navier-Stokes simulations with dynamic immersed boundaries.} Moreover, since the new approach maintains linearity in the pressure and the nonlinear dependence on the matrix coefficients are scale-invariant, the data-optimized parameters generalize extremely well to new flows and simulation resolutions.
 
@@
 \end{equation}
-where $x$ is the desired pressure field vector, $b$ is the source term (proportional to the divergence of the velocity field to be projected), and $A$ is the Poisson matrix.
-For conservative Poisson equations, $A$ is symmetric, has zero-sum rows and columns, is negative semi-definite, and has a single zero eigenvalue.
+where $x$ is the unknown pressure field vector, $b$ is the source term proportional to the divergence of the velocity field to be projected, and $A$ is the discrete matrix for the Poisson operator.
+For a conservative Poisson operator, $A$ is symmetric, has zero-sum rows and columns, is negative semi-definite, and has a single zero eigenvalue.
 The matrix is also extremely sparse.
@@
 \end{equation}
-where $r$ is the residual. In practise, only an approximate solution for $\epsilon$ is obtained, after which the solution and residual are incremented
+where $r$ is the residual.
+\textcolor{blue}{In the context of the pressure Poisson equation, the residual is the remaining divergence in the velocity field.
+Driving this residual to zero by updating the pressure is the goal of the projection step.}
+
+In practise, only an approximate solution for $\epsilon$ is obtained, after which the solution and residual are incremented
 \begin{equation}\label{eq:increment}
@@
 \end{equation}
-This process is iterated until the residual is reduced to a specified level.
+\textcolor{blue}{This process is iterated until the velocity-divergence residual is reduced to a specified tolerance, at which point the projection step is complete.}
 
@@
 A single iteration of GMG is called a V-cycle and consists of (i) a solution precondition step, (ii) residual restriction down to the reduced-size problem, (iii) approximate solution of this problem, (iv) solution prolongation back up to correct the fine grid, and (v) solution smoothing.
-This process is recursive, being applied to the reduced-size problems until they are small enough to be solved directly, resulting in $O(N\log N)$ computational cost overall.
-% \begin{equation}
-%     r_c = R r \quad\rightarrow\quad A_c \epsilon_c = r_c \quad\rightarrow\quad \epsilon = P \epsilon_c
-% \end{equation}
-% where $R$ is the $N_c \times N$ restriction operator, $P$ is the $N \times N_c$ prolongation operator 
+This process is recursive, being applied to the reduced-size problems until they are small enough to be solved directly, resulting in $O(N)$ operations per V-cycle.
 The first four steps of the V-cycle distribute the residual throughout the domain, which enables simple and relatively fast stationary methods such as Gauss-Sidel or Successive Over Relation (SOR) to effectively smooth the local error in the projected solution.
@@
 
-As \textit{any} element of the residual of the elliptic Poisson system potentially influences \textit{every} element of the update, $O(N\log N)$ is the best possible solution time scaling.
-However, data-driven methods can still be used to accelerate pressure projection by speeding-up and increasing the residual reduction of each V-cycle iteration.
+As the Poisson equation is elliptic, \textit{any} element of the velocity-divergence residual $r$ potentially influences \textit{every} element of the update $\epsilon$.
+Therefore the linear $O(N)$ scaling achieved by GMG is already optimal.
+However, data-driven methods can still be used to accelerate GMG projection by speeding-up and increasing the residual reduction of each V-cycle iteration.
 
-The linearity of equation \ref{eq:aer} is a critical property which the data-driven method must maintain.
-Consider that the modes of the residual will change as the solver converges, meaning that a nonlinear method could not be applied iteratively.
+The linearity of equation \ref{eq:aer} is a critical property which the data-driven projection method must maintain.
+Without it, the projection method can not be applied iteratively to drive the velocity-divergence to the required tolerance of the flow solver.
 However, this linearity is only with respect to the update and residual fields.
-The operators of the MG method can all potentially be (implicit or explicit) nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
+The GMG operators can potentially be explicit nonlinear functions of $A$, embedding information about the discrete problem and boundary conditions.
 
-Which MG operation is the best candidate for such an approach?
-As discussed in the introduction, significant effort has focused on optimization of the prolongation operator and its transpose restriction operator.
-The prolongation operator is an \textit{implicit} function of $A$, making their construction difficult in algebraic settings and their optimization mathematically and numerically complex even in geometric settings \cite{KATRUTSA2020112524,greenfeld2019learning}.
-Note that super-resolution operators are related to prolongation, but would violate the linearity constraint.
+Which GMG operation is the best candidate for such an approach?
+Significant effort has focused on the optimization of the prolongation operator and its transpose restriction operator.
+However, prolongation/restriction operators are not explicit functions of $A$, making their optimization mathematically and numerically complex \cite{KATRUTSA2020112524,greenfeld2019learning}.
+And while CNN encoding/decoding are simple to optimize with back-propagation, their nonlinear activation functions make them invalid in this application.
 
@@
 where $D$ is the diagonal of $A$, is sufficient for the V-cycle to distribute the residual throughout the domain and is as fast as possible; being a single Schur (broadcasted) vector product.
-Therefore, for the remainder of the paper we will use a simple Jacobi preconditioner and uniform pooling/distribution for restriction/prolongation and focus on a parameterized smoothing operator.
+Therefore, for the remainder of the paper we will use a simple Jacobi preconditioner and uniform pooling/distribution for restriction/prolongation and focus on a data-driven smoothing operator.
 
-While more complex options are certainly possible, this work uses a simple parameterized Jacobi-like smoother
+While more complex options are certainly possible, this work considers a sparse approximate inverse as a smoother
 \begin{equation}\label{eq:smooth}
@@
 \end{equation}
-where $\tilde A^{-1}=f(A\,|\theta)$ is an approximate matrix-inverse with the same sparsity as $A$ and parameter vector $\theta$.
-The matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be computed and stored ahead of time.
-And unlike Gauss-Sidel or SOR smoothers, the matrix-vector multiplication of equation \ref{eq:smooth} requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
+where $\tilde A^{-1}=f(A\,|\theta)$ is a parameterized pseudo-inverse with the same sparsity as $A$ and $\theta$ is the parameter vector.
+The advantage of this pseudo-inverse smoother is speed.
+Unlike Gauss-Sidel or SOR smoothers, the sparse matrix-vector multiplication of equation \ref{eq:smooth} requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
+Additionally, the matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be stored ahead of time, avoiding on the fly function evaluations.
 
-There are few constraints on $\tilde A^{-1}$: it must have units of $A^{-1}$, and symmetry of $A$ implies the approximate inverse should also be symmetric.
+There are few constraints on $\tilde A^{-1}$: it must scale with $A^{-1}$, and symmetry of $A$ implies the pseudo-inverse should also be symmetric.
 For simplicity, the diagonal and off-diagonal coefficients of $\tilde A^{-1}$ are constructed independently
@@
 
-The parameterized smoother is optimized for a set of training data $X=\{A,x^k,b\}$.
-The loss function is simply the reduction in the norm of the residual after a V-cycle iteration $L = \log_{10}(|r^{k+1}| / |r^{k}|)$, which means that example pressure \textit{solutions} are not required.
+The parameterized smoother is optimized for a set of training data $X=\{A,r^0\}$. The loss is defined as the reduction in the log-$L_2$-norm of the residual after each V-cycle iteration 
+$$L = \log_{10}(|r^{k+1}|_2 / |r^{k}|_2)$$
 This loss is averaged over each iteration and each example in the data-set.
-The optimal parameters are defined as
+\textcolor{blue}{Working directly with a residual loss has a number of advantages.
+First and foremost, the purpose of the pressure projection step is to drive the velocity-divergence residual to zero, making this the ultimate judge of any projection method.
+Second, this incorporates problem-specific residual data which would be missing from a metric based only on the V-cycle operator.
+Finally, the residual is always available, unlike the error with respect to the unknown exact pressure solution.}
+
+The optimal parameters of the accelerated GMG projection method are then given by the minimization
 \begin{equation}
@@
     \end{subfigure}
-    \caption{Sample solutions from the data-sets of three of the six synthetic cases.}
+    \caption{Sample solutions (left) from the data-sets of three of the six synthetic cases.
+\textcolor{blue}{Also shown are the solution errors (middle) and residuals (right) using the data-driven solvers using after reducing the residual norm by $10^{-3}$.}}
     \label{fig:synthetic cases}
 \end{figure}
+
+\section{Synthetic Discrete Poisson System Results}
+
+\textcolor{blue}{A set of six synthetic cases were developed to establish the ability of the data-driven approach to project out residuals located at domain boundaries, body boundaries, or within the fluid.
+The three 2D cases are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
+The `static' cases feature a randomized pressure gradient throughout the domain produced by residuals on the domain boundaries.
+The `dipole' and `sphere' cases feature residuals on a random dipole or on the boundary of a random immersed sphere within an otherwise quiescent flow.
+Neumann conditions are applied on the domain and sphere boundaries using the Boundary Data Immersion Method (BDIM) to adjust the $A$ matrix coefficients, as described and validated in \cite{maertens2015accurate,Lauber2022}.
+The  generative equations for each synthetic case are given in \ref{app synth}.}
+
+%All cases are initialized with $x^0=0$ and all cases feature initially localized residuals; i.e.
+$r^0\ne0$ only in a fraction of the cells, but $x$ must be updated throughout the domain, starkly illustrating the elliptic nature of the projection step.
+A data-driven GMG solver is optimized for each synthetic case using 100 randomized training examples.
+\textcolor{blue}{Figure~\ref{fig:synthetic cases} shows the velocity residual distribution produced by the trained solvers using a tolerance of $|r^k|_2/|r^0|_2<10^{-3}$, as well as the error in the pressure compared to a result obtained using a classic GMG method converged to machine precision.
+The results show that the initially highly-localized residual is project and distributed throughout the domain, without build-up on the domain or immersed boundaries.}
+
 \begin{figure}
@@
 (b) Time to reduce pressure residual by $10^{-3}$ for classical and parameterized smoothers on each synthetic case.
-Time is relative to the time of a single V-cycle using the Jacobi smoother.}
+Time is relative to a single Jacobi-smoothed V-cycle on each grid.}
     \label{fig:synthetic results}
@@
 
-\section{Synthetic Discrete Poisson System Results}
+Figure~\ref{fig:cross plot} quantifies the generalization performance of each trained projection method on 100 unseen test examples for each case.
+\textcolor{blue}{The results for a Jacobi-smoothed GMG V-cycle are shown for comparison as this is the initial condition for the \textit{untrained} data-driven method.} After training, the data-driven method vastly outperform the Jacobi V-cycle, doubling the residual loss on the 3D-dipole case and providing nearly 30-fold improvement on the 3D-static case.
+While the performance of the data-driven projection method is best when testing and training on the same case, most of the solvers still improve on the Jacobi-smoothed GMG performance for cases outside of their training set.
+Indeed, the solver trained on the 2D-sphere generalizes essentially as well as a solver trained on the `union' of the all training case data.
+The exceptions are the static cases, with the solver trained on the 2D-static case failing to converge on three of the other test cases.
+Note that despite identical $A$ matrices in the static and dipole cases, the performance of the those solvers are completely different.
+This indicates that the data-driven methods are specializing based on the residual data as well as the matrix structure, a feature unique to this approach.
 
-A set of six synthetic projection cases were constructed to establish the characteristics of the data-driven approach.
-The three 2D cases are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
-The `static' cases have a hydrostatic gradient throughout the domain, with the direction and magnitude randomized.
-The `dipole' and `sphere' cases have a randomized dipole/sphere within a quiescent flow.
-All cases are initialized with $x^0=0$.
-%, and all cases feature initially localized residuals; i.e.
-$r^0\ne0$ only in a fraction of the cells, but $x$ must be updated throughout the domain, starkly illustrating the elliptic nature of the projection step.
-Neumann boundary conditions are applied on all boundaries, including the boundary of the immersed sphere, through adjustment of the $A$ matrix coefficients which are otherwise uniform.
+\textcolor{blue}{Next, the acceleration of the data-driven projection method is evaluated against high-performance GMG solvers using classic stationary smoothers; Gauss-Sidel and SOR.} The `union'-trained data-driven solver is chosen and 100 tests are generated for each case on different grids to test the ability of the data-driven method to generalize to new grid sizes.
 
-Figure~\ref{fig:cross plot} characterizes the generalization of the parameterized smoother's residual reduction over a single V-cycle on 100 randomized `test' case examples after optimization using 100 examples of the `train' case.
-Each example uses a grid size of $N=32^M$ points, ie $N=32^2$ in 2D and $N=32^3$ in 3D.
-The V-cycle residual reduction using a Jacobi-smoother is shown for comparison, as this is the fastest option and the initial condition for the data-driven method.
-The data driven-method vastly outperforms the Jacobi-smoothed V-cycle, improving the residual loss from 105\% on the 3D-dipole case to 2880\% on the 3D-static case.
-
-As expected, the performance of the data-driven projection method is best when testing and training on the same case, with a single V-cycle reducing the residual by $|r_{k+1}|/|r_k|=10^{-1.19}$ on the 2D-sphere case down to $10^{-1.68}$ on the 2D-dipole case.
-Note that despite identical $A$ matrices in the static and dipole cases, the data-driven method finds completely different optimal $\tilde A^{-1}$ matrices, as shown by their different generalization performance.
-While the performance of the solver trained on the simple static cases generalizes poorly, the others cases generalize well and the solver trained on the 2D-sphere performs nearly as well as the solver trained on the `union' of the all data.
-
-The acceleration of the `union'-trained data-driven projection method is evaluated on new example data of a different size, $n=64^M$ points.
-Figure~\ref{fig:synthetic time} shows the time required to reduce the residual by $10^{-3}$.
-The time is scaled by the time required to run a single V-cycle using a Jacobi smoother but the Jacobi smoother isn't a viable option since it can require hundreds of V-cycles to solve even these simple projection problems.
-While the Jacobi-like parameterized smoother is only around 30-50\% slower per V-cycle, it converges in only 1-3 V-cycles in all cases.
-This results in a 80-210\% speed-up (mean: 133\%) relative to optimized serial Gauss-Sidel and SOR smoothers.
-This speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any additional communication.
+The results in Figure~\ref{fig:synthetic time} show that the data-driven method has no issue projecting the velocity divergence on unseen grid sizes, reducing the residual by $10^{-3}$ in only 2-5x the time of a single Jacobi-smoothed V-cycle.
+\textcolor{blue}{This is chosen as our unit of time since Jacobi-smoothing requires the smallest possible number of operations per V-cycle on a given grid.} As the pseudo-inverse smoother is many times faster than the Gauss-Sidel and SOR smoothers, this results in an overall 80-210\% speed-up (mean: 133\%) relative to classic GMG solvers.
+Note that this speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any additional communication.
 
@@
 
-\section{Unsteady Incompressible Simulation Results}
+\section{Unsteady Incompressible Simulation Projection Results}
 
 Five unsteady incompressible simulation cases were used to further characterize the accelerated projection method, Figure \ref{fig:simulation cases}.
-All simulations use the same validated Cartesian-grid method \cite{maertens2015accurate} but feature significantly different physics, i.e.
-2D and 3D simulations with and without background flows, immersed geometries, body motion, and body deformation.
-The computational grids are of different sizes and aspect ratios, and the V-cycle is extended recursively down to the smallest possible grid in all cases.
+\textcolor{blue}{The first three cases are variations on standard unsteady flow benchmarks, while the second two are variations of recent validated biologically-inspired flows \cite{Lauber2022}.} The simulations feature significantly different physics to test the accelerated projection performance from flows with and without background velocities, immersed geometries, body motion, and body deformation, as well as using computational grids of different sizes and aspect ratios.
+\textcolor{blue}{All simulations use the same extensively validated unsteady incompressible Navier-Stokes BDIM solver \cite{maertens2015accurate,Lauber2022} and 100 Poisson matrices $A$ and initial residuals $r^0$ are copied from each unsteady simulation to form the training and testing data.
+The details of each case are found in \ref{app flow}.}
+
+Figure \ref{fig:simulation cases} shows the pressure solutions, initial residual field, and the residual after a single V-cycle of the data-driven GMG method trained on each case.
+The results show that the residual decreases throughout the domain, including at the domain and immersed boundaries.
+\textcolor{blue}{This is further verified by Fig~\ref{fig:simulation forces}, which compares the unsteady pressure force on the circle flow (case a) and the swimming shark (case b) using both the data-driven and Gauss-Sidel smoothed GMG solvers.
+In both cases, the data-driven method matches the Gauss-Sidel forces for the same residual tolerance.} As such, the new data-driven method is shown to produce uniformly valid solutions despite only being trained to optimize the global residual loss.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \caption{Cylinder pressure}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.47\textwidth}
+        \centering
+        \caption{Swimming shark}
+    \end{subfigure}
+    \caption{Integrated pressure forces on the (a) cylinder and (b) swimming shark test cases using the data-driven and Gauss-Sidel GMG solvers for different residual tolerance levels.
+The $|r^k/r^0|<10^{-3}$ level is indistinguishable from that obtained driving the residuals to machine zero.}
+    \label{fig:simulation forces}
+\end{figure}
+
+Figure \ref{fig:scaled loss} shows that when the data-driven method trained on the synthetic cases of the previous section is transferred to these unseen simulation cases, it reduces the residual 2.5 to 3.9 times more effectively than an untrained Jacobi-smoothed V-cycle.
+Indeed, without any further training this transfer solver achieves 85-95\% of the residual reduction of a smoother optimized for each new case.
+Even more promising is that training on reduced-size simulations closes that small gap almost completely.
+Training on a $1/4^\text{th}$-scale simulation is fast, requiring only $N/4^M$ points (N/16 in 2D and N/64 in 3D) and $\approx 1/4$ the number of time steps, while achieving 99-100\% of the residual reduction of training with full-scale data.
+Such an \textit{auto-tuning} approach enables a highly effective data-driven projection method to be developed for any flow simulation case with very little overhead.
+Figure \ref{fig:simulation time} shows that this data-driven method greatly accelerates the projection step relative to the classic MG methods on these real flow cases.
+The solver tuned on the reduced resolution cases provides 112 - 230\% acceleration, and even the transferred solver provides a mean acceleration of 120\%.
 
@@
 \end{figure}
-
-Figure \ref{fig:scaled loss} shows that when the data-driven method trained on the synthetic cases of the previous section is transferred to these unseen simulation cases, it reduces the residual 2.5 to 3.9 times more effectively than a V-cycle using Jacobi smoothing.
-Indeed, without any further training this transfer solver achieves 85-95\% of the residual reduction of a smoother optimized for each new case.
-Even more promising is that training on reduced-size simulations closes that small gap almost completely.
-Training on a $1/4^\text{th}$-scale simulation is fast, requiring only $N/4^M$ points (N/16 in 2D and N/64 in 3D) and $\approx 1/4$ the number of time steps, while achieving 99-100\% of the residual reduction of training with full-scale data.
-Such an \textit{auto-tuning} approach enables a highly effective data-driven projection method to be developed for any flow simulation case with very little overhead.
-
-Figure \ref{fig:simulation time} shows that this data-driven method greatly accelerates the projection step relative to the classic MG methods on these real flow cases.
-The solver tuned on the reduced resolution cases provides 112 - 230\% acceleration, and even the transferred solver provides a mean acceleration of 120\%.
-The pressure solutions, initial residual field, and the residual after a single data-driven V-cycle are shown in \ref{fig:simulation cases}.
-The residual decreases throughout the domain, including at the external and internal boundaries.
-As such, the new data-driven method is shown to produce uniformly valid solutions despite only being trained to optimize the global residual loss.
-
 \begin{figure}
@@
 This manuscript develops a successful data-driven method to accelerate the solution of discrete pressure Poisson systems found in incompressible flow simulations.
-Multi-grid methods are identified as linear convolutional encoder-decoder networks with optimal ($N\log N$) scaling, and the matrix coefficients are identified as the critical nonlinear input, not the projection source-term, embedding information such as boundary conditions.
+Geometric Multi-Grid (GMG) methods are identified as linear convolutional encoder-decoder networks with optimal $O(N)$ scaling, and the matrix coefficients are identified as a critical nonlinear input, not only the projection source-term, as they embed information such as boundary conditions.
 Mathematical constraints are used to further focus the learning capacity to a parameterized Jacobi-like Multi-grid smoother.
-The resulting data-driven solver is within 33\% of the minimum computational cost per V-cycle, and shown to accelerate classic Gauss-Sidel and SOR smoothers by 80-233\% on eleven simulation cases.
+The resulting data-driven solver is within 33\% of the minimum computational cost per V-cycle, and shown to accelerate classic Gauss-Sidel and SOR smoothed GMG solvers by 80-233\% on eleven simulation cases.
 Because of the focused learning capacity, the generalization is excellent, enabling 90\% effective transfer learning from a synthetic data-set and nearly 100\% transfer from reduced resolution simulations.
@@
 Wherever possible, this work has made the simplest choice in parameterization, leaving significant opportunities for future improvements.
-Many other flow solvers and linear systems are yet to be explored, and extensions to this basic data-driven approach could accelerate solutions for a wide array of discrete partial differential equations.
+\textcolor{blue}{The flow cases in this manuscript use Cartesian-grids, but this does not limit the generality of the projection problems as the resulting $A$ matrices are nonuniform due to the presence of the immersed geometries.
+The current data-driven GMG framework can therefore be readily extended to the nonuniform matrices induced by stretched structured grids.
+Extensions to unstructured grids would require the use of algebraic instead of geometric multi-grid, and a similar data-driven sparse smoother could accelerate such projection methods.}
 
 \bibliography{mybibfile}
+\color{blue}
+\appendix
+\section{Synthetic case details}\label{app synth}
+
+The synthetic cases are all generated with simple functions on uniform 2D or 3D grid using $n$ grid cells in each direction.
+$n=32$ cells were used for the training data and the testing data in Fig~\ref{fig:cross plot}.
+$n=64,96$ and $128$ were used for the testing data in Fig~\ref{fig:synthetic time}.
+
+The 2D and 3D static cases are generated from a constant gradient solution
+$$ x_i = \hat m \cdot \vec q_i$$
+where $\vec q_i$ is the vector to the center of grid-cell $i$ and $\hat m$ is a random unit vector.
+The matrix $A$ is defined by $a_{ij}=1$ on cell faces, $a_{ij}=0$ on domain faces, and $a_{ii}=-\sum_j a_{ij}$.
+The initial residual is then $r^0=A x$ which is nonzero only on the domain boundaries.
+
+The 2D and 3D dipole cases are generated using a localized residual function
+$$ r_i = \hat m \cdot \left(\vec q_i-\vec Q\right)\ e^{-\sigma^2 |\vec q_i-\vec Q|^2} $$
+where $\vec Q$ is a random location in the fluid domain and $\sigma$ is a random width. The same uniform $A$ matrix is used as in the static case.
+
+The 2D and 3D sphere cases are generated using the residual from an immersed sphere with random center $\vec Q$ and radius $s$, moving in a random direction $\hat m$ in an initially still fluid.
+Following the Boundary Data Immersion Method \cite{maertens2015accurate,Lauber2022} the conservative  pressure equation is then
+$$ \oint_{\partial\Omega_i} \frac{\partial \phi}{\partial n}\beta \,\text{d}s = \oint_{\partial\Omega_i} m_n \,(1-\beta)  \,\text{d}s $$
+where $\partial\Omega_i$ are the faces of grid cell $i$, $\hat n$ is the face normal, $\phi$ is the scaled pressure, and $\beta$ is a coefficient which smoothly transitions from 1 to 0 as a function of the signed distance $d$ from the grid cell face to the immersed boundary.
+For example, a sphere has signed distance $d=|\vec q-\vec Q|-s$, and we could use $\beta=\min(1,\max(0,d+\frac 1 2))$.
+
+This equation is applied on each unit cell using second order central-finite difference and cell-center quadrature. For example, in 1D this gives
+\begin{gather*}
+a_{i,i-1}=\beta^w_i,\ a_{i,i+1}=\beta^e_i ,\ a_{ii}=-(\beta^w_i+\beta^e_i),\ a_{ij}=0\ \text{else}\\
+r_i =  -m\left(\beta^e_i-\beta^w_i\right)
+\end{gather*}
+where $\beta^{w,e}_i$ are the values on the west and east faces of cell $i$. The residual is non-zero only in the immersed boundary transition region where $\beta^e\ne\beta^w$.
+
+\section{Unsteady simulation case details}\label{app flow}
+
+The details for the five unsteady flow cases shown in Figure~\ref{fig:simulation cases} are:
+\begin{enumerate}[(a)]
+    \item 2D flow past a static circular cylinder: Radius $r=32$ grid cells, domain size $16r$ by $8r$ cells, cylinder center $(4r,4r)$, and Reynolds number $\text{Re}=Ur/\nu=250$.
+    \item 3D flow past a static donut: Major radius $R=32$ cells, minor radius $r=R/4$, domain size $8R$ by $4R$ by $4R$, center $(2R,2R,2R)$, and $\text{Re} = RU/\nu=10^3$.
+    \item 3D Taylor-Green Vortex turbulent decay: initial velocity function $u=-\sin(kx)\cos(ky)\cos(kz)$, $v=\cos(kx)\cos(ky)\cos(kz)$, $w=0$ with $k=\pi/n$, domain size $n=128$ cubed, and $\text{Re}=10^5$.
+    \item 2D flow induced by a flapping plate wing: Length $L=64$ cells, initial position $(3L,4L)$, horizontal displacement $x=L\sin(\omega t)$, rotation angle $\alpha=\frac\pi 4\cos(\omega t)$, domain size $6L$ by $6L$ cells, and $\text{Re}=\omega L^2/\nu=250$.
+    \item 2D flow past the undulating cross-section of a swimming shark: Body length $L=128$ cells, domain size $4L$ by $2L$, undulation wavenumber $k=5.3/L$, tail peak-to-peak amplitude $A=0.2L$, Strouhal number $\text{St}=fA/U=0.3$, and $\text{Re}=UL/\nu=10^4$.
+\end{enumerate}
+Reduced resolution training data used for Figure~\ref{fig:tuned simulation} uses the same setup as above, except the resolution is decreased.
+For example, a $\frac 14$-resolution wing simulation uses $L=16$ cells which reduces the amplitude of motion and domain size proportionally.
 

### 2022-04-06 src/TunedSmoother.jl
Update synthetic cases figure

@@ -4,7 +4,7 @@ include("candidate_smoothers.jl")
 export Jacobi!,GS!,SOR!,pseudo!,state,precond!,tunedJ!
 
 include("create_synthetic.jl")
-export create_synthetic
+export create_synthetic,static,dipole,sphere
 
 include("create_waterlily.jl")
 export create_waterlily,circle,TGV,donut,wing,shark

### 2022-04-06 src/create_synthetic.jl

@@ -32,7 +32,7 @@ end
 
 @fastmath kern₀(d) = 0.5+0.5d+0.5sin(π*d)/π
 μ₀(d) = kern₀(clamp(d,-1,1))
-function sphere(;n=32,N=3,T::Type=Float32,x0=rand(T,N),m=rand(T,N),s=rand(),Δt=1)
+function sphere(;n=32,N=2,T::Type=Float32,x0=rand(T,N),m=rand(T,N),s=rand(),Δt=1)
     dims = ntuple(i->n+2,N)
     L,b = zeros(T,dims...,N), zeros(T,dims)
     x0 .*= n/3; x0 .+= (n/3); s *= n/4; m ./= √sum(abs2,m)

### 2022-04-06 tune_synthetic.jl

@@ -61,12 +61,33 @@ begin
 end
 savefig("crossloss.png")
 
-using GeometricMultigrid: mg, @loop
-data = create_synthetic(len=1)
+using GeometricMultigrid: Vcycle!,mg,mg!
+data = Dict(
+    "2D-static"=>static(m=[4.,3.]),
+    "2D-dipole"=>dipole(x0=[1,0.8],s=0.05,m=[2.,1.]),
+    "2D-sphere"=>sphere(x0=[0.,0.7],s=0.6,m=[1.,1.])
+)
+p = []; size = (400,400)
 for name in ["2D-static", "2D-dipole", "2D-sphere"]
-    A,b = data[name][1]
-    x,hist = mg(A,b)
-    name == "2D-sphere" && (@loop x[I] *= -4*A.D[I])
-    heatmap(x.data[x.R],size = (250,250),legend=false,axis=nothing)
-    savefig(name*".png")
+    # machine precision solution
+    A,b = data[name]
+    x,_ = mg(A,b)
+    # data-driven residual and solution after 1-Vcycle
+    st = state(A,b;smooth! = pseudo!, p = opt[name])
+    Vcycle!(st; smooth! = pseudo!); y=st.x
+    # zero data inside immersed geoms
+    for I in CartesianIndices((3:32,3:32))
+        x.data[I] *= -A.D[I]/4
+        y.data[I] *= -A.D[I]/4 
+    end
+    y .-= x
+    # plots
+    push!(p,heatmap(b.data[x.R];size,legend=false,axis=nothing,clim=extrema(b.data)))
+    push!(p,heatmap(st.r.data[x.R];size,legend=false,axis=nothing,clim=extrema(b.data ./10)))
+    push!(p,heatmap(x.data[x.R];size,legend=false,axis=nothing,clim=extrema(x.data)))
+    push!(p,heatmap(y.data[x.R];size,legend=false,axis=nothing,clim=extrema(x.data ./10)))
 end
+plot(permutedims(reshape(p,(4,3)))...,layout=(4,3),size=(1200,1600))
+savefig("synthetic.png")
+plot(p...,layout=(3,4),size=(1600,1200))
+savefig("synthetic2.png")

### 2022-04-06 tex/article.tex

@@
 The parameterized smoother is optimized for a set of training data $X=\{A,r^0\}$. The loss is defined as the reduction in the log-$L_2$-norm of the residual after each V-cycle iteration 
-$$L = \log_{10}(|r^{k+1}|_2 / |r^{k}|_2)$$
+\begin{equation}
+L = \log_{10}(|r^{k+1}|_2 / |r^{k}|_2)
+\end{equation}
 This loss is averaged over each iteration and each example in the data-set.
@@
 The 2D and 3D dipole cases are generated using a localized residual function
-$$ r_i = \hat m \cdot \left(\vec q_i-\vec Q\right)\ e^{-\sigma^2 |\vec q_i-\vec Q|^2} $$
+$$ r_i = \hat m \cdot \left(\vec q_i-\vec Q\right)\ e^{-\frac{|\vec q_i-\vec Q|^2}{\sigma^2 }} $$
 where $\vec Q$ is a random location in the fluid domain and $\sigma$ is a random width. The same uniform $A$ matrix is used as in the static case.

### 2022-04-06 tune_synthetic.jl
change residual colors

@@ -62,12 +62,15 @@ end
 savefig("crossloss.png")
 
 using GeometricMultigrid: Vcycle!,mg,mg!
+balance(a,b) = (min(a,-b),max(-a,b))
+myex(f) = balance(extrema(f)...)
+size = (400,400)
 data = Dict(
     "2D-static"=>static(m=[4.,3.]),
     "2D-dipole"=>dipole(x0=[1,0.8],s=0.05,m=[2.,1.]),
     "2D-sphere"=>sphere(x0=[0.,0.7],s=0.6,m=[1.,1.])
 )
-p = []; size = (400,400)
+p = []; 
 for name in ["2D-static", "2D-dipole", "2D-sphere"]
     # machine precision solution
     A,b = data[name]
@@ -82,12 +85,10 @@ for name in ["2D-static", "2D-dipole", "2D-sphere"]
     end
     y .-= x
     # plots
-    push!(p,heatmap(b.data[x.R];size,legend=false,axis=nothing,clim=extrema(b.data)))
-    push!(p,heatmap(st.r.data[x.R];size,legend=false,axis=nothing,clim=extrema(b.data ./10)))
+    push!(p,heatmap(b.data[x.R];size,legend=false,axis=nothing,c=:RdBu,clim=myex(b.data)))
+    push!(p,heatmap(st.r.data[x.R];size,legend=false,axis=nothing,c=:RdBu,clim=myex(b.data ./10)))
     push!(p,heatmap(x.data[x.R];size,legend=false,axis=nothing,clim=extrema(x.data)))
     push!(p,heatmap(y.data[x.R];size,legend=false,axis=nothing,clim=extrema(x.data ./10)))
 end
 plot(permutedims(reshape(p,(4,3)))...,layout=(4,3),size=(1200,1600))
 savefig("synthetic.png")
-plot(p...,layout=(3,4),size=(1600,1200))
-savefig("synthetic2.png")

### 2022-04-06 tex/article.tex
Updates from Overleaf

@@
-\documentclass[review]{elsarticle}
+\documentclass[]{elsarticle}
 
@@
 \usepackage{xcolor}
+\usepackage{svg}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 For a conservative Poisson operator, $A$ is symmetric, has zero-sum rows and columns, is negative semi-definite, and has a single zero eigenvalue.
-The matrix is also extremely sparse.
+\textcolor{blue}{The zero eigenvalue means the solution is unique up to an additive constant, in agreement with the derivative action of the pressure on the velocity-divergence.
+While it is possible to add an additional condition to the matrix, this is not required and has no impact on the projection problem or the measured pressure forces.} The matrix is also extremely sparse.
 While the solution vector size $N$ may easily be $10^6-10^8$, a second-order scheme on structured grids in $M$ dimensions result in only $M$ non-zero sub-diagonals.
@@
     \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/2D-static.png}
-        \caption{2D-static}
-        \label{fig:2D-static}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/2D-dipole.png}
-        \caption{2D-dipole}
-        \label{fig:2D-mu}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/2D-sphere.png}
-        \caption{2D-sphere}
-        \label{fig:2D-sphere}
-    \end{subfigure}
-    \caption{Sample solutions (left) from the data-sets of three of the six synthetic cases.
-\textcolor{blue}{Also shown are the solution errors (middle) and residuals (right) using the data-driven solvers using after reducing the residual norm by $10^{-3}$.}}
+    \includegraphics[width=0.8\textwidth]{figures/synthetic}
+    \caption{\textcolor{blue}{Examples from the 2D static (left), dipole (center), and sphere (right) synthetic cases.
+The initial residual $r^0$ (row-1) and 10x residual after one data-driven V-cycle $10r^1$ (row-2) plotted on the same scale.
+The solution after one data-driven V-cycle $x^1$ (row-3) and it's 10x error compared to a machine precision solution $10\epsilon^1$ (row-4) plotted on the same scale.}}
     \label{fig:synthetic cases}
@@
 
-\textcolor{blue}{A set of six synthetic cases were developed to establish the ability of the data-driven approach to project out residuals located at domain boundaries, body boundaries, or within the fluid.
-The three 2D cases are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
-The `static' cases feature a randomized pressure gradient throughout the domain produced by residuals on the domain boundaries.
-The `dipole' and `sphere' cases feature residuals on a random dipole or on the boundary of a random immersed sphere within an otherwise quiescent flow.
+\textcolor{blue}{A set of six synthetic cases were developed to establish the ability of the data-driven approach to project out residuals located at (i) domain boundaries, (ii) within the fluid, or (iii) on body boundaries.
+The three 2D cases and their highly localize residuals are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
+The `static' cases feature a randomized pressure gradient throughout the domain produced by residuals only on the domain boundaries (i).
+The `dipole' and `sphere' cases feature residuals on a random dipole in the fluid (ii) or on the boundary of a random immersed sphere (iii).
 Neumann conditions are applied on the domain and sphere boundaries using the Boundary Data Immersion Method (BDIM) to adjust the $A$ matrix coefficients, as described and validated in \cite{maertens2015accurate,Lauber2022}.
@@
 A data-driven GMG solver is optimized for each synthetic case using 100 randomized training examples.
-\textcolor{blue}{Figure~\ref{fig:synthetic cases} shows the velocity residual distribution produced by the trained solvers using a tolerance of $|r^k|_2/|r^0|_2<10^{-3}$, as well as the error in the pressure compared to a result obtained using a classic GMG method converged to machine precision.
-The results show that the initially highly-localized residual is project and distributed throughout the domain, without build-up on the domain or immersed boundaries.}
+\textcolor{blue}{Figure~\ref{fig:synthetic cases} shows the residual and error of each case after \textit{one} data-driven V-cycle.
+The results show that the initially highly-localized residual is projected throughout the domain, without build-up of error on the domain or immersed boundaries.
+Repeated V-cycles drives the residual and error to machine zero in every case.}
+
+Figure~\ref{fig:cross plot} quantifies the generalization performance of each trained projection method on 100 unseen test examples for each case.
+\textcolor{blue}{The results for a Jacobi-smoothed GMG V-cycle are shown for comparison as this is the initial condition for the \textit{untrained} data-driven method.} After training, the data-driven method vastly outperform the Jacobi V-cycle, doubling the residual loss on the 3D-dipole case and providing nearly 30-fold improvement on the 3D-static case.
+While the performance of the data-driven projection method is best when testing and training on the same case, most of the solvers still improve on the Jacobi-smoothed GMG performance for cases outside of their training set.
+Indeed, the solver trained on the 2D-sphere generalizes essentially as well as a solver trained on the `union' of the all training case data.
+The exceptions are the static cases, with the solver trained on the 2D-static case failing to converge on three of the other test cases.
+Note that despite identical $A$ matrices in the static and dipole cases, the performance of the those solvers are completely different.
+This indicates that the data-driven methods are specializing based on the residual data as well as the matrix structure, a feature unique to this approach.
 
@@
 
-Figure~\ref{fig:cross plot} quantifies the generalization performance of each trained projection method on 100 unseen test examples for each case.
-\textcolor{blue}{The results for a Jacobi-smoothed GMG V-cycle are shown for comparison as this is the initial condition for the \textit{untrained} data-driven method.} After training, the data-driven method vastly outperform the Jacobi V-cycle, doubling the residual loss on the 3D-dipole case and providing nearly 30-fold improvement on the 3D-static case.
-While the performance of the data-driven projection method is best when testing and training on the same case, most of the solvers still improve on the Jacobi-smoothed GMG performance for cases outside of their training set.
-Indeed, the solver trained on the 2D-sphere generalizes essentially as well as a solver trained on the `union' of the all training case data.
-The exceptions are the static cases, with the solver trained on the 2D-static case failing to converge on three of the other test cases.
-Note that despite identical $A$ matrices in the static and dipole cases, the performance of the those solvers are completely different.
-This indicates that the data-driven methods are specializing based on the residual data as well as the matrix structure, a feature unique to this approach.
-
-\textcolor{blue}{Next, the acceleration of the data-driven projection method is evaluated against high-performance GMG solvers using classic stationary smoothers; Gauss-Sidel and SOR.} The `union'-trained data-driven solver is chosen and 100 tests are generated for each case on different grids to test the ability of the data-driven method to generalize to new grid sizes.
+\textcolor{blue}{Finally, the acceleration of the data-driven projection method is evaluated against high-performance GMG solvers using classic stationary smoothers; Gauss-Sidel and SOR.} The `union'-trained data-driven solver is chosen and 100 tests are generated for each case on different grids to test the ability of the data-driven method to generalize to new grid sizes.
 
@@
     \begin{subfigure}[b]{\textwidth}
+
         \centering
         \includegraphics[width=\textwidth]{figures/donuttriple.png}
-        \caption{Slice of 3D torus (donut) flow}
+        \caption{Slice through 3D donut flow}
     \end{subfigure}
-    \begin{subfigure}[c]{0.6\textwidth}
+    \begin{subfigure}[c]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{figures/TGVtriple.png}
-        \caption{Slice of 3D Taylor-Green Vortex}
+        \includegraphics[width=\textwidth,trim={0 150 0 0},clip=true]{figures/TGVtriple.png}
+        \caption{Slice through 3D Taylor-Green Vortex (TGV)}
     \end{subfigure}
-    \begin{subfigure}[c]{0.6\textwidth}
+    \begin{subfigure}[c]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{figures/wingtriple.png}
+        \includegraphics[width=\textwidth,trim={0 100 0 60},clip=true]{figures/wingtriple.png}
         \caption{Flapping wing}
@@
     \hfill
-    \caption{Snapshots from the five flow simulation cases showing the pressure solution (left), the initial residual (middle), and the residual after a single V-cycle (right) using the data-driven projection method.
-The Taylor-Green Vortex and torus flow are 3D, the flapping wing is dynamic without a background flow and the swimming shark is a deforming geometry.
-All residuals are visualized using $\log_{10}\text{abs}(r)$ on the same scale, $10^{-6} \ldots 10^{-1}$.}
+    \caption{Snapshots from the five flow simulation cases showing the pressure solution (left), the initial residual $|r^0|$ (middle), and after a single V-cycle $|r^1|$ (right) using the data-driven projection method.
+The TGV and donut flow are 3D, the flapping wing is dynamic without a background flow and the swimming shark is a deforming geometry.
+All residuals are visualized on the same log-scale, $10^{-6} \ldots 10^{-1}$.
+The TGV and wing images have been zoomed in for display purposes.}
     \label{fig:simulation cases}

### 2022-04-07 benchmark.jl
Move legends

@@ -30,14 +30,14 @@ end
 
 begin # plot
     using StatsPlots,CategoricalArrays
-    cats = ["Gauss-Sidel","SOR","Ã⁻¹ union"]
+    cats = ["GS","SOR","Ã⁻¹"]
     n = length(data)
     colors = repeat([palette(:default)[2],palette(:default)[4],palette(:default)[3]],inner=n)
     ctg = CategoricalArray(repeat(cats,inner=n))
     levels!(ctg,cats)
-    groupedbar((counts.*time_factor)',size=(400,350),
-                group=ctg,c=colors,legend=:bottomright, 
+    groupedbar((counts.*time_factor)',size=(500,400),
+                group=ctg,c=colors,legend=:outerbottomright, 
                 yaxis=("relative time"),
                 xaxis=("cases",(1:n,keys(data)),60))
 end
-savefig("synthetic_timing.png")
+savefig("synthetic_timing.pdf")

### 2022-04-07 test_waterlily.jl

@@ -40,12 +40,12 @@ begin
     cats = ["Jacobi","transfer","⅛","¼","½","1"]
     ctg = CategoricalArray(repeat(cats,inner=length(data)))
     levels!(ctg,cats)
-    groupedbar(scaleloss', size = (420,400),
-                group=ctg, legend=:bottomright, palette=:Greens_6,
+    groupedbar(scaleloss', size = (500,400),
+                group=ctg, legend=:outerbottomright, palette=:Greens_6,
                 yaxis=("log₁₀ residual reduction",:flip),
                 xaxis=("cases",(1:length(data),keys(data))),)
 end
-savefig("scaleloss.png")
+savefig("scaleloss.pdf")
 
 begin
     scaledata = create_waterlily(p=4)
@@ -96,11 +96,11 @@ begin
     ctg = CategoricalArray(repeat(cats,inner=n))
     levels!(ctg,cats)
     groupedbar(crosscount',size=(400,400),
-                group=ctg, legend=:bottomright,c=colors,
+                group=ctg, legend=:topleft,c=colors,
                 yaxis=("relative time"),
                 xaxis=("cases",(1:length(data),keys(data))),)
 end
-savefig("crosscount.png")
+savefig("crosscount.pdf")
 
 # plot best pseudo-inverse functions across examples
 begin

### 2022-04-07 figures/forces.jl
Add force plot

@@ -1,0 +1,37 @@
+using TunedSmoother,WaterLily,Plots
+using GeometricMultigrid: Vcycle!
+
+# shark parameters from test_waterlily
+p = [0.0673015, -0.104415, -0.024194, -0.182964, -0.298915]
+
+A,St,remeasure = 0.1,0.3,true
+cycles,period,steps = 2,2A/St,120
+t₀,Δt = 3,cycles*period/steps
+
+# Set up and run simulation
+sim = shark(6;A,St)
+sim_step!(sim,t₀;remeasure)
+
+# Get Poisson data over next period
+data = [(TunedSmoother.sim_collect_poisson!(sim;Δt,remeasure),sim_time(sim)) for i ∈ 1:steps]
+
+# Integrate pressure data at time t
+get_forces(data;kw...) = map(data) do ((A,p,b),t)
+	st = state(A,b;kw...)
+	mg!(st;kw...)
+	WaterLily.∮nds(st.x.data,sim.body,t*sim.L/sim.U)./(0.5*sim.L*sim.U^2)
+end
+
+begin
+	reltol=1e-3
+	thrust = plot(xlabel="scaled time", ylabel="scaled thrust force")
+	side = plot(xlabel="scaled time", ylabel="scaled side force")
+	forces = get_forces(data;reltol)
+	plot!(thrust,last.(data),first.(forces),label="GS",c=palette(:default)[2])
+	plot!(side,  last.(data), last.(forces),label="GS",c=palette(:default)[2])
+	forces = get_forces(data;reltol,smooth! = pseudo!, p)
+	plot!(thrust,last.(data),first.(forces),label="Ã⁻¹",line=:dash,c=palette(:default)[3])
+	plot!(side,  last.(data), last.(forces),label="Ã⁻¹",line=:dash,c=palette(:default)[3])
+end
+plot(thrust,side,layout=(2,1))
+savefig("forces.pdf")

### 2022-04-07 tex/article.tex
Updates from Overleaf

@@
 
-%All cases are initialized with $x^0=0$ and all cases feature initially localized residuals; i.e.
-$r^0\ne0$ only in a fraction of the cells, but $x$ must be updated throughout the domain, starkly illustrating the elliptic nature of the projection step.
 A data-driven GMG solver is optimized for each synthetic case using 100 randomized training examples.
-\textcolor{blue}{Figure~\ref{fig:synthetic cases} shows the residual and error of each case after \textit{one} data-driven V-cycle.
+\textcolor{blue}{Figure~\ref{fig:synthetic cases} shows the residual and error of each case after one data-driven V-cycle.
 The results show that the initially highly-localized residual is projected throughout the domain, without build-up of error on the domain or immersed boundaries.
@@
     \hfill
-    \begin{subfigure}[b]{0.47\textwidth}
+    \begin{subfigure}[b]{0.5\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{figures/synthetic_timing.png}
+        \includegraphics[width=\textwidth]{figures/synthetic_timing}
         \caption{solver time}
@@
 The results show that the residual decreases throughout the domain, including at the domain and immersed boundaries.
-\textcolor{blue}{This is further verified by Fig~\ref{fig:simulation forces}, which compares the unsteady pressure force on the circle flow (case a) and the swimming shark (case b) using both the data-driven and Gauss-Sidel smoothed GMG solvers.
-In both cases, the data-driven method matches the Gauss-Sidel forces for the same residual tolerance.} As such, the new data-driven method is shown to produce uniformly valid solutions despite only being trained to optimize the global residual loss.
+\textcolor{blue}{This is further verified by Fig~\ref{fig:simulation forces}, which shows the unsteady pressure force the swimming shark case using the data-driven GMG solver is indistinguishable from the Gauss-Sidel smoothed results.} As such, the new data-driven method is shown to produce uniformly valid solutions despite only being trained to optimize the global residual loss.
 
@@
     \centering
-    \begin{subfigure}[b]{0.47\textwidth}
-        \centering
-        \caption{Cylinder pressure}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.47\textwidth}
-        \centering
-        \caption{Swimming shark}
-    \end{subfigure}
-    \caption{Integrated pressure forces on the (a) cylinder and (b) swimming shark test cases using the data-driven and Gauss-Sidel GMG solvers for different residual tolerance levels.
-The $|r^k/r^0|<10^{-3}$ level is indistinguishable from that obtained driving the residuals to machine zero.}
+    \includegraphics[width=0.7\textwidth]{figures/forces.pdf}
+    \caption{\textcolor{blue}{Integrated thrust and side pressure forces the swimming shark test case using the Gauss-Sidel (GS) and data-driven ($\tilde A^{-1}$) GMG solvers and $|r^k/r^0|<10^{-3}$ tolerance level.}}
     \label{fig:simulation forces}
@@
     \centering
-    \begin{subfigure}[b]{0.47\textwidth}
+    \begin{subfigure}[b]{0.52\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{figures/scaleloss.png}
+        \includegraphics[width=\textwidth]{figures/scaleloss}
         \caption{single-cycle residual reduction}
@@
     \hfill
-    \begin{subfigure}[b]{0.47\textwidth}
+    \begin{subfigure}[b]{0.42\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{figures/crosscount.png}
+        \includegraphics[width=\textwidth]{figures/crosscount}
         \caption{solver time}

### 2022-04-08 tex/article.tex
submitted revised version

@@
 Pressure projection is the single most computationally expensive step in an unsteady incompressible fluid simulation.
-\textcolor{blue}{This work demonstrates the ability of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection.} Geometric Multi-Grid methods are identified as linear convolutional encoder-decoder networks and a data-driven smoother is developed using automatic differentiation to optimize the velocity-divergence projection.
+\textcolor{black}{This work demonstrates the ability of data-driven methods to accelerate the approximate solution of the Poisson equation at the heart of pressure projection.} Geometric Multi-Grid methods are identified as linear convolutional encoder-decoder networks and a data-driven smoother is developed using automatic differentiation to optimize the velocity-divergence projection.
 The new method is found to accelerate classic Multi-Grid methods by a factor of two to three with no loss of accuracy on eleven 2D and 3D flow cases including cases with dynamic immersed solid boundaries.
@@
 While there is a long history of optimizing multi-grid methods (both geometric \cite{tang2000sparse} and algebraic \cite{brezina2006adaptive}), few of these have taken a direct data-driven approach.
-\textcolor{blue}{\cite{tang2000sparse} construct a sparse approximate smoother by solving a series of least-square matrix equations instead of a data-driven approach.
+\textcolor{black}{In \cite{tang2000sparse}, a sparse approximate smoother is constructed by solving a series of least-square matrix equations instead of a data-driven approach.
 This improved the convergence properties on extremely skewed grids compared to Gauss-Sidel smoothers, but not on more regular grids or when using a very sparse (and therefore fast) approximate inverse.}
@@
 Recent work has shown promising initial results in constructing data-driven restriction and prolongation operators \cite{KATRUTSA2020112524,greenfeld2019learning}.
-\textcolor{blue}{However, improving the architecture of these operators is a very challenging discrete optimization problem, limiting the results achieved thus far.
+\textcolor{black}{However, improving the architecture of these operators is a very challenging discrete optimization problem, limiting the results achieved thus far.
 Both \cite{KATRUTSA2020112524,greenfeld2019learning} show improved convergence spectra compared to classic GMG methods, but no overall speed-up.
@@
 
-\textcolor{blue}{Building on this foundation, this manuscript develops a novel data-driven smoother which is optimize using automatic differentiation to minimize the velocity-divergence over the full recursive GMG V-cycle.
+\textcolor{black}{Building on this foundation, this manuscript develops a novel data-driven smoother which is optimized using automatic differentiation to minimize the velocity-divergence over the full recursive GMG V-cycle.
 This new framework achieves 2 to 3-fold acceleration compared to standard GMG on eleven 2D and 3D benchmark projection problems including those derived from unsteady Navier-Stokes simulations with dynamic immersed boundaries.} Moreover, since the new approach maintains linearity in the pressure and the nonlinear dependence on the matrix coefficients are scale-invariant, the data-optimized parameters generalize extremely well to new flows and simulation resolutions.
@@
 For a conservative Poisson operator, $A$ is symmetric, has zero-sum rows and columns, is negative semi-definite, and has a single zero eigenvalue.
-\textcolor{blue}{The zero eigenvalue means the solution is unique up to an additive constant, in agreement with the derivative action of the pressure on the velocity-divergence.
+\textcolor{black}{The zero eigenvalue means the solution is unique up to an additive constant, in agreement with the derivative action of the pressure on the velocity-divergence.
 While it is possible to add an additional condition to the matrix, this is not required and has no impact on the projection problem or the measured pressure forces.} The matrix is also extremely sparse.
@@
 where $r$ is the residual.
-\textcolor{blue}{In the context of the pressure Poisson equation, the residual is the remaining divergence in the velocity field.
+\textcolor{black}{In the context of the pressure Poisson equation, the residual is the remaining divergence in the velocity field.
 Driving this residual to zero by updating the pressure is the goal of the projection step.}
@@
 \end{equation}
-\textcolor{blue}{This process is iterated until the velocity-divergence residual is reduced to a specified tolerance, at which point the projection step is complete.}
+\textcolor{black}{This process is iterated until the velocity-divergence residual is reduced to a specified tolerance, at which point the projection step is complete.}
 
@@
 Unlike Gauss-Sidel or SOR smoothers, the sparse matrix-vector multiplication of equation \ref{eq:smooth} requires no back-propagation and so can be vectorized in serial or parallel implementations, offering a significant potential speed-up.
-Additionally, the matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be stored ahead of time, avoiding on the fly function evaluations.
+Additionally, the matrix $A$ is constant during the projection step (and often for an entire simulation), meaning $\tilde A^{-1}$ can be computed and stored ahead of time.
 
@@
 This loss is averaged over each iteration and each example in the data-set.
-\textcolor{blue}{Working directly with a residual loss has a number of advantages.
+\textcolor{black}{Working directly with a residual loss has a number of advantages.
 First and foremost, the purpose of the pressure projection step is to drive the velocity-divergence residual to zero, making this the ultimate judge of any projection method.
@@
     \includegraphics[width=0.8\textwidth]{figures/synthetic}
-    \caption{\textcolor{blue}{Examples from the 2D static (left), dipole (center), and sphere (right) synthetic cases.
+    \caption{\textcolor{black}{Examples from the 2D static (left), dipole (center), and sphere (right) synthetic cases.
 The initial residual $r^0$ (row-1) and 10x residual after one data-driven V-cycle $10r^1$ (row-2) plotted on the same scale.
@@
 
-\textcolor{blue}{A set of six synthetic cases were developed to establish the ability of the data-driven approach to project out residuals located at (i) domain boundaries, (ii) within the fluid, or (iii) on body boundaries.
-The three 2D cases and their highly localize residuals are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
-The `static' cases feature a randomized pressure gradient throughout the domain produced by residuals only on the domain boundaries (i).
+\textcolor{black}{A set of six synthetic cases were developed to establish the ability of the data-driven approach to project out residuals (i) on domain boundaries, (ii) within the fluid, or (iii) on body boundaries.
+The three 2D cases and their highly localized residuals are shown in Figure~\ref{fig:synthetic cases}, and each has a matching 3D case.
+The `static' cases feature a random linear pressure field generated by residuals on the domain boundaries (i).
 The `dipole' and `sphere' cases feature residuals on a random dipole in the fluid (ii) or on the boundary of a random immersed sphere (iii).
@@
 A data-driven GMG solver is optimized for each synthetic case using 100 randomized training examples.
-\textcolor{blue}{Figure~\ref{fig:synthetic cases} shows the residual and error of each case after one data-driven V-cycle.
+\textcolor{black}{Figure~\ref{fig:synthetic cases} also shows the residual and error of each case after one data-driven V-cycle.
 The results show that the initially highly-localized residual is projected throughout the domain, without build-up of error on the domain or immersed boundaries.
@@
 
-Figure~\ref{fig:cross plot} quantifies the generalization performance of each trained projection method on 100 unseen test examples for each case.
-\textcolor{blue}{The results for a Jacobi-smoothed GMG V-cycle are shown for comparison as this is the initial condition for the \textit{untrained} data-driven method.} After training, the data-driven method vastly outperform the Jacobi V-cycle, doubling the residual loss on the 3D-dipole case and providing nearly 30-fold improvement on the 3D-static case.
+Figure~\ref{fig:cross plot} quantifies the generalization performance of each trained projection method on 100 unseen test examples across cases.
+\textcolor{black}{The results for a Jacobi-smoothed GMG V-cycle are shown for comparison as this is the initial condition for the \textit{untrained} data-driven method.} After training, the data-driven method vastly outperform the Jacobi V-cycle, doubling the residual loss on the 3D-dipole case and providing nearly 30-fold improvement on the 3D-static case.
 While the performance of the data-driven projection method is best when testing and training on the same case, most of the solvers still improve on the Jacobi-smoothed GMG performance for cases outside of their training set.
@@
 
-\textcolor{blue}{Finally, the acceleration of the data-driven projection method is evaluated against high-performance GMG solvers using classic stationary smoothers; Gauss-Sidel and SOR.} The `union'-trained data-driven solver is chosen and 100 tests are generated for each case on different grids to test the ability of the data-driven method to generalize to new grid sizes.
+\textcolor{black}{Finally, the acceleration of the data-driven projection method is evaluated against high-performance GMG solvers using classic stationary smoothers; Gauss-Sidel (GS) and Successive-Over-Relaxation (SOR).} The `union'-trained data-driven solver is used and 100 tests are generated for each case on different grids to test the ability of the data-driven method to generalize to new grid sizes.
 
 The results in Figure~\ref{fig:synthetic time} show that the data-driven method has no issue projecting the velocity divergence on unseen grid sizes, reducing the residual by $10^{-3}$ in only 2-5x the time of a single Jacobi-smoothed V-cycle.
-\textcolor{blue}{This is chosen as our unit of time since Jacobi-smoothing requires the smallest possible number of operations per V-cycle on a given grid.} As the pseudo-inverse smoother is many times faster than the Gauss-Sidel and SOR smoothers, this results in an overall 80-210\% speed-up (mean: 133\%) relative to classic GMG solvers.
+\textcolor{black}{This is chosen as our unit of time since Jacobi-smoothing requires the smallest possible number of operations per V-cycle, normalizing results across grids.} As the pseudo-inverse smoother is many times faster than the Gauss-Sidel and SOR smoothers, this results in an overall 80-210\% speed-up (mean: 133\%) relative to classic GMG solvers.
 Note that this speed-up will be even more favorable in parallel computation as the new smoother operates directly on the local residual without back-propagation, eliminating any additional communication.
@@
 Five unsteady incompressible simulation cases were used to further characterize the accelerated projection method, Figure \ref{fig:simulation cases}.
-\textcolor{blue}{The first three cases are variations on standard unsteady flow benchmarks, while the second two are variations of recent validated biologically-inspired flows \cite{Lauber2022}.} The simulations feature significantly different physics to test the accelerated projection performance from flows with and without background velocities, immersed geometries, body motion, and body deformation, as well as using computational grids of different sizes and aspect ratios.
-\textcolor{blue}{All simulations use the same extensively validated unsteady incompressible Navier-Stokes BDIM solver \cite{maertens2015accurate,Lauber2022} and 100 Poisson matrices $A$ and initial residuals $r^0$ are copied from each unsteady simulation to form the training and testing data.
+\textcolor{black}{The first three cases are variations on standard unsteady flow benchmarks, while the second two are variations of recent validated biologically-inspired flows \cite{Lauber2022}.} The simulations feature significantly different physics to test the accelerated projection performance from flows with and without background velocities, immersed geometries, body motion, and body deformation, as well as using computational grids of different sizes and aspect ratios.
+\textcolor{black}{All simulations use the same extensively validated unsteady incompressible Navier-Stokes BDIM solver \cite{maertens2015accurate,Lauber2022} and 100 Poisson matrices $A$ and initial residuals $r^0$ are copied from each unsteady simulation to form the training and testing data.
 The details of each case are found in \ref{app flow}.}
@@
 The results show that the residual decreases throughout the domain, including at the domain and immersed boundaries.
-\textcolor{blue}{This is further verified by Fig~\ref{fig:simulation forces}, which shows the unsteady pressure force the swimming shark case using the data-driven GMG solver is indistinguishable from the Gauss-Sidel smoothed results.} As such, the new data-driven method is shown to produce uniformly valid solutions despite only being trained to optimize the global residual loss.
+\textcolor{black}{This is further verified by Fig~\ref{fig:simulation forces}, which demonstrates that the unsteady swimming shark pressure forces using the data-driven GMG solver is indistinguishable from the Gauss-Sidel smoothed results.} As such, the new data-driven method is shown to produce uniformly valid solutions despite only being trained to optimize the global residual loss.
 
@@
     \includegraphics[width=0.7\textwidth]{figures/forces.pdf}
-    \caption{\textcolor{blue}{Integrated thrust and side pressure forces the swimming shark test case using the Gauss-Sidel (GS) and data-driven ($\tilde A^{-1}$) GMG solvers and $|r^k/r^0|<10^{-3}$ tolerance level.}}
+    \caption{\textcolor{black}{Integrated thrust and side pressure forces the swimming shark test case using the Gauss-Sidel (GS) and data-driven ($\tilde A^{-1}$) GMG solvers and $|r^k/r^0|<10^{-3}$ tolerance level.}}
     \label{fig:simulation forces}
@@
 Wherever possible, this work has made the simplest choice in parameterization, leaving significant opportunities for future improvements.
-\textcolor{blue}{The flow cases in this manuscript use Cartesian-grids, but this does not limit the generality of the projection problems as the resulting $A$ matrices are nonuniform due to the presence of the immersed geometries.
+\textcolor{black}{The flow cases in this manuscript use Cartesian-grids, but this does not limit the generality of the projection problems as the resulting $A$ matrices are nonuniform due to the presence of the immersed geometries.
 The current data-driven GMG framework can therefore be readily extended to the nonuniform matrices induced by stretched structured grids.
@@
 \bibliography{mybibfile}
-\color{blue}
+\color{black}
 \appendix

### 2022-04-17 benchmark.jl
Regenerate synthetic_timing plot

@@ -31,11 +31,12 @@ end
 begin # plot
     using StatsPlots,CategoricalArrays
     cats = ["GS","SOR","Ã⁻¹"]
+    data = create_synthetic(len=1)
     n = length(data)
     colors = repeat([palette(:default)[2],palette(:default)[4],palette(:default)[3]],inner=n)
     ctg = CategoricalArray(repeat(cats,inner=n))
     levels!(ctg,cats)
-    groupedbar((counts.*time_factor)',size=(500,400),
+    groupedbar(rel_time',size=(500,400),
                 group=ctg,c=colors,legend=:outerbottomright, 
                 yaxis=("relative time"),
                 xaxis=("cases",(1:n,keys(data)),60))
